### 2014-09-20 doc/informe/paper.tex
moved to doc/ because of specification

% Preview source code

%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{float}
\usepackage{amstext}
\usepackage{graphicx}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
\newcommand{\lyxmathsym}[1]{\ifmmode\begingroup\def\b@ld{bold}
  \text{\ifx\math@version\b@ld\bfseries\fi#1}\endgroup\else#1\fi}

\makeatother

\usepackage[english]{babel}
\begin{document}

\title{A Pedestrian Simulation }

\author{Daniel Parisi, Agustin Marseillan, Castiglione Gonzalo}
\maketitle
\begin{abstract}
En este paper se presenta un nuevo método para simular peatones virtuales
basado en el modelo de la fuerza social. En el modelo presentado,
cada peatón posee un punto movil frente a el y camina siempre hasta
este. Este punto representa un objetivo a corto plazo que se debe
cumplir. Cada peatón se encarga de mover este punto según a donde
necesite llegar. 
\end{abstract}
keywords:

pedestrian, collision avoidance, future, force model

\pagebreak{}

\section{Introduccion}

// Daniel tiene ya preparada una introducción\\

El transito de personas es un factor de suma importancia en el análisis
y diseño de instalaciones tales como edificios públicos, peatonales,
estaciones de trenes, entre otros.

// Hace mucho tiempo que se viene estudiando a las personas en grupo
y se sabe que

// Existen efectos de comportamiento colectivos de auto organización
tales como cuellos de botellas, formaciones en filas, bloqueos.

// Decir porque una simulación de peatones es útil para estas situaciones.\\

Analizar estructuras de transito de peatones usando los cambios propuestos
para el modelo de la fuerza social. Implementar una interfaz gráfica
para poder visualizar los resultados de cambiar el modelo y cada uno
de los parámetros

\section{Modelo de agentes}

El actual modelo se encuentra definido uncamente por peatones. Estos
se encuentran definidos por: 
\begin{itemize}
\item Area circular

Representa el área física que ocupa el peatón. El radio del círculo
es generado aleatoriamente con el fin de representar peatones diferentes.
El rango de valores se distribuye uniformemente en el intervalo $[0.25,0.29]$
$[cm]$.

\item Objetivo a largo plazo

Se represa por por un segmento de recta, al tocarse, se considera
que el objetivo fue cumplido. Se permite la definición de múltiples
objetivos, en cuyo caso, se deben cumplir todos de manera secuencial
según el orden en que fueron especificados.

\item Posición objetivo a corto plazo

Llamado Future, representa un punto a corta distancia del peatón,
que debe ser alcanzado. El seguir este punto garantiza que se va a
cumplir el objetivo a largo plazo, aunque podría recorrerse un camino
no óptimo en cuanto a distancia recorrida. Este punto es un punto
móvil y se puede aplicar fuerzas sobre el. La masa de este punto fue
definida fija con un valor de $1$ $[kg]$.

\item Velocidad objetivo

Con el fin de representar peatones que puedan estar apurados o tranquilos,
se definió la velocidad máxima deseada de un peatón de manera aleatoria.
El rango de valores se encuentra definido en el intervalo $[1,1.6]$
$[m/s]$.

\item Distancia de reacción

Representa la distancia a la cual va a tratar de posicionar de sí
mismo un peatón su propio future. Una mayor distancia representa un
peatón que reacciona más rápido a una posible colisión.

\end{itemize}
En la siguiente imagen se puede observar de manera gráfica la descripción
de un peatón:

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.5]{pedestrian-top}\caption{Vista superior de un peaton}

\par\end{centering}

\end{figure}

// FALTA ESPECIFICAR:

// i representa un peaton e i\textquoteright{} representa el future
del peaton

// que se usa Euler para el calculo del dx de cada cuerpo

// el dt usado

\section{Funcionamiento}

Cada peatón en la simulación posee un objetivo a largo plazo que sea
desea que alcance. Para asegurar que esto se cumpla, se trata siempre
de mantener su future (objetivo a corto plazo) alineado con el camino
más óptimo hacia su objetivo. Sin embargo, pueden darse casos en donde
exista uno o más peatones en el camino, obligando a tener que buscar
rutas alternativas. Es en estas circunstancias en donde el objetivo
a corto plazo va a cambiar su dirección según corresponda.

El movimiento de los peatones se realiza de manera sincrónica y se
calcula en cuatro etapas: 
\begin{enumerate}
\item Cálculo de la fuerza sobre sobre cada future. 
\item Actualización de la posición de cada future. 
\item Cálculo de la fuerza sobre cada peatón. 
\item Actualización de la posicion de cada peatón. \\

\end{enumerate}
En donde, cada etapa se define de la siguiente manera:
\begin{enumerate}
\item Cálculo de la fuerza sobre sobre cada future.

En esta etapa, lo que se va a hacer es calcular la fuerza que sufre
cada uno de los futures existentes debido a la existencia de otros
peatones. Esta se realiza sólo cuando la distancia entre el peatón
y su future se encuentra por encima de cierto valor. Esto es así ya
que a altos niveles de densidad de personas. Uno ya no intenta moverse
ya que simplemente es arrastrado por la masa de gente. \textbf{(verificar
si es correcta esta última frase)}

En el caso contrario, cuando que un peatón se encuentra habilitado
para moverse, se realiza un filtro de todos aquellos peatones que
se encuentran a sus espaldas, ya que estos no son casos que afectam
la trayectoria de la persona. La condición que debe cumplirse para
considerar un peatón $j$ como detrás del peatón $i$ es:

\[
v=normal(i,center.target.i)
\]
\[
v_{x1x0}=v_{x1}-v_{x0}
\]
\[
v_{x1x0}.x*(i.y-v_{x0}.y)-v_{x1x0}.y*(i.x-v_{x0}.x)>0
\]

Una vez filtrado los peatones, simplemente se calcula por cada future
restante, la fuerza de repulsión entre estos. Este se realiza utilizando
la fórmula:

\[
F_{i',j'}=\alpha e^{-dist(i',j')/\beta}
\]

en donde $\alpha$ y $\beta$ son constantes predefinidas y fijas.
Los valores que se usaron son $?$ y $?$ respectivamente. Esto produce
que los peatones tienda siempre a alejarse de grandes multitudes más
de lo que aleja de una sola persona. Si la suma de todas las fuerzas
ejercidas sobre todos los demás futures $j\lyxmathsym{\textquoteright}$
al future $i\lyxmathsym{\textquoteright}$ es menor que cierto umbral,
entonces se desprecia esta fuerza y el future $i\lyxmathsym{\textquoteright}$
simplemente es posicionado sobre la recta que une al peatón $i$ con
su objetivo a largo plazo a distancia que indique la distancia de
reacción del peatón.

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{pedestrian-top-forces}\caption{Fuerzas que actúan sobre el Future $i'$}
\end{figure}

\item Actualización de la posición de cada future.

En esta etapa, simplemente se actualiza la posición de cada future
según el cálculo de la fuerza aplicada en la etapa previa. Este cálculo
se realiza utilizando las fórmulas Eulerianas.

\item Cálculo de la fuerza sobre cada peatón.

El peatón siempre se mueve hacia la dirección en la que apunta su
future y de acuerdo a la fuerza de deseo.

Esta fuerza representa la atracción que un peatón $i$ ejerce sobre
sí mismo a fin de dar un paso hacia su future y tratar de alcanzarlo.
Esta definida por la siguiente fórmula:

\[
F_{deseo}=\frac{dist(i',i)}{dist_{react}}\frac{v_{desire}-v_{curr}}{\tau}\frac{i'-i}{|i'-i|}
\]

En donde $\tau=0.5$

\item Actualización de la posición de cada peatón.

La nueva posicion de cada peatón es calculada en esta etapa utilizando
las mismas fórmulas mencionada en la etapa 2.

\item Validación del modelo

\textbf{// Poner Graficos indicando distancias y esquemas del future
y la particula. }

\item Conclusiones

\textbf{// agregar al final futuras opciones que se abren con este
trabajo}

\end{enumerate}
\pagebreak{}
\begin{enumerate}
\item Referencias

{[}1{]}... Karamouzas?

{[}2{]}...\end{enumerate}

\end{document}

### 2014-10-18 src/main/java/ar/edu/itba/pedestriansim/back/PedestrianSimApp.java
Curva no lineal que dice la velocidad con la que se va a mover el pedestrian hacia su future. Ruido al future (tanto angular como longutudinal). Considerar choques con cierto delta

@@ -41,8 +41,7 @@ public class PedestrianSimApp implements Runnable {
 
 	private static final Logger logger = Logger.getLogger(PedestrianSimApp.class);
 
-
-	private final boolean FUTURE_FORCE_MODEL = false;
+	private final boolean FUTURE_FORCE_MODEL = true;
 	private final PedestrianAppConfig _config;
 
 	public PedestrianSimApp(PedestrianAppConfig config) {
@@ -66,7 +65,7 @@ public class PedestrianSimApp implements Runnable {
 		});
 		sim.onStep(new PedestrianAreaStateFileWriter(
 			fileCloser.register(newFileWriter(_config.staticfile())), 
-			fileCloser.register(newFileWriter(_config.dynamicfile())), 0.03f)
+			fileCloser.register(newFileWriter(_config.dynamicfile())), 0.01f)
 		);
 		if (FUTURE_FORCE_MODEL) {
 			configureFutureModelComponents(sim);
@@ -90,16 +89,16 @@ public class PedestrianSimApp implements Runnable {
 				}
 			})
 			.onEnd(new Function<PedestrianArea, PedestrianArea>() {
-			@Override
-			public PedestrianArea apply(PedestrianArea input) {
-				try {
-					fileCloser.close();
-				} catch (IOException e) {
-					throw new IllegalStateException(e);
+				@Override
+				public PedestrianArea apply(PedestrianArea input) {
+					try {
+						fileCloser.close();
+					} catch (IOException e) {
+						throw new IllegalStateException(e);
+					}
+					return input;
 				}
-				return input;
-			}
-		});
+			});
 		return sim;
 	}
 
@@ -115,7 +114,7 @@ public class PedestrianSimApp implements Runnable {
 		final PedestrianForces forces = new PedestrianForcesFactory().build(_config);
 		sim
 			.onStep(new FutureForceUpdaterComponent(forces))
-			.onStep(new FuturePositionUpdaterComponent())
+			.onStep(new FuturePositionUpdaterComponent(true, false))
 			.onStep(new PedestrianForceUpdaterComponent(forces));
 	}
 	

### 2014-10-18 src/main/java/ar/edu/itba/pedestriansim/back/entity/force/ReactionDistanceDesireForce.java

@@ -4,20 +4,49 @@ import org.newdawn.slick.geom.Vector2f;
 
 import ar.edu.itba.pedestriansim.back.entity.Pedestrian;
 
+import com.google.common.base.Preconditions;
+
 public class ReactionDistanceDesireForce implements PedestrianForce {
 
-	private final DrivingForce forceModel;
-	
-	public ReactionDistanceDesireForce() {
-		forceModel = new DrivingForce();
+	public static enum FunctionType {
+		LINEAR {
+			@Override
+			float p(float distance, float maxDistance) {
+				distance = Math.min(distance, maxDistance);
+				return distance / maxDistance;
+			}
+		},
+		SQ {
+			@Override
+			float p(float distance, float maxDistance) {
+				float p = LINEAR.p(distance, maxDistance);
+				return p * p;
+			}
+		},
+		SQRT {
+			@Override
+			float p(float distance, float maxDistance) {
+				float p = LINEAR.p(distance, maxDistance);
+				return (float) Math.sqrt(p);
+			}
+		};
+		abstract float p(float distance, float maxDistance);
+	};
+
+	private final FunctionType _functionType;
+	private final DrivingForce _forceModel;
+
+	public ReactionDistanceDesireForce(FunctionType functionType) {
+		_forceModel = new DrivingForce();
+		_functionType = functionType;
 	}
-	
+
 	@Override
 	public Vector2f apply(Pedestrian subject) {
 		Vector2f target = subject.getFuture().getBody().getCenter();
 		float distance = subject.getBody().getCenter().distance(target);
-		float p = distance / subject.getReactionDistance();
-		return forceModel.getForce(subject.getBody(), target, subject.getMaxVelocity() * p);
+		float p = _functionType.p(distance, subject.getReactionDistance());
+		Preconditions.checkArgument(0 <= p && p <= 1);
+		return _forceModel.getForce(subject.getBody(), target, subject.getMaxVelocity() * p);
 	}
-
 }

### 2014-10-18 src/main/java/ar/edu/itba/pedestriansim/back/factory/PedestrianForcesFactory.java

@@ -5,6 +5,7 @@ import ar.edu.itba.pedestriansim.back.entity.PedestrianForces;
 import ar.edu.itba.pedestriansim.back.entity.force.ExponentialRepulsionForce;
 import ar.edu.itba.pedestriansim.back.entity.force.PedestrianFutureAdjustmentForce;
 import ar.edu.itba.pedestriansim.back.entity.force.ReactionDistanceDesireForce;
+import ar.edu.itba.pedestriansim.back.entity.force.ReactionDistanceDesireForce.FunctionType;
 import ar.edu.itba.pedestriansim.back.entity.force.SpringForceModel;
 
 public class PedestrianForcesFactory {
@@ -15,7 +16,7 @@ public class PedestrianForcesFactory {
 		forces.setWallRepulsionForceModel(new ExponentialRepulsionForce());
 		forces.setExternalForceRadiusThreshold(config.getExternalForceRadiusThreshold());
 		forces.setExternalForceThreshold(config.getExternalForceThreshold());
-		forces.setDesireForce(new ReactionDistanceDesireForce());
+		forces.setDesireForce(new ReactionDistanceDesireForce(FunctionType.SQ));
 		forces.setForceOnFuture(new PedestrianFutureAdjustmentForce(150, 10, 50));
 		forces.setCollisitionModel(new SpringForceModel());
 		return forces;

### 2014-10-18 src/main/java/ar/edu/itba/pedestriansim/back/logic/FuturePositionUpdaterComponent.java

@@ -18,6 +18,13 @@ public class FuturePositionUpdaterComponent extends PedestrianAreaStep {
 
 	private EulerMethod _eulerMethod = new EulerMethod();
 
+	private boolean _longitudinalNoise, _perpendicularNoise;
+
+	public FuturePositionUpdaterComponent(boolean longitudinalNoise, boolean perpendicularNoise) {
+		_longitudinalNoise = longitudinalNoise;
+		_perpendicularNoise = perpendicularNoise;
+	}
+
 	@Override
 	public void update(PedestrianArea input) {
 		for (Pedestrian subject : input.pedestrians()) {
@@ -27,10 +34,26 @@ public class FuturePositionUpdaterComponent extends PedestrianAreaStep {
 
 	private void update(PedestrianArea input, Pedestrian pedestrian) {
 		RigidBody futureBody = pedestrian.getFuture().getBody();
-		Vector2f forceOnFuture = futureBody.getAppliedForce();
+		Vector2f forceOnFuture = addNoise(futureBody.getAppliedForce());
 		float elapsedTimeInSeconds = input.timeStep().floatValue();
 		Vector2f deltaVelocity = _eulerMethod.deltaVelocity(futureBody, forceOnFuture, elapsedTimeInSeconds, velocityCache);
 		Vector2f deltaPosition = _eulerMethod.deltaPosition(futureBody, forceOnFuture, elapsedTimeInSeconds, positionCache);
 		futureBody.apply(deltaVelocity, deltaPosition);
+	}
+
+	private Vector2f addNoise(Vector2f vector) {
+		if (!_longitudinalNoise && !_perpendicularNoise) {
+			return vector;
+		}
+		Vector2f result = new Vector2f();
+		if (_perpendicularNoise) {
+			float sign = Math.signum((float) Math.random() - 0.5f);
+			result.add(vector.copy().add(sign * 90).scale(0.1f));
+		}
+		if (_longitudinalNoise) {
+			float p = (float) Math.random() / 5f - 0.1f;
+			result.add(vector.copy().scale(p));
+		}
+		return result.add(vector);
 	}
 }

### 2014-10-18 src/main/java/ar/edu/itba/pedestriansim/front/GUIPedestrianSim.java

@@ -33,6 +33,8 @@ import com.google.common.io.Closer;
 
 public class GUIPedestrianSim extends BasicGame {
 
+	private static final int FPS = 120;
+
 	public static final Logger logger = Logger.getLogger(GUIPedestrianSim.class);
 	public static final CommandParser parser;
 	static {
@@ -107,7 +109,7 @@ public class GUIPedestrianSim extends BasicGame {
 		_camera.setZoom(20f);
 		_renderer = new PedestrianAreaRenderer(_camera);
 		gc.setAlwaysRender(true);
-		gc.setTargetFrameRate(60);
+		gc.setTargetFrameRate(FPS);
 		gc.getInput().addKeyListener(new KeyHandler(_camera, _renderer, gc));
 	}
 

### 2014-10-18 src/main/java/ar/edu/itba/pedestriansim/front/UpdatePositionsFromFile.java

@@ -15,7 +15,7 @@ import com.google.common.collect.Maps;
 
 public class UpdatePositionsFromFile extends PedestrianAreaStep {
 	
-	private final int framesToSkip = 2;
+	private final int framesToSkip = 0;
 	private int frameIndex = 0;
 
 	private Supplier<DymaimcFileStep> _stepsSupplier;

### 2014-10-18 src/main/java/ar/edu/itba/pedestriansim/metric/CalculateMetricsFromFile.java

@@ -80,7 +80,7 @@ public class CalculateMetricsFromFile {
 		onSimulationEnd();
 	}
 
-	public boolean update(float delta) {
+	public boolean update(float dt) {
 		for (Metric metric : allMetrics) {
 			metric.onIterationStart();
 		}
@@ -96,14 +96,15 @@ public class CalculateMetricsFromFile {
 				StaticFileLine staticLinei = _staticPedestrianInfoById.get(linei.id());
 				StaticFileLine staticLinej = _staticPedestrianInfoById.get(linej.id());
 				float centerDist = linei.center().distance(linej.center());
-				if (centerDist <= staticLinei.radius() + staticLinej.radius()) {
+				float deltaDist = 0.1f;
+				if (centerDist <= staticLinei.radius() + staticLinej.radius() + deltaDist) {
 					for (CollitionMetric metric : collitionMetrics) {
-						metric.onCollition(delta, linei.id(), linej.id());
+						metric.onCollition(dt, linei.id(), linej.id());
 					}
 				}
 			}
 			for (SimpleMetric metric : simpleMetrics) {
-				metric.update(delta, linei, _staticPedestrianInfoById.get(linei.id()));
+				metric.update(dt, linei, _staticPedestrianInfoById.get(linei.id()));
 			}
 		}
 		for (Metric metric : allMetrics) {

### 2014-10-18 src/main/java/ar/edu/itba/pedestriansim/metric/component/CollitionCount.java

@@ -48,7 +48,7 @@ public class CollitionCount implements CollitionMetric {
 	}
 
 	private static class CollitionPair {
-		private final int _p1Id, _p2Id;
+		private final Integer _p1Id, _p2Id;
 
 		public CollitionPair(int p1Id, int p2Id) {
 			_p1Id = p1Id;
@@ -57,14 +57,13 @@ public class CollitionCount implements CollitionMetric {
 
 		@Override
 		public int hashCode() {
-
-			return Integer.hashCode(_p1Id) + Integer.hashCode(_p2Id);
+			return _p1Id.hashCode() + _p2Id.hashCode();
 		}
 
 		@Override
 		public boolean equals(Object obj) {
 			CollitionPair other = (CollitionPair) obj;
-			return _p1Id == other._p1Id && _p2Id == other._p2Id;
+			return _p1Id.intValue() == other._p1Id.intValue() && _p2Id.intValue() == other._p2Id.intValue();
 		}
 	}
 }

### 2014-10-19 src/main/java/ar/edu/itba/pedestriansim/back/PedestrianSimApp.java
cambiones menores

@@ -7,6 +7,8 @@ import java.io.IOException;
 import org.apache.log4j.Logger;
 
 import ar.edu.itba.command.CommandParser;
+import ar.edu.itba.common.rand.RandomGenerator;
+import ar.edu.itba.common.rand.UniformRandomGenerator;
 import ar.edu.itba.pedestriansim.back.config.CrossingConfig;
 import ar.edu.itba.pedestriansim.back.entity.PedestrianAppConfig;
 import ar.edu.itba.pedestriansim.back.entity.PedestrianArea;
@@ -24,6 +26,7 @@ import ar.edu.itba.pedestriansim.back.logic.RemovePedestriansOnTarget;
 import ar.edu.itba.pedestriansim.back.logic.SocialForceUpdaterComponent;
 
 import com.google.common.base.Function;
+import com.google.common.base.Optional;
 import com.google.common.base.Preconditions;
 import com.google.common.base.Predicate;
 import com.google.common.io.Closer;
@@ -65,7 +68,7 @@ public class PedestrianSimApp implements Runnable {
 		});
 		sim.onStep(new PedestrianAreaStateFileWriter(
 			fileCloser.register(newFileWriter(_config.staticfile())), 
-			fileCloser.register(newFileWriter(_config.dynamicfile())), 0.01f)
+			fileCloser.register(newFileWriter(_config.dynamicfile())), 0.02f)
 		);
 		if (FUTURE_FORCE_MODEL) {
 			configureFutureModelComponents(sim);
@@ -112,9 +115,12 @@ public class PedestrianSimApp implements Runnable {
 
 	private void configureFutureModelComponents(PedestrianSim sim) {
 		final PedestrianForces forces = new PedestrianForcesFactory().build(_config);
+		final float noiseP = 0.1f;
 		sim
 			.onStep(new FutureForceUpdaterComponent(forces))
-			.onStep(new FuturePositionUpdaterComponent(true, false))
+			.onStep(new FuturePositionUpdaterComponent(
+				Optional.of(new UniformRandomGenerator(-noiseP, noiseP)), Optional.<RandomGenerator>absent())
+			)
 			.onStep(new PedestrianForceUpdaterComponent(forces));
 	}
 	

### 2014-10-19 src/main/java/ar/edu/itba/pedestriansim/back/logic/FuturePositionUpdaterComponent.java

@@ -3,10 +3,13 @@ package ar.edu.itba.pedestriansim.back.logic;
 import org.apache.log4j.Logger;
 import org.newdawn.slick.geom.Vector2f;
 
+import ar.edu.itba.common.rand.RandomGenerator;
 import ar.edu.itba.pedestriansim.back.entity.Pedestrian;
 import ar.edu.itba.pedestriansim.back.entity.PedestrianArea;
 import ar.edu.itba.pedestriansim.back.entity.physics.EulerMethod;
 import ar.edu.itba.pedestriansim.back.entity.physics.RigidBody;
+
+import com.google.common.base.Optional;
 
 public class FuturePositionUpdaterComponent extends PedestrianAreaStep {
 
@@ -18,9 +21,9 @@ public class FuturePositionUpdaterComponent extends PedestrianAreaStep {
 
 	private EulerMethod _eulerMethod = new EulerMethod();
 
-	private boolean _longitudinalNoise, _perpendicularNoise;
+	private Optional<? extends RandomGenerator> _longitudinalNoise, _perpendicularNoise;
 
-	public FuturePositionUpdaterComponent(boolean longitudinalNoise, boolean perpendicularNoise) {
+	public FuturePositionUpdaterComponent(Optional<? extends RandomGenerator> longitudinalNoise, Optional<? extends RandomGenerator> perpendicularNoise) {
 		_longitudinalNoise = longitudinalNoise;
 		_perpendicularNoise = perpendicularNoise;
 	}
@@ -42,17 +45,16 @@ public class FuturePositionUpdaterComponent extends PedestrianAreaStep {
 	}
 
 	private Vector2f addNoise(Vector2f vector) {
-		if (!_longitudinalNoise && !_perpendicularNoise) {
+		if (!_longitudinalNoise.isPresent() && !_perpendicularNoise.isPresent()) {
 			return vector;
 		}
 		Vector2f result = new Vector2f();
-		if (_perpendicularNoise) {
+		if (_perpendicularNoise.isPresent()) {
 			float sign = Math.signum((float) Math.random() - 0.5f);
-			result.add(vector.copy().add(sign * 90).scale(0.1f));
+			result.add(vector.copy().add(sign * 90).scale(_perpendicularNoise.get().generate()));
 		}
-		if (_longitudinalNoise) {
-			float p = (float) Math.random() / 5f - 0.1f;
-			result.add(vector.copy().scale(p));
[…]

### 2014-10-19 src/main/java/ar/edu/itba/pedestriansim/front/GUIPedestrianSim.java

@@ -33,7 +33,7 @@ import com.google.common.io.Closer;
 
 public class GUIPedestrianSim extends BasicGame {
 
-	private static final int FPS = 120;
+	private static final int FPS = 160;
 
 	public static final Logger logger = Logger.getLogger(GUIPedestrianSim.class);
 	public static final CommandParser parser;

### 2014-10-19 src/main/java/ar/edu/itba/pedestriansim/front/UpdatePositionsFromFile.java

@@ -48,6 +48,7 @@ public class UpdatePositionsFromFile extends PedestrianAreaStep {
 		for (PedestrianDynamicLineInfo dynamicInfo : step.pedestriansInfo()) {
 			StaticFileLine staticInfo = staticInfoById.get(dynamicInfo.id());
 			Pedestrian p = new Pedestrian(staticInfo.id(), staticInfo.team(), new RigidBody(staticInfo.mass(), dynamicInfo.center(), staticInfo.radius()));
+			p.getBody().getVelocity().set(dynamicInfo.velocity());
 			p.pedestrianRepulsionForceValues().setAlpha(staticInfo.pedestrianAlpha()).setBeta(staticInfo.pedestrianBeta());
 			input.addPedestrian(p);
 			p.getFuture().getBody().setCenter(dynamicInfo.futureCenter());

### 2014-10-19 src/main/java/ar/edu/itba/pedestriansim/metric/RunsGenerator.java

@@ -80,7 +80,7 @@ public class RunsGenerator {
 						}
 
 						private String buildFileId(float threshold, float alpha, Range<Float> beta) {
-							return "b=" + beta + "-a=" + alpha + "-t=" + threshold;
+							return "b=" + beta.lowerEndpoint() + "-a=" + alpha + "-t=" + threshold;
 						}
 					});
 				}

### 2014-10-19 src/main/java/ar/edu/itba/pedestriansim/metric/component/AverageTurnedAngle.java

@@ -33,7 +33,11 @@ public class AverageTurnedAngle implements SimpleMetric {
 			value.velocity.set(pedestrian.velocity());
 		} else {
 			float deltaAngle = (float) (value.velocity.getTheta() - pedestrian.velocity().getTheta());
-			value.angle += Math.abs(deltaAngle);
+			deltaAngle = Math.abs(deltaAngle);
+			if (deltaAngle > 180) {
+				deltaAngle = 360 - deltaAngle;
+			}
+			value.angle += deltaAngle;
 			value.velocity.set(pedestrian.velocity());
 		}
 	}
@@ -58,8 +62,13 @@ public class AverageTurnedAngle implements SimpleMetric {
 	}
 
 	private static class PedestrianTurnedAngle {
-		Vector2f velocity = new Vector2f();
+		final Vector2f velocity = new Vector2f();
 		float angle = 0;
+		
+		@Override
+		public String toString() {
+			return angle + "";
+		}
 	}
 
 	@Override

### 2014-10-20 doc/informe/paper.tex
agrego requerimientos de PF. Mejoro/completo varios aspectos del informe.

@@
 
-%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.1.1 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
 \documentclass[english]{article}
-\usepackage[T1]{fontenc}
 \usepackage[latin9]{inputenc}
@@
 
+%% Because html converters don't know tabularnewline
+\providecommand{\tabularnewline}{\\}
+
 \makeatother
 
-\usepackage[english]{babel}
+\usepackage{babel}
 \begin{document}
@@
 
-\author{Daniel Parisi, Agustin Marseillan, Castiglione Gonzalo}
+\author{Castiglione Gonzalo, Agustin Marseillan, Daniel Parisi}
 \maketitle
 \begin{abstract}
-En este paper se presenta un nuevo método para simular peatones virtuales
+En este paper se presenta un nuevo método para simular peatónes virtuales
 basado en el modelo de la fuerza social. En el modelo presentado,
@@
 
-\section{Introduccion}
+\section{Introducción}
 
@@
 El transito de personas es un factor de suma importancia en el análisis
-y diseño de instalaciones tales como edificios públicos, peatonales,
+y diseño de instalaciones tales como edificios públicos, peatónales,
 estaciones de trenes, entre otros.
@@
 
-// Decir porque una simulación de peatones es útil para estas situaciones.\\
+// Decir porque una simulación de peatónes es útil para estas situaciones.\\
 
-Analizar estructuras de transito de peatones usando los cambios propuestos
+Analizar estructuras de transito de peatónes usando los cambios propuestos
 para el modelo de la fuerza social. Implementar una interfaz gráfica
@@
 
-\section{Modelo de agentes}
+\section{Formulacíon del modelo}
 
-El actual modelo se encuentra definido uncamente por peatones. Estos
-se encuentran definidos por: 
+A continuación se presentan los efectos que van a determinar el movimiento
+de un peatón:
+\begin{enumerate}
+\item El peatón desea alcanzar su objetivo a largo plazo de la manera mas
+cómoda posible. Por lo tanto va a intentar alcanzarlo sin tener que
+tomar desvios innecesarios, por ejemplo el camino mas corto.
+\item El movimiento del peatón se ve influenciado por otros peatones. Dependiendo
+de la distancia con la que se encuentre de otro peatón y la trayectoria
+que se pueda predecir de este último, un peatón va a sentir la necesidad
+de realizar cambios a la ruta deseada a fin de evitar colisiones.
+Es por este efecto que el peatón va a necesitar recalcular su trayectoria
+según nuevos peatones aparecen en su campo de visión.
+\item La velocidad de movimiento se ver influenciada según necesidades o
+estados de ánimo del peatón en cuestión.
+\end{enumerate}
+Para representar los efectos presentados, un peatón se encuentra definido
+como según se especifica a continuación: 
 \begin{itemize}
@@
 
-Representa el área física que ocupa el peatón. El radio del círculo
-es generado aleatoriamente con el fin de representar peatones diferentes.
+Representa el área física y espacio personal ocupado. El radio del
+círculo es generado aleatoriamente a fin de representar peatónes diferentes.
 El rango de valores se distribuye uniformemente en el intervalo $[0.25,0.29]$
@@
 
-Se represa por por un segmento de recta, al tocarse, se considera
-que el objetivo fue cumplido. Se permite la definición de múltiples
-objetivos, en cuyo caso, se deben cumplir todos de manera secuencial
-según el orden en que fueron especificados.
+Representado por un área estática. Al ser tocada, se considera al
+objetivo como cumplido. Se permite la definición de múltiples objetivos,
+en cuyo caso, se deben cumplir todos de manera secuencial según el
+orden en que fueron especificados.
 
-\item Posición objetivo a corto plazo
+\item Objetivo a corto plazo
 
-Llamado Future, representa un punto a corta distancia del peatón,
-que debe ser alcanzado. El seguir este punto garantiza que se va a
-cumplir el objetivo a largo plazo, aunque podría recorrerse un camino
-no óptimo en cuanto a distancia recorrida. Este punto es un punto
-móvil y se puede aplicar fuerzas sobre el. La masa de este punto fue
-definida fija con un valor de $1$ $[kg]$.
+Llamado Future, representa un punto a una cierta distancia del centro
+del area circular. Este es un objetivo dinámico.
+
+Se encuentra representado por una masa definida fija con un valor
+de $1$ $[kg]$. No es colisionable.
 
@@
 
-Con el fin de representar peatones que puedan estar apurados o tranquilos,
-se definió la velocidad máxima deseada de un peatón de manera aleatoria.
-El rango de valores se encuentra definido en el intervalo $[1,1.6]$
+Representa la velocidad a la que el peatón desea avanzar. Este valor
+es un valor aleatorio ya que definido en el intervalo $[1.2,1.4]$
 $[m/s]$.
@@
 
-Representa la distancia a la cual va a tratar de posicionar de sí
-mismo un peatón su propio future. Una mayor distancia representa un
-peatón que reacciona más rápido a una posible colisión.
+Representa la distancia a la cual se va a tratar de posicionar de
+sí mismo un peatón su propio future. Una mayor distancia representa
+un peatón que reacciona antes frente a una posible colisión.
 
 \end{itemize}
+\vspace{1cm}
+
 En la siguiente imagen se puede observar de manera gráfica la descripción
@@
 \begin{figure}[H]
-\begin{centering}
-\includegraphics[scale=0.5]{pedestrian-top}\caption{Vista superior de un peaton}
-
-\par\end{centering}
-
+\centering{}\includegraphics[scale=0.5]{pedestrian-top}\protect\caption{Vista superior de un peatón}
 \end{figure}
 
-// FALTA ESPECIFICAR:
-
-// i representa un peaton e i\textquoteright{} representa el future
-del peaton
-
-// que se usa Euler para el calculo del dx de cada cuerpo
-
-// el dt usado
+Se reserva el uso de las letras para repersentar a un peatón y versión
+con tilde para representar su future en el resto del documento.\\
 
@@
 
-Cada peatón en la simulación posee un objetivo a largo plazo que sea
-desea que alcance. Para asegurar que esto se cumpla, se trata siempre
-de mantener su future (objetivo a corto plazo) alineado con el camino
-más óptimo hacia su objetivo. Sin embargo, pueden darse casos en donde
-exista uno o más peatones en el camino, obligando a tener que buscar
-rutas alternativas. Es en estas circunstancias en donde el objetivo
-a corto plazo va a cambiar su dirección según corresponda.
+Cada peatón en la simulación posee como objetivo final, alcanzar el
+objetivo a largo plazo. Para asegurar esto, se trata siempre de mantener
+al future (objetivo a corto plazo) alineado con el camino más corto
+hacia el objetivo final. Sin embargo, pueden darse casos en donde
+existan otros peatónes en esta trayectoria, obligando a tener que
+utilizar rutas alternativas. Es en estas circunstancias es cuando
+el objetivo a corto plazo va a ser trasladado según la situación.
 
-El movimiento de los peatones se realiza de manera sincrónica y se
-calcula en cuatro etapas: 
+El movimiento de los peatónes se calcula en cuatro etapas: 
 \begin{enumerate}
@@
 \item Cálculo de la fuerza sobre cada peatón. 
-\item Actualización de la posicion de cada peatón. \\
+\item Actualización de la posición de cada peatón. \\
 
@@
 cada uno de los futures existentes debido a la existencia de otros
-peatones. Esta se realiza sólo cuando la distancia entre el peatón
+peatónes. Esta se realiza sólo cuando la distancia entre el peatón
 y su future se encuentra por encima de cierto valor. Esto es así ya
-que a altos niveles de densidad de personas. Uno ya no intenta moverse
-ya que simplemente es arrastrado por la masa de gente. \textbf{(verificar
-si es correcta esta última frase)}
+que a altos niveles de densidad de personas. Uno ya no puede moverse
+y simplemente es arrastrado por la masa de gente.
 
 En el caso contrario, cuando que un peatón se encuentra habilitado
-para moverse, se realiza un filtro de todos aquellos peatones que
-se encuentran a sus espaldas, ya que estos no son casos que afectam
+para moverse, se realiza un filtro de todos aquellos peatónes que
+se encuentran a sus espaldas, ya que estos no son casos que afectan
 la trayectoria de la persona. La condición que debe cumplirse para
@@
 \[
-v=normal(i,center.target.i)
+A=(Ax,\, Ay)=i
 \]
 \[
-v_{x1x0}=v_{x1}-v_{x0}
+B=(Bx,\, By)=A+rotation(\overrightarrow{ii'},\,\pi/2)
 \]
 \[
-v_{x1x0}.x*(i.y-v_{x0}.y)-v_{x1x0}.y*(i.x-v_{x0}.x)>0
+C=(Cx,\, Cy)=j
+\]
+Luego, se debe cumplir que:
+
+\[
+(Bx-Ax)*(Cy-Ay)-(By-Ay)*(Cx-Ax)>0
 \]
 
-Una vez filtrado los peatones, simplemente se calcula por cada future
+Una vez filtrados los peatónes, simplemente se calcula por cada future
 restante, la fuerza de repulsión entre estos. Este se realiza utilizando
@@
 \[
-F_{i',j'}=\alpha e^{-dist(i',j')/\beta}
+F_{ext}(i)=\sum_{j}F_{i',j'}=\sum_{j}\alpha e^{-dist(i',j')/\beta}
 \]
@@
 en donde $\alpha$ y $\beta$ son constantes predefinidas y fijas.
-Los valores que se usaron son $?$ y $?$ respectivamente. Esto produce
-que los peatones tienda siempre a alejarse de grandes multitudes más
-de lo que aleja de una sola persona. Si la suma de todas las fuerzas
-ejercidas sobre todos los demás futures $j\lyxmathsym{\textquoteright}$
-al future $i\lyxmathsym{\textquoteright}$ es menor que cierto umbral,
-entonces se desprecia esta fuerza y el future $i\lyxmathsym{\textquoteright}$
-simplemente es posicionado sobre la recta que une al peatón $i$ con
-su objetivo a largo plazo a distancia que indique la distancia de
-reacción del peatón.
+Los valores que se usaron son $\alpha=800$ y $\beta=[0.65,\,085]$
+con distribución uniforme. Luego de calculadado $F_{ext}$, si su
+valor es menor que cierto umbral, entonces se desprecia esta fuerza
+y el future $i\lyxmathsym{\textquoteright}$ simplemente se alinea
+con el objetivo estático a distancia que indique la distancia de reacción
+del peatón. Caso contrario, cuando la contribución de las fuerzas
+externas debe considerarse, se suma la contribución del peatón $i$
+sobre su future para ajustarlo según su objetivo estático. Esta fuerza
+se calcula a usando la formula del resorte. Los extremos de este resorte
+se encuentran en el punto a distancia ``distancia de reaccion''
+sobre el segmento de recta que une al peatón $i$ con su objetivo
+estático y la posición del future $i'$.
+
+A modo ilustrativo, se muestra en la figura 2 como la trayectoria
+del peatón $i$ es afectada por la del peatón $j$ a través de $F(i',\, j')$
+y es alineada al objetivo con $F(i,\, i')$
 
 \begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{pedestrian-top-forces}\caption{Fuerzas que actúan sobre el Future $i'$}
+\centering{}\includegraphics[scale=0.5]{pedestrian-top-forces}\protect\caption{Fuerzas que actúan sobre el Future $i'$}
 \end{figure}
 
+\begin{enumerate}
 \item Actualización de la posición de cada future.
@@
 En esta etapa, simplemente se actualiza la posición de cada future
-según el cálculo de la fuerza aplicada en la etapa previa. Este cálculo
-se realiza utilizando las fórmulas Eulerianas.
+según el cálculo de la fuerza $F$ aplicada en la etapa previa. Este
+cálculo se realiza utilizando las fórmulas de Euler.
+
+Para romper con situaciones con altos grados de simetría, se agrega
+ruido $P=10\%$ sobre $F$. Para esto, se aplican dos formas de ruido:
+\begin{itemize}
+\item Ruido longitudinal:
+
+\begin{itemize}
+\item Se toma un valor $p$ según una distribución aleatoria uniforme en
+el intervalo $[-P,\, P]$ y se calcula: $FL_{i'}=F_{i'}*p$
+\end{itemize}
+\item Ruido angular:
+
+\begin{itemize}
+\item Se toma $sgn=\{-1,\,1\}$ utilizando una distribución uniforme y $p$
+en $[-P,\, P]$ con la misma distribución. Luego se calcula: $FA_{i'}=rotation(F_{i'},\,\pi*sgn)*p$
+\end{itemize}
+\end{itemize}
+
+Por último se toma $F'_{i'}=F_{i'}+FL_{i'}+FA_{i'}$ y de aplican
+las ecuaciones de movimiento.
 
@@
 
-\item Validación del modelo
+\end{enumerate}
+\end{enumerate}
+
+\section{Validación del modelo }
+
+Los resultados obtenidos fueron comparados utilizando el modelo ``Social
+Force Model'' utilizando los valores propuestos por Dirk Helbing
+{[}2{]}. Los escenarios de prueba fueron cruce y hallway.
+
+Los resultados fueron cuantificados utilizando las siguientes métricas:
+\begin{enumerate}
+\item Cantidad total de colisiones
+
+TODO: (como se calcula)
+
+\item Duración promedio de las coliciones
+
+TODO: (como se calcula)
+
+\item Velocidad promedio de viaje
+
+TODO: (como se calcula)
+
+\item Tiempo promedio de viaje
+
+TODO: (como se calcula)
+
+\item Promedio de la distancia recorrida
+
+TODO: (como se calcula)
+
+\item Ángulo giro promedio
+
+TODO: (como se calcula)
+
+\end{enumerate}
+\vspace{1cm}
+En la tabla a continuación se presentan las mediciones de las métricas
+utilizando un total de $10$ corridas:
+
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+Valores & 1 & 2 & 3 & 4 & 5 & 6\tabularnewline
+\hline 
+\hline 
+$\alpha=800,\,\beta=[0.65,\,0.85]$ & (1.800, 0.748)  & (34.600, 8.333)  & (1.024, 0.016)  & (1.910, 0.022)  & (2.392, 0.005)  & (111.062, 19.122)\tabularnewline
+\hline 
+$\alpha=2000,\,\beta=0.08$ & (5.333, 2.625) & (12.333, 8.340)  & (1.052, 0.003)  & (1.876, 0.003)  & (2.391, 0.002)  & (106.185, 13.778)\tabularnewline
+\hline 
+\end{tabular}
 
@@
 
-\item Conclusiones
+\section{Conclusiones}
 
@@
 
-\end{enumerate}
 \pagebreak{}
-\begin{enumerate}
-\item Referencias
 
-{[}1{]}... Karamouzas?
-
-{[}2{]}...\end{enumerate}
+\section{Referencias}
+\begin{itemize}
+\item {[}1{]} ... Karamouzas ...
+\item {[}2{]} ...Helbing ...\end{itemize}
 

### 2014-11-19 doc/informe/paper.tex
actuazo tex

@@
 \documentclass[english]{article}
+\usepackage[T1]{fontenc}
 \usepackage[latin9]{inputenc}
+\usepackage[a4paper]{geometry}
+\geometry{verbose,tmargin=1in,bmargin=1in,headheight=1in,headsep=1in}
 \usepackage{float}
-\usepackage{amstext}
+\usepackage{amsmath}
 \usepackage{graphicx}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
-\newcommand{\lyxmathsym}[1]{\ifmmode\begingroup\def\b@ld{bold}
-  \text{\ifx\math@version\b@ld\bfseries\fi#1}\endgroup\else#1\fi}
-
 %% Because html converters don't know tabularnewline
@@
 
-\title{A Pedestrian Simulation }
+\title{A Pedestrian Simulationnnnnn}
+
+\title{Future Virtual Particle Force Model}
 
@@
 \begin{abstract}
-En este paper se presenta un nuevo método para simular peatónes virtuales
-basado en el modelo de la fuerza social. En el modelo presentado,
-cada peatón posee un punto movil frente a el y camina siempre hasta
-este. Este punto representa un objetivo a corto plazo que se debe
-cumplir. Cada peatón se encarga de mover este punto según a donde
-necesite llegar. 
+We present a novel method to simulate virtual pedestrians based on
+the social force model. In our model, each pedestrian has a point
+in front of him called Future Virtual Particle (FVP) which represents
+where the pedestrian is headed to and at what speed.
 \end{abstract}
@@
 
-pedestrian, collision avoidance, future, force model
+pedestrian, collision avoidance, future virtual particle, force model
 
@@
 
-\section{Introducción}
+\section{Introduction}
 
-// Daniel tiene ya preparada una introducción\\
+\subsection{Motivacion y antecedentes}
 
-El transito de personas es un factor de suma importancia en el análisis
-y diseño de instalaciones tales como edificios públicos, peatónales,
-estaciones de trenes, entre otros.
+Navigation of biological, sinthetic or virtual agents is a relevant
+problem in several fields such as pedestrian dynamics, moving robots
+and animation of characters for videogames and motion pictures.
 
-// Hace mucho tiempo que se viene estudiando a las personas en grupo
-y se sabe que
+Modelling and simulating the displacement of agents througth arbitrarily
+complex enviroments may be stated in an hierachical structure of mecahnisms
+depending mianly on the distance from the agent. This level has been
+named, from closer to further, as operational (walking, lowst level
+physical-computaitnal model for displacement), tactical (wayfinding,
+route chocie) and strategic (general activity planning) {[}Hoogonen
+and Bovy 2004{]}. These levels are not independient, factors affecting
+one level may impact in the following and vice versa, for example,
+the route choice may vary due to congestion of agents producing from
+previous route chice and walking behavior. Also, obstacles can impact
+on the operational level or tactical level depending on the particular
+geometry of the enviroment. The particular mechanism we want to address
+is the avoidance of obstacles being fixed or moving (another agent)
+which involves operational and tactical aspects of the navigation.
 
-// Existen efectos de comportamiento colectivos de auto organización
-tales como cuellos de botellas, formaciones en filas, bloqueos.
+A general approach is to take an existing operational model and equip
+it with a higher level model which allows better and smoother collision
+avoidance behavior. Exisiting low level models can be taken from pedestrian
+dynamics field and in general this models can be classified into rule
+based and force based, discrete and continuous space description,
+etc. {[}Schadschneider 2009{]}.
 
-// Decir porque una simulación de peatónes es útil para estas situaciones.\\
+A famous example of continuos and force based model is the Social
+Force Model {[}Helbing 1995, 2000{]}. In this model the dynamic for
+virtual pedestrians is derived from the Newton equation\textquoteright s
+considering the total force exceterd over each agent is the result
+of three forces: Contact, Social and Driving Force. While the driving
+force points towards the final objective of each pedestrian, the social
+force is repulsive and acts as a kind of collision avoidance force.
+However this social force term introduce several artefacts in some
+configurations {[}see for example Lakoba et al. 2005, Parisi et al
+2009{]}.
 
-Analizar estructuras de transito de peatónes usando los cambios propuestos
-para el modelo de la fuerza social. Implementar una interfaz gráfica
-para poder visualizar los resultados de cambiar el modelo y cada uno
-de los parámetros
+Cellular automata models make use of a spacial grid, which can be
+occuied or empty, along with a set of rules determining the evolution
+and conflict resolution of virtual pedestrians moving over the cells
+of the grid. An emblematic celluar automata model is the one proposed
+by Kirchner and Schadschneider {[}2002{]}.
 
-\section{Formulacíon del modelo}
+It have been also proposed hibrid models such as the Contractile Particle
+Model {[}Baglietto and Parisi, 2011{]} in which a continuos description
+of the space is combined with a set of simple rules governig the dynamcis
+of the system.
 
-A continuación se presentan los efectos que van a determinar el movimiento
-de un peatón:
+The basic operational model as the ones described above can be improved
+if higher level mechanisms were added to manage more complex issues
+as eficient avoidance. Some recent examples can be found in the literature.
+
+Karamouzas et al. (2009) proposed a method for collision avoidance
+modifying the social force model, basically, replacing the social
+force term by a new \textquotedblleft evasive\textquotedblright{}
+force which tends to avoid future collisions. The magnitud and direction
+of this force is calculaed considering the predictions of these possible
+collisions.
+
+Kretz et al. 2011 have arrised the point that the key ingredient in
+social force model is the driving force instead of interaction force,
+so in this work the authors propose a method for dinamically adjust
+the desired velocity following the gradient of a field given by a
+time map, in other words, the desired velocity is choosen as the quickest
+path to the objective taking into account the geometry and other agents
+(collision, congestions, jams, etc.). Also mounted on the SFM, Moussaïd
+et al. {[}2011{]} have presented a model using a \textquotedblleft cognitive
+heuristics\textquotedblright{} to determine the norm and direction
+of the desired velocity for each agent dinamically during the evolution
+of the system.
+
+In the same line, we also proposed that the navigation capacity of
+virtual agents should be concentrated in the on-line decision of the
+desired velocity. Similar to this approach, we postulate a new method
+derived from the methods used in robotics/artificial inteligence\dots{}
+The method deals with two aspects of the navigation mechanism. The
+first one is geometrical problem of finding intermediate goals when
+the final goal is not visible from the current position of the virtual
+agent. The second aspect is the local avoidance of other agents, which
+is performed via a reactive mechanism inspired in (robot navigation
+/ artificial inteligence) aproaches ¿?¿?¿\dots ..?¿?¿ {[} Ref.???
+??? {]}.
+
+The method proposed could be mounted on different basic displacement
+models like de SFM or the CPM, in the present work we have chosen
+the first one.
+
+\subsection{Social Force Model}
+
+En el Social Force Model cada peatón se rige por una serie de reglas
+presentads por Helbing en sus paper {[}Helbing 1995, 2000{]}. A partir
+de estas reglas, proupso un modelo en donde cada peatón sufre una
+fuerza de deseo que lo provoca a acercarse hacia su objetivo y una
+fuerza de repulsión contra cada uno de los demas peatones. Junto a
+estas dos, existe la fuerza de contacto producto del conectacto físico.
+\\
+
+Cada una de las fuerzas en el modelo se define usando las siguientes
+fórmulas:\\
+
+Fuerza de contacto (Granular):
+
+\[
+F_{G_{i}}=\sum_{j=1,j\ne i}^{N_{P}}[-\epsilon_{ij}k_{n}e_{ij}^{n}+v_{ij}^{t}\epsilon_{ij}k_{t}e_{ij}^{t}]\, g(\epsilon_{ij})
+\]
+
+En donde: $\epsilon_{ij}=r_{ij}-(R_{i}+R_{j})$
+
+\begin{figure}[H]
+\begin{centering}
+\includegraphics[scale=0.4]{sfm/ganular}
+\par\end{centering}
+
+\protect\caption{Fuerza de contact granular}
+
+\end{figure}
+
+\vspace{1cm}
+
+Fuerza social:
+\[
+F_{S_{i}}=\sum_{j=1,j\ne i}^{N_{P}}Aexp(-\frac{\epsilon_{ij}}{B})\, e_{ij}^{n}
+\]
+
+\vspace{1cm}
+
+\begin{figure}[H]
+\begin{centering}
+\includegraphics[scale=0.6]{sfm/sf}
+\par\end{centering}
+
+\protect\caption{Fuerza social}
+\end{figure}
+
+Fuerza de deseo:
+
+\[
+F_{D_{i}}=m_{i}\frac{v_{di}e_{i}-v_{i}}{\tau}
+\]
+
+\begin{figure}[H]
+\begin{centering}
+\includegraphics[scale=0.7]{sfm/drivingforce}
+\par\end{centering}
+
+\protect\caption{Driving force}
+\end{figure}
+
+\vspace{1cm}
+
+Luego, se calcula $F_{i}=F_{G_{i}}+F_{S_{i}}+F_{D_{i}}$
+
+En donde los parametros se encuentran definidos con lo siguientes
+valores: $A=2000\,[N]$, $B=0.08\,[m]$, $k_{n}=1.2\,10^{5}\,[\frac{N}{m}]$,
+$k_{t}=2.4\,10^{5}\,[\frac{kg}{m/s}]$ y $\tau=0.5\,[s]$.
+
+\subsection{Future Vector Particle Model}
+
+Debido a que el SFM presenta una fuerza ficticia sobre el peatón,
+se generan artificios en la navegación ante la presencia de grandes
+cantidades de peatones. \{...\}
+
+Frente a esto se presenta un nuevo modelo
+
+// no reproduce valores de Caudal Específico ni Diagrama Fundamental
+
+// To do: explicar nuestros aportes al modelo, observaciones sobre
+el SFM\\
+
+\section{The Model}
+
+\subsection{Hipotesis}
+
+In the following the main effects that determine the motion of a pedestrian
+will be introduced: (agregar que son las mismas hipotesis que presenta
+Helbin en su paper)
 \begin{enumerate}
-\item El peatón desea alcanzar su objetivo a largo plazo de la manera mas
-cómoda posible. Por lo tanto va a intentar alcanzarlo sin tener que
-tomar desvios innecesarios, por ejemplo el camino mas corto.
-\item El movimiento del peatón se ve influenciado por otros peatones. Dependiendo
-de la distancia con la que se encuentre de otro peatón y la trayectoria
-que se pueda predecir de este último, un peatón va a sentir la necesidad
-de realizar cambios a la ruta deseada a fin de evitar colisiones.
-Es por este efecto que el peatón va a necesitar recalcular su trayectoria
-según nuevos peatones aparecen en su campo de visión.
-\item La velocidad de movimiento se ver influenciada según necesidades o
-estados de ánimo del peatón en cuestión.
+\item The pedestrian wants to reach to his goal in the shortest possible
+path.
+\item The pedestrian's movement is influenced by other pedestrians. Depending
+on the distance between the two of them and the predicted trayectory,
+the pedestrian will feel the need to change his route to be able to
+avoid the other pedestrian. It is because of this effect that pedestrians
+will need to recalculate their route as new pedestrians get closer
+to them.
+\item Movement speed will be influenced by needs.
 \end{enumerate}
-Para representar los efectos presentados, un peatón se encuentra definido
-como según se especifica a continuación: 
+
+\subsection{??}
+
+A pedestrian is defined as follows:
 \begin{itemize}
-\item Area circular
+\item Circular shape
 
-Representa el área física y espacio personal ocupado. El radio del
-círculo es generado aleatoriamente a fin de representar peatónes diferentes.
-El rango de valores se distribuye uniformemente en el intervalo $[0.25,0.29]$
-$[cm]$.
+Represents the space that this pedestrian occupies. Circle's radio
+is generated randomly to represent different types of pedestrians.
+The range of values is distributed uniformly in $[0.25,0.29]$$[cm]$.
 
-\item Objetivo a largo plazo
+\item Long term objective
 
-Representado por un área estática. Al ser tocada, se considera al
-objetivo como cumplido. Se permite la definición de múltiples objetivos,
-en cuyo caso, se deben cumplir todos de manera secuencial según el
-orden en que fueron especificados.
+Represented by a static area. When it is touched by a pedestrian,
+it is considered as accomplished. Multiple objectives can by defined
+in a list, in this case, each of them must be reached in order.
 
+\item Short term objective
 \item Objetivo a corto plazo
 
-Llamado Future, representa un punto a una cierta distancia del centro
-del area circular. Este es un objetivo dinámico.
+Called FVP, it represents a point at a relative distance from the
+pedestrian's center. It's a dynamic objective.
 
-Se encuentra representado por una masa definida fija con un valor
-de $1$ $[kg]$. No es colisionable.
+It is defined as a$1$ $[kg]$ mass. Not collisionable.
 
-\item Velocidad objetivo
+\item Desired speed
 
-Representa la velocidad a la que el peatón desea avanzar. Este valor
-es un valor aleatorio ya que definido en el intervalo $[1.2,1.4]$
-$[m/s]$.
+Represents the speed the pedestrian would walk if he was alone. Varies
+randomly between$[1.2,1.4]$ $[m/s]$.
 
-\item Distancia de reacción
+\item Reaction distance
 
-Representa la distancia a la cual se va a tratar de posicionar de
-sí mismo un peatón su propio future. Una mayor distancia representa
-un peatón que reacciona antes frente a una posible colisión.
+Maximum distance between a pedestrian and his FVP, it represents the
+distance at which a real pedestrian would react from an obstacle.
 
@@
 
-En la siguiente imagen se puede observar de manera gráfica la descripción
-de un peatón:
+Fig 1: Pedestrian and his FVP.
 
 \begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{pedestrian-top}\protect\caption{Vista superior de un peatón}
+\centering{}\includegraphics[scale=0.5]{pedestrian-top}\protect\caption{Pedestrian top view}
 \end{figure}
 
-Se reserva el uso de las letras para repersentar a un peatón y versión
-con tilde para representar su future en el resto del documento.\\
+In the document, we will call pedestrians with a letter and FVP of
+pedestrian x will be called x'.\\
 
-\section{Funcionamiento}
+\subsection{Implementation}
 
-Cada peatón en la simulación posee como objetivo final, alcanzar el
-objetivo a largo plazo. Para asegurar esto, se trata siempre de mantener
-al future (objetivo a corto plazo) alineado con el camino más corto
-hacia el objetivo final. Sin embargo, pueden darse casos en donde
-existan otros peatónes en esta trayectoria, obligando a tener que
-utilizar rutas alternativas. Es en estas circunstancias es cuando
-el objetivo a corto plazo va a ser trasladado según la situación.
+Each pedestrian has to reach the long term objective at some point,
+to ensure this, the FVP always feels the need to be aligned with the
+shortest path to the long term objective. On the other hand, there
+are sometimes obstacles in the way, which will make this impossible,
+in this cases, the route will have to change depending on the situation.
 
-El movimiento de los peatónes se calcula en cuatro etapas: 
+The pedestrian movement is calculated in four steps:
 \begin{enumerate}
-\item Cálculo de la fuerza sobre sobre cada future. 
-\item Actualización de la posición de cada future. 
-\item Cálculo de la fuerza sobre cada peatón. 
-\item Actualización de la posición de cada peatón. \\
+\item Calculate forces for each FVP.
+\item Update positions for each FVP.
+\item Calculate forces for each pedestrian.
+\item Update positions for each pedestrian.\\
 
 \end{enumerate}
-En donde, cada etapa se define de la siguiente manera:
+Each step is defined as follows:
 \begin{enumerate}
-\item Cálculo de la fuerza sobre sobre cada future.
+\item FVP force calculation.
 
-En esta etapa, lo que se va a hacer es calcular la fuerza que sufre
-cada uno de los futures existentes debido a la existencia de otros
-peatónes. Esta se realiza sólo cuando la distancia entre el peatón
-y su future se encuentra por encima de cierto valor. Esto es así ya
-que a altos niveles de densidad de personas. Uno ya no puede moverse
-y simplemente es arrastrado por la masa de gente.
-
-En el caso contrario, cuando que un peatón se encuentra habilitado
-para moverse, se realiza un filtro de todos aquellos peatónes que
-se encuentran a sus espaldas, ya que estos no son casos que afectan
-la trayectoria de la persona. La condición que debe cumplirse para
-considerar un peatón $j$ como detrás del peatón $i$ es:
+In each iteration, the FVP from pedestrian $i$ feels a force generated
+by the other pedestrians and FVPs. First of all, we filter de pedestrians
+$j$ who are not in the range of sight of pedestrian $i$ as follows:
 
 \[
-A=(Ax,\, Ay)=i
+k=i+\begin{pmatrix}0 & -1\\
+1 & 0
+\end{pmatrix}\overrightarrow{ii'}
 \]
-\[
-B=(Bx,\, By)=A+rotation(\overrightarrow{ii'},\,\pi/2)
-\]
-\[
-C=(Cx,\, Cy)=j
-\]
-Luego, se debe cumplir que:
+The following must be valid:
 
 \[
-(Bx-Ax)*(Cy-Ay)-(By-Ay)*(Cx-Ax)>0
+(k_{x}-i_{x})*(j_{y}-i_{y})-(k_{y}-i_{y})*(j_{x}-i_{x})>0
 \]
 
-Una vez filtrados los peatónes, simplemente se calcula por cada future
-restante, la fuerza de repulsión entre estos. Este se realiza utilizando
-la fórmula:
+Once filtered, the force is calculated for every other FVP. The repulsion
+force between i' and j' is defined as follows:
 
@@
 
-en donde $\alpha$ y $\beta$ son constantes predefinidas y fijas.
-Los valores que se usaron son $\alpha=800$ y $\beta=[0.65,\,085]$
-con distribución uniforme. Luego de calculadado $F_{ext}$, si su
-valor es menor que cierto umbral, entonces se desprecia esta fuerza
-y el future $i\lyxmathsym{\textquoteright}$ simplemente se alinea
-con el objetivo estático a distancia que indique la distancia de reacción
-del peatón. Caso contrario, cuando la contribución de las fuerzas
-externas debe considerarse, se suma la contribución del peatón $i$
-sobre su future para ajustarlo según su objetivo estático. Esta fuerza
-se calcula a usando la formula del resorte. Los extremos de este resorte
-se encuentran en el punto a distancia ``distancia de reaccion''
-sobre el segmento de recta que une al peatón $i$ con su objetivo
-estático y la posición del future $i'$.
+where $\alpha$ and $\beta$ are predefined constants. Afterwards,
+we calculate the repulsion force between i' and j using the same formula
+but different $\alpha$ and $\beta$. Afterwards, we calculate the
+force between pedestrian i and his FVP i', this is a force that pushes
+i' to be in its desired relative distance from the pedestrian. This
+force is represented with a spring of length ``reaction distance''
+and constant $K$. When we sum all these, we get the final $F_{ext}$.
 
-A modo ilustrativo, se muestra en la figura 2 como la trayectoria
-del peatón $i$ es afectada por la del peatón $j$ a través de $F(i',\, j')$
-y es alineada al objetivo con $F(i,\, i')$
+Fig 2: FVP force calculation.
 
@@
 \begin{enumerate}
-\item Actualización de la posición de cada future.
+\item FVP position update.
 
-En esta etapa, simplemente se actualiza la posición de cada future
-según el cálculo de la fuerza $F$ aplicada en la etapa previa. Este
-cálculo se realiza utilizando las fórmulas de Euler.
+In this stage, the position of the FVP is updated with Euler's formula
+and the forces calculated in the previous step.
 
-Para romper con situaciones con altos grados de simetría, se agrega
-ruido $P=10\%$ sobre $F$. Para esto, se aplican dos formas de ruido:
+\end{enumerate}
+
+To avoid high simetry situations, a low noise $P=10\%$ is added to
+$F$. There are two ways to apply this noise:
 \begin{itemize}
-\item Ruido longitudinal:
+\item Radial noise:
 
 \begin{itemize}
-\item Se toma un valor $p$ según una distribución aleatoria uniforme en
-el intervalo $[-P,\, P]$ y se calcula: $FL_{i'}=F_{i'}*p$
-\end{itemize}
-\item Ruido angular:
+\item A value $p$ is taken randomly from a uniform distribution $[-P,\, P]$
+and calculate: $FL_{i'}=F_{i'}*p$
+\item Angular noise:
 
 \begin{itemize}
-\item Se toma $sgn=\{-1,\,1\}$ utilizando una distribución uniforme y $p$
-en $[-P,\, P]$ con la misma distribución. Luego se calcula: $FA_{i'}=rotation(F_{i'},\,\pi*sgn)*p$
+\item A value $sgn=\{-1,\,1\}$ is taken randomly from a uniform distribution
+and a value $p$ from $[-P,\, P]$. Then $FA_{i'}=rotation(F_{i'},\,\pi*sgn)*p$
+is calculated.
 \end{itemize}
@@
 
-Por último se toma $F'_{i'}=F_{i'}+FL_{i'}+FA_{i'}$ y de aplican
-las ecuaciones de movimiento.
+At last, we find $F'_{i'}=F_{i'}+FL_{i'}+FA_{i'}$ and apply euler's
+movement equations.
 
-\item Cálculo de la fuerza sobre cada peatón.
+\end{itemize}
+\begin{enumerate}
+\item Pedestrian forces calculation.
 
-El peatón siempre se mueve hacia la dirección en la que apunta su
-future y de acuerdo a la fuerza de deseo.
-
-Esta fuerza representa la atracción que un peatón $i$ ejerce sobre
-sí mismo a fin de dar un paso hacia su future y tratar de alcanzarlo.
-Esta definida por la siguiente fórmula:
+The pedestrian always wants to move in the direction his FVP is pointing
+and its magnitude is defined as Fd or desire force:
 
@@
 
-En donde $\tau=0.5$
+Where $\tau=0.5$
 
-\item Actualización de la posición de cada peatón.
+\item Pedestrian position update.
 
-La nueva posicion de cada peatón es calculada en esta etapa utilizando
-las mismas fórmulas mencionada en la etapa 2.
+The new position of the pedestrian will be calculated using Euler's
+formula and the desire force calculated in the previous step.
 
@@
 \end{enumerate}
+TODO: Los valores que se usaron son $\alpha=800$ y $\beta=[0.65,\,085]$
+con distribución uniforme.
 
-\section{Validación del modelo }
+\section{Calibracion}
+
+\subsection{Metricas a usar}
 
@@
 \end{enumerate}
+
+\section{Results}
+
 \vspace{1cm}

### 2014-11-20 src/main/java/ar/edu/itba/common/util/StepFunction.java
elimino KillPedestrianStuckOnWall de la simulacion. creo mapa habitacion (a pedido de daniel). cuando el peaton cambia su objetivo, ya no pone mas al future en la pocicion del body. ahora se muestra el tiempo en la gui. elimino codigo muerto. creo nueva variable que elimina los efectos que el peaton siente a partir del resto de los peatones y repulsion (social) de las paredes cuanto mas cerca se encuentre de su objetivo. otros cambios menores.

@@ -1,0 +1,18 @@
+package ar.edu.itba.common.util;
+
+import com.google.common.base.Function;
+
+public class StepFunction implements Function<Float, Float> {
+
+	private final float _x;
+
+	public StepFunction(float x) {
+		_x = x;
+	}
+
+	@Override
+	public Float apply(Float input) {
+		return input < _x ? 0f : 1f;
+	}
+
+}

### 2014-11-20 src/main/java/ar/edu/itba/pedestriansim/back/entity/mision/PedestrianTargetArea.java

@@ -1,16 +1,30 @@
 package ar.edu.itba.pedestriansim.back.entity.mision;
 
+import org.apache.commons.lang3.builder.ReflectionToStringBuilder;
+import org.apache.commons.lang3.builder.ToStringStyle;
 import org.newdawn.slick.geom.Line;
 import org.newdawn.slick.geom.Shape;
 import org.newdawn.slick.geom.Vector2f;
+
+import ar.edu.itba.pedestriansim.back.entity.PedestrianArea;
 
 public class PedestrianTargetArea implements PedestrianTarget {
 
 	private Line _targetArea;
 	private Vector2f _result = new Vector2f();
+	private int _id;
 
 	public PedestrianTargetArea(Line targetArea) {
 		_targetArea = targetArea;
+	}
+
+	public PedestrianTargetArea setId(int id) {
+		_id = id;
+		return this;
+	}
+
+	public int id() {
+		return _id;
 	}
 
 	@Override
@@ -24,4 +38,8 @@ public class PedestrianTargetArea implements PedestrianTarget {
 		return _result;
 	}
 
+	@Override
+	public String toString() {
+		return ReflectionToStringBuilder.toString(this, ToStringStyle.MULTI_LINE_STYLE);
+	}
 }

### 2014-11-20 src/main/java/ar/edu/itba/pedestriansim/back/logic/FutureForceUpdaterComponent.java

@@ -6,6 +6,7 @@ import org.apache.log4j.Logger;
 import org.newdawn.slick.geom.Line;
 import org.newdawn.slick.geom.Vector2f;
 
+import ar.edu.itba.common.util.LinearFunction;
 import ar.edu.itba.pedestriansim.back.entity.Pedestrian;
 import ar.edu.itba.pedestriansim.back.entity.PedestrianArea;
 import ar.edu.itba.pedestriansim.back.entity.PedestrianForces;
@@ -14,9 +15,13 @@ import ar.edu.itba.pedestriansim.back.entity.force.RepulsionForce;
 import ar.edu.itba.pedestriansim.back.entity.physics.RigidBody;
 import ar.edu.itba.pedestriansim.back.entity.physics.Vectors;
 
+import com.google.common.base.Function;
 import com.google.common.collect.Maps;
 
 public class FutureForceUpdaterComponent extends PedestrianAreaStep {
+
+//	private final Function<Float, Float> _wallRepulsionSmooth = new StepFunction(1.5f);
+	private final Function<Float, Float> _wallRepulsionSmooth = new LinearFunction(2f, 3f);
 
 	@SuppressWarnings("unused")
 	private static final Logger logger = Logger.getLogger(FutureForceUpdaterComponent.class);
@@ -34,27 +39,27 @@ public class FutureForceUpdaterComponent extends PedestrianAreaStep {
 		for (Pedestrian subject : input.pedestrians()) {
 			Vector2f repulsion = new Vector2f();
 			Vector2f future1Center = subject.getFuture().getBody().getCenter();
+			Vector2f subjectCenter = subject.getBody().getCenter();
+			float d = _wallRepulsionSmooth.apply(subject.getTargetSelection().getTarget().getClosesPoint(subjectCenter).distance(future1Center));
 			for (Pedestrian other : input.pedestrians()) {
 				if (subject != other && !isOnBack(subject, other)) {
 					Vector2f future2Center = other.getFuture().getBody().getCenter();
 					repulsion.add(
-						repulsionForce.between(future1Center, future2Center, subject.pedestrianRepulsionForceValues())
+						repulsionForce.between(future1Center, future2Center, subject.pedestrianRepulsionForceValues()).scale(d)
 					);
 					Vector2f futureVector1 = subject.getFuture().getBody().getCenter().copy().sub(subject.getBody().getCenter());
[…]

### 2014-11-20 src/main/java/ar/edu/itba/pedestriansim/front/UpdatePositionsFromFile.java

@@ -1,5 +1,6 @@
 package ar.edu.itba.pedestriansim.front;
 
+import java.math.BigDecimal;
 import java.util.Map;
 
 import ar.edu.itba.pedestriansim.back.entity.Pedestrian;
@@ -39,6 +40,7 @@ public class UpdatePositionsFromFile extends PedestrianAreaStep {
 		if (step == null) {
 			return;	// XXX: simulation finished!
 		}
+		input.setElapsedTime(new BigDecimal(step.step()));
 		frameIndex++;
 		if (frameIndex <= framesToSkip) {
 			return;

### 2014-11-23 doc/informe/paper.tex
estandarizo todas las imagenes del papaer (re hice todas con ppt). cambio detalles varios en el paper.

@@
 
-\title{A Pedestrian Simulationnnnnn}
+\title{A Pedestrian Simulation}
 
@@
 
-\subsection{Motivacion y antecedentes}
+\subsection{Motivation and previous work}
 
@@
 
-En el Social Force Model cada peatón se rige por una serie de reglas
-presentads por Helbing en sus paper {[}Helbing 1995, 2000{]}. A partir
-de estas reglas, proupso un modelo en donde cada peatón sufre una
-fuerza de deseo que lo provoca a acercarse hacia su objetivo y una
-fuerza de repulsión contra cada uno de los demas peatones. Junto a
-estas dos, existe la fuerza de contacto producto del conectacto físico.
-\\
+{[}Helbing 1995, 2000{]} presents a Model in which each pedestrian
+feels a ``desire force'' towards his objective and a ``repulsion
+force'' towards other pedestrians. On a lower level, a collission
+force is present.
 
-Cada una de las fuerzas en el modelo se define usando las siguientes
-fórmulas:\\
-
-Fuerza de contacto (Granular):
+Collision force (Granular):
 
@@
 
-En donde: $\epsilon_{ij}=r_{ij}-(R_{i}+R_{j})$
+Where: $\epsilon_{ij}=r_{ij}-(R_{i}+R_{j})$
 
@@
 
-Fuerza social:
+Social Force:
 \[
@@
 \begin{centering}
-\includegraphics[scale=0.6]{sfm/sf}
+\includegraphics[scale=0.4]{sfm/sf}
 \par\end{centering}
 
-\protect\caption{Fuerza social}
+\protect\caption{Social Force}
 \end{figure}
 
-Fuerza de deseo:
+Desire Force:
 
@@
 \begin{centering}
-\includegraphics[scale=0.7]{sfm/drivingforce}
+\includegraphics[scale=0.4]{sfm/drivingforce}
 \par\end{centering}
@@
 
-Luego, se calcula $F_{i}=F_{G_{i}}+F_{S_{i}}+F_{D_{i}}$
+Afterwards $F_{i}=F_{G_{i}}+F_{S_{i}}+F_{D_{i}}$is calculated
 
-En donde los parametros se encuentran definidos con lo siguientes
-valores: $A=2000\,[N]$, $B=0.08\,[m]$, $k_{n}=1.2\,10^{5}\,[\frac{N}{m}]$,
+Fixed parameter values: $A=2000\,[N]$, $B=0.08\,[m]$, $k_{n}=1.2\,10^{5}\,[\frac{N}{m}]$,
 $k_{t}=2.4\,10^{5}\,[\frac{kg}{m/s}]$ y $\tau=0.5\,[s]$.
 
-\subsection{Future Vector Particle Model}
+While this model doesn't present a very real behaviour for pedestrians,
+it worked as a starting point for numerous projects.
 
-Debido a que el SFM presenta una fuerza ficticia sobre el peatón,
-se generan artificios en la navegación ante la presencia de grandes
-cantidades de peatones. \{...\}
+\subsection{Future Virtual Particle Model}
 
-Frente a esto se presenta un nuevo modelo
+Given that the SFM adds a fictional force on pedestrians, navigation
+stops imitating reality when there's a big quantity of pedestrians.
+Pedestrians also show a collision avoidance method that resembles
+magnetism, with movements that are clearly governed by the squared
+distance to the other pedestrian. Also, SFM didn't have the same values
+as well known metrics for real-case scenarios such as the flow of
+pedestrians going out a door and the fundamental diagram.
 
-// no reproduce valores de Caudal Específico ni Diagrama Fundamental
-
-// To do: explicar nuestros aportes al modelo, observaciones sobre
-el SFM\\
+Because of this, we present a new model.
 
@@
 
-In the following the main effects that determine the motion of a pedestrian
-will be introduced: (agregar que son las mismas hipotesis que presenta
-Helbin en su paper)
+The main effects that govern the motion of a pedestrian are the same
+as Helbin's:
 \begin{enumerate}
-\item The pedestrian wants to reach to his goal in the shortest possible
-path.
+\item The pedestrian wants to reach his goal in the shortest possible path.
 \item The pedestrian's movement is influenced by other pedestrians. Depending
@@
 the pedestrian will feel the need to change his route to be able to
-avoid the other pedestrian. It is because of this effect that pedestrians
+avoid the other pedestrians. It is because of this effect that pedestrians
 will need to recalculate their route as new pedestrians get closer
@@
 
-\subsection{??}
+\subsection{Definition}
 
@@
 \item Short term objective
-\item Objetivo a corto plazo
 
@@
 
-\subsection{Implementation}
+\subsection{Algorithm}
 
@@
 
+\end{enumerate}
+
 \[
-F_{deseo}=\frac{dist(i',i)}{dist_{react}}\frac{v_{desire}-v_{curr}}{\tau}\frac{i'-i}{|i'-i|}
+F_{desire_{i}}=m_{i}\frac{\frac{dist(i',i)}{dist_{react}}e_{i}-v_{i}}{\tau}
 \]
@@
 Where $\tau=0.5$
-
+\begin{enumerate}
 \item Pedestrian position update.
@@
 \end{enumerate}
-TODO: Los valores que se usaron son $\alpha=800$ y $\beta=[0.65,\,085]$
-con distribución uniforme.
 
-\section{Calibracion}
+\section{Calibration}
 
-\subsection{Metricas a usar}
+\subsection{Metrics}
 
-Los resultados obtenidos fueron comparados utilizando el modelo ``Social
-Force Model'' utilizando los valores propuestos por Dirk Helbing
-{[}2{]}. Los escenarios de prueba fueron cruce y hallway.
+The results where compared to the SFM using the values propposed by
+Dirk Helbing {[}2{]}. The test scenarios where crossing and hallway
+for they present the main two types of simmetry (90 degrees and 180
+degrees).
 
-Los resultados fueron cuantificados utilizando las siguientes métricas:
+The metrics used where:
 \begin{enumerate}
-\item Cantidad total de colisiones
+\item Number of collisions
 
-TODO: (como se calcula)
+When a pedestrian's body is touching another one, a counter is incremented,
+it won't be incremented again unless it separates and touch again.
+This counter represents the amount of collisions.
 
-\item Duración promedio de las coliciones
+\item Total duration of collisions:
 
-TODO: (como se calcula)
+When a pedestrian's body is touching another one, a counter is incremented
+by the time step of the simulation. This counter will represent the
+total time pedestrians were colliding.
 
-\item Velocidad promedio de viaje
+\item Average walking speed:
 
-TODO: (como se calcula)
+//TODO
 
-\item Tiempo promedio de viaje
+\item Average travel time:
 
-TODO: (como se calcula)
+When a pedestrian appears in the map, this time is recorded, once
+he reaches his goal, the travel time is calculated with this value.
+The average of all this times represents the average travel time.
 
-\item Promedio de la distancia recorrida
+\item Average travel distance:
 
-TODO: (como se calcula)
+Each step, the distance a pedestrian has traveled from the source
+is saved. When this pedestrian reaches his goal, that distance is
+considered as finished and it is saved elsewhere. Afterwards, an average
+of all finished distances is calculated.
 
-\item Ángulo giro promedio
+\item Average turn angle:
 
-TODO: (como se calcula)
+Each step, the angle of the previous velocity of a pedestrian and
+the current one is saved and added to a total. When this pedestrians
+reaches his goal, this total is considered as finished and it is saved
+elsewhere. Afterwards, an average of all finished turn angles is calculated.
 
 \end{enumerate}
+
+\subsection{Values}
+
+To calibrate the model, runs varying parameters were made. A wide
+spectrum of values was covered, testing every combination of every
+possible one. After seeing clear preferences towards certain values,
+the values were refined within that scope. After numerous iterations
+of this process, the values that best suit these metrics are$\alpha=800$
+y $\beta=[0.65,\,085]$ uniformly distributed.
+
+//TODO todos los demás parámetros
 
@@
 \vspace{1cm}
-En la tabla a continuación se presentan las mediciones de las métricas
-utilizando un total de $10$ corridas:
 
+\begin{table}[H]
+{\scriptsize{}}%
 \begin{tabular}{|c|c|c|c|c|c|c|}
 \hline 
-Valores & 1 & 2 & 3 & 4 & 5 & 6\tabularnewline
+{\scriptsize{}Values} & {\scriptsize{}1} & {\scriptsize{}2} & {\scriptsize{}3} & {\scriptsize{}4} & {\scriptsize{}5} & {\scriptsize{}6}\tabularnewline
 \hline 
 \hline 
-$\alpha=800,\,\beta=[0.65,\,0.85]$ & (1.800, 0.748)  & (34.600, 8.333)  & (1.024, 0.016)  & (1.910, 0.022)  & (2.392, 0.005)  & (111.062, 19.122)\tabularnewline
+{\scriptsize{}$\alpha=800,\,\beta=[0.65,\,0.85]$} & {\scriptsize{}(1.800, 0.748) } & {\scriptsize{}(34.600, 8.333) } & {\scriptsize{}(1.024, 0.016) } & {\scriptsize{}(1.910, 0.022) } & {\scriptsize{}(2.392, 0.005) } & {\scriptsize{}(111.062, 19.122)}\tabularnewline
 \hline 
-$\alpha=2000,\,\beta=0.08$ & (5.333, 2.625) & (12.333, 8.340)  & (1.052, 0.003)  & (1.876, 0.003)  & (2.391, 0.002)  & (106.185, 13.778)\tabularnewline
+{\scriptsize{}$\alpha=2000,\,\beta=0.08$} & {\scriptsize{}(5.333, 2.625)} & {\scriptsize{}(12.333, 8.340) } & {\scriptsize{}(1.052, 0.003) } & {\scriptsize{}(1.876, 0.003) } & {\scriptsize{}(2.391, 0.002) } & {\scriptsize{}(106.185, 13.778)}\tabularnewline
 \hline 
-\end{tabular}
+\end{tabular}\protect\caption{Metrics comparing SFM vs FVPM. Average of $10$ runs.}
+\end{table}
 
@@
 
-\section{Conclusiones}
+\section{Conclusions}
 
@@
 
-\section{Referencias}
+\section{References}
 \begin{itemize}

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/back/config/HallwayConfig.java
las paredes ahora pueden ser gruesas especificando la direccion en la cual las cosas rebotan (para poder detectar cuando un objeto la traspaso). ahora es posible modificar los FPS en runtime usando el pas numerico (1 decremente y 2 aumenta). al reiniciar la simulacion, la camara y zoom no se reinician.

@@ -59,11 +59,11 @@ public class HallwayConfig implements ApplicationConfigBuilder {
 	private void addWalls(PedestrianArea area) {
 		// Arriba
 		area.addObstacle(
-			new Wall(new Line(0, 15, 30, 15)).setThickBorder(new Line(0, 14.9f, 30, 14.9f))
+			new Wall(new Line(0, 15, 30, 15)).setThickDirection(new Vector2f(0, 1))
 		);
 		// Abajo
 		area.addObstacle(
-			new Wall(new Line(0, 19, 30, 19)).setThickBorder(new Line(0, 19.1f, 30, 19.1f))
+			new Wall(new Line(0, 19, 30, 19)).setThickDirection(new Vector2f(0, -1))
 		);
 	}
 }

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/back/config/SquareRoomConfig.java

@@ -68,19 +68,18 @@ public class SquareRoomConfig implements ApplicationConfigBuilder {
 		// derecha
 		area.addObstacle(new Wall(new Line(maxX, yOffset, maxX, maxY)));
 		// Abajo
-		float thick = 0.1f;
 		area.addObstacle(new Wall(new Line(xOffset, maxY, doorXMin, maxY))
-			.setThickBorder(new Line(xOffset, maxY + thick, doorXMin, maxY + thick))
+			.setThickDirection(new Vector2f(0, -1))
 		);
 		area.addObstacle(new Wall(new Line(doorXMax, maxY, maxX, maxY))
-			.setThickBorder(new Line(doorXMax, maxY + thick, maxX, maxY + thick))
+			.setThickDirection(new Vector2f(0, -1))
 		);
 		// Pasillo al final
 		area.addObstacle(new Wall(new Line(doorXMin, maxY, doorXMin, maxY + 4))
-			.setThickBorder(new Line(doorXMin + thick, maxY, doorXMin + thick, maxY + 4))
+			.setThickDirection(new Vector2f(1, 0))
 		);
 		area.addObstacle(new Wall(new Line(doorXMax, maxY, doorXMax, maxY + 4))
-			.setThickBorder(new Line(doorXMax - thick, maxY, doorXMax - thick, maxY + 4))
+			.setThickDirection(new Vector2f(-1, 0))
 		);
 	}
 }

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/back/entity/Wall.java

@@ -1,18 +1,23 @@
 package ar.edu.itba.pedestriansim.back.entity;
 
 import org.newdawn.slick.geom.Line;
+import org.newdawn.slick.geom.Vector2f;
 
-public class Wall {
+import com.google.common.base.Optional;
+import com.google.common.base.Preconditions;
 
-	private Line _thickBorder;
+public final class Wall {
+
 	private Line _line;
+	private Optional<Vector2f> _normal = Optional.absent();
 
 	public Wall(Line line) {
 		_line = line;
 	}
 
-	public Wall setThickBorder(Line extraBorder) {
-		_thickBorder = extraBorder;
+	public Wall setThickDirection(Vector2f normal) {
+		Preconditions.checkArgument(Math.abs(new Vector2f(line().getNormal(0)).dot(normal)) == 1);
+		_normal = Optional.of(normal);
 		return this;
 	}
 
@@ -20,11 +25,11 @@ public class Wall {
 		return _line;
 	}
 
-	public Line thickBorder() {
-		return _thickBorder;
+	public Optional<Vector2f> normal() {
+		return _normal;
 	}
 
 	public boolean isThick() {
-		return _thickBorder != null;
+		return normal().isPresent();
 	}
 }

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/back/entity/force/SpringForceModel.java

@@ -2,10 +2,9 @@ package ar.edu.itba.pedestriansim.back.entity.force;
 
 import org.newdawn.slick.geom.Circle;
 import org.newdawn.slick.geom.Line;
-import org.newdawn.slick.geom.Rectangle;
-import org.newdawn.slick.geom.Shape;
 import org.newdawn.slick.geom.Vector2f;
 
+import ar.edu.itba.pedestriansim.back.entity.Wall;
 import ar.edu.itba.pedestriansim.back.entity.physics.Collitions;
 import ar.edu.itba.pedestriansim.back.entity.physics.RigidBody;
 import ar.edu.itba.pedestriansim.back.entity.physics.Vectors;
@@ -30,34 +29,45 @@ public class SpringForceModel {
 		return Vectors.zero();
 	}
 
-	public Vector2f getForce(RigidBody shape1, Shape shape) {
-		if (shape instanceof Line) {
-			return getForce(shape1, (Line) shape);
-		}
-		if (shape instanceof Rectangle) {
-			Rectangle rectangle = (Rectangle) shape;
-			Line closest = null;
-			float closestDistance = 0;
-			Line border = new Line(0, 0);
-			for (int i = 0; i < 4; i++) {
-				border.set(rectangle.getPoint(i), rectangle.getPoint((i + 1) % 4));
-				float currDistance = border.distance(shape1.getCenter());
-				if (closest == null || currDistance < closestDistance) {
-					closest = border;
-					closestDistance = currDistance;
+	public Vector2f getForce(RigidBody body, Wall wall) {
+		Vector2f center = body.getCenter();
+		Line line = wall.line();
+		final float wallTicknesSq = 1;
+		if (wall.isThick()) {
+			line.getClosestPoint(center, closestPointCache);
+			Vector2f wallDir = closestPointCache.copy().sub(center);
+			Vector2f wallDirNorm = closestPointCache.copy().sub(center).normalise();
+			float dot = wallDirNorm.dot(wall.normal().get());
+			if (dot == 1) {
+				float rSq = body.getRadius() * body.getRadius() * 4;
+				if (closestPointCache.distanceSquared(line.getStart()) < rSq || closestPointCache.distanceSquared(line.getEnd()) < rSq) {
+					return Vectors.zero();
 				}
+				if (center.distanceSquared(closestPointCache) > wallTicknesSq) {
+					return Vectors.zero();
+				}
+				float overlapping = Collitions.overlapping(body.getShape(), line);
[…]

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/back/entity/physics/RigidBody.java

@@ -5,14 +5,14 @@ import org.apache.commons.lang3.builder.ToStringStyle;
 import org.newdawn.slick.geom.Circle;
 import org.newdawn.slick.geom.Vector2f;
 
-public class RigidBody {
+public final class RigidBody {
 
-	private Vector2f _center;
-	private Vector2f _velocity;
-	private Vector2f _appliedForce;
-	private float _mass;
-	private float _radius;
-	private Circle _shape;
+	private final Vector2f _center;
+	private final Vector2f _velocity;
+	private final Vector2f _appliedForce;
+	private final float _mass;
+	private final float _radius;
+	private final Circle _shape;
 
 	public RigidBody(float mass, Vector2f location, float radius) {
 		_mass = mass;
@@ -25,10 +25,6 @@ public class RigidBody {
 
 	public float getMass() {
 		return _mass;
-	}
-
-	public void setMass(float mass) {
-		this._mass = mass;
 	}
 
 	public Vector2f getVelocity() {

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/back/entity/physics/Vectors.java

@@ -2,6 +2,9 @@ package ar.edu.itba.pedestriansim.back.entity.physics;
 
 import org.newdawn.slick.geom.Line;
 import org.newdawn.slick.geom.Vector2f;
+
+import com.google.common.base.Preconditions;
+
 /**
  * Class used to make calculations with vectors
  * 
@@ -40,4 +43,12 @@ public class Vectors {
 		return alignmentVector;
 	}
 
+	public static float angle(Vector2f v1, Vector2f v2) {
+		double angle = Math.abs(v1.getTheta() - v2.getTheta());
+		if (angle > 180) {
+			angle = 360 - angle;
+		}
+		Preconditions.checkArgument(0 <= angle && angle <= 180);
+		return (float) angle;
+	}
 }

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/back/logic/FutureForceUpdaterComponent.java

@@ -21,7 +21,7 @@ import com.google.common.collect.Maps;
 public class FutureForceUpdaterComponent extends PedestrianAreaStep {
 
 //	private final Function<Float, Float> _wallRepulsionSmooth = new StepFunction(1.5f);
-	private final Function<Float, Float> _wallRepulsionSmooth = new LinearFunction(2f, 3f);
+	private final Function<Float, Float> _repulsionSmooth = new LinearFunction(2f, 3f);
 
 	@SuppressWarnings("unused")
 	private static final Logger logger = Logger.getLogger(FutureForceUpdaterComponent.class);
@@ -40,21 +40,20 @@ public class FutureForceUpdaterComponent extends PedestrianAreaStep {
 			Vector2f repulsion = new Vector2f();
 			Vector2f future1Center = subject.getFuture().getBody().getCenter();
 			Vector2f subjectCenter = subject.getBody().getCenter();
-			float d = _wallRepulsionSmooth.apply(subject.getTargetSelection().getTarget().getClosesPoint(subjectCenter).distance(future1Center));
+			float d = _repulsionSmooth.apply(subject.getTargetSelection().getTarget().getClosesPoint(subjectCenter).distance(future1Center));
+			Vector2f futureVector1 = subject.getFuture().getBody().getCenter().copy().sub(subject.getBody().getCenter());
 			for (Pedestrian other : input.pedestrians()) {
 				if (subject != other && !isOnBack(subject, other)) {
 					Vector2f future2Center = other.getFuture().getBody().getCenter();
 					repulsion.add(
-						repulsionForce.between(future1Center, future2Center, subject.pedestrianRepulsionForceValues()).scale(d)
+						repulsionForce.between(future1Center, future2Center, subject.pedestrianRepulsionForceValues())
 					);
-					Vector2f futureVector1 = subject.getFuture().getBody().getCenter().copy().sub(subject.getBody().getCenter());
 					Vector2f futureVector2 = other.getFuture().getBody().getCenter().copy().sub(other.getBody().getCenter());
-					double angle = Math.abs(futureVector1.getTheta() - futureVector2.getTheta());
-					angle = (angle > 180) ? 360 - angle : angle; 
+					double angle = Vectors.angle(futureVector1, futureVector2);
 					if (angle > 120) {
 						Vector2f body2Center = other.getBody().getCenter();
 						repulsion.add(
[…]

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/back/logic/KillPedestrianStuckOnWall.java

@@ -18,21 +18,21 @@ public class KillPedestrianStuckOnWall extends PedestrianAreaStep {
 
 	@Override
 	public void update(PedestrianArea input) {
-		_toRemove.clear();
-		for (Pedestrian p : input.pedestrians()) {
-			for (Wall wall : input.obstacles()) {
-				if (wall.isThick()) {
-					Line line = new Line(p.getBody().getCenter(), p.getFuture().getBody().getCenter());
-					if (line.intersect(wall.thickBorder(), true, tmp)) {
-						System.out.println(" [WARN] Peaton atravesando pared: " + p.getId());
-						_toRemove.add(p);
-					}
-				}
-			}
-		}
-		if (!_toRemove.isEmpty()) {
-			input.removePedestrians(_toRemove);
-		}
+//		_toRemove.clear();
+//		for (Pedestrian p : input.pedestrians()) {
+//			for (Wall wall : input.obstacles()) {
+//				if (wall.isThick()) {
+//					Line line = new Line(p.getBody().getCenter(), p.getFuture().getBody().getCenter());
+//					if (line.intersect(wall.thickBorder(), true, tmp)) {
+//						System.out.println(" [WARN] Peaton atravesando pared: " + p.getId());
+//						_toRemove.add(p);
+//					}
+//				}
+//			}
+//		}
+//		if (!_toRemove.isEmpty()) {
+//			input.removePedestrians(_toRemove);
+//		}
 	}
 
 }

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/back/logic/PedestrianForceUpdaterComponent.java

@@ -35,7 +35,7 @@ public class PedestrianForceUpdaterComponent extends PedestrianAreaStep {
 			externalForces.add(collitionModel.getForce(subject.getBody(), other.getBody()));
 		}
 		for (Wall wall : input.obstacles()) {
-			externalForces.add(collitionModel.getForce(subject.getBody(), wall.line()));
+			externalForces.add(collitionModel.getForce(subject.getBody(), wall));
 		}
 		return externalForces;
 	}

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/back/logic/SocialForceUpdaterComponent.java

@@ -71,7 +71,7 @@ public class SocialForceUpdaterComponent extends PedestrianAreaStep {
 		for (Wall wall : walls) {
 			Line line = wall.line();
 			if (pedesitan.getShape().intersects(line)) {
-				f.add(wallCollisionForceModel.getForce(pedesitan.getBody(), line));
+				f.add(wallCollisionForceModel.getForce(pedesitan.getBody(), wall));
 			}
 		}
 		return f;

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/front/GUIPedestrianSim.java

@@ -36,7 +36,7 @@ import com.google.common.io.Closer;
 
 public class GUIPedestrianSim extends BasicGame {
 
-	private static final int FPS = 160;
+	private static final int FPS = 80;
 
 	public static final Logger logger = Logger.getLogger(GUIPedestrianSim.class);
 	public static final CommandParser parser;
@@ -71,11 +71,13 @@ public class GUIPedestrianSim extends BasicGame {
 		appContainer.start();
 	}
 
+	private GameContainer _gc;
 	private PedestrianAppConfig _config;
 	private Camera _camera;
 	private PedestrianSim _simulation;
 	private PedestrianAreaRenderer _renderer;
 	private boolean _simulationIsFinished = false;
+	private boolean _initialized;
 
 	public GUIPedestrianSim(ApplicationConfigBuilder configBuilder) {
 		super("Pedestrian simulation");
@@ -86,10 +88,12 @@ public class GUIPedestrianSim extends BasicGame {
 		} else {
 			logger.info("Assuming already defined run on given configuration");
 		}
+		_initialized = false;
 	}
 
 	@Override
 	public void init(GameContainer gc) throws SlickException {
+		_gc = gc;
 		final Closer closer = Closer.create();
 		Scanner staticReader = closer.register(newScanner(_config.staticfile()));
 		Scanner dynamicReader = closer.register(newScanner(_config.dynamicfile()));
@@ -113,12 +117,15 @@ public class GUIPedestrianSim extends BasicGame {
 				}
 			})
 		;
-		_camera = new Camera();
-		_camera.setZoom(20f);
-		_renderer = new PedestrianAreaRenderer(_camera);
-		gc.setAlwaysRender(true);
-		gc.setTargetFrameRate(FPS);
-		gc.getInput().addKeyListener(new KeyHandler(_camera, _renderer, gc));
+		if (!_initialized) {
+			_initialized = true;
+			_camera = new Camera();
+			_camera.setZoom(20f);
+			_renderer = new PedestrianAreaRenderer(_camera);
+			gc.setAlwaysRender(true);
+			gc.setTargetFrameRate(FPS);
+		}
+		gc.getInput().addKeyListener(new KeyHandler(_camera));
 	}
 
 	private Scanner newScanner(File file) {
[…]

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/front/InputKey.java

@@ -2,22 +2,13 @@ package ar.edu.itba.pedestriansim.front;
 
 public abstract class InputKey {
 
-	private boolean _oncePerClick;
 	private boolean _pressed;
 
 	public InputKey() {
-		this(false);
-	}
-
-	public InputKey(boolean oncePerTap) {
-		_oncePerClick = oncePerTap;
 		_pressed = false;
 	}
 
 	public void onKeyPressed() {
-		if (_pressed && _oncePerClick) {
-			return;
-		}
 		_pressed = true;
 		pressed();
 	}

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/front/KeyHandler.java

@@ -2,7 +2,6 @@ package ar.edu.itba.pedestriansim.front;
 
 import java.util.List;
 
-import org.newdawn.slick.GameContainer;
 import org.newdawn.slick.Input;
 import org.newdawn.slick.KeyListener;
 
@@ -10,19 +9,15 @@ import com.google.common.collect.Lists;
 
 public class KeyHandler implements KeyListener {
 
-	private PedestrianAreaRenderer _renderer;
 	private Camera _camera;
-	private GameContainer _gc;
 
 	private final List<KeyMapping> handlers = Lists.newLinkedList();
-	
-	public KeyHandler(Camera camera, PedestrianAreaRenderer renderer, GameContainer gc) {
+
+	public KeyHandler(Camera camera) {
 		_camera = camera;
-		_renderer = renderer;
-		_gc = gc;
 		initialize();
 	}
-	
+
 	private void initialize() {
 		handlers.add(new KeyMapping(13, new ZoomIn()));
 		handlers.add(new KeyMapping(Input.KEY_ADD, new ZoomIn()));
@@ -38,11 +33,6 @@ public class KeyHandler implements KeyListener {
 		handlers.add(new KeyMapping(Input.KEY_S, new ScrollDown()));
 		handlers.add(new KeyMapping(Input.KEY_A, new ScrollLeft()));
 		handlers.add(new KeyMapping(Input.KEY_D, new ScrollRight()));
-		
-		handlers.add(new KeyMapping(Input.KEY_C, new ToggleRenderDebugInfo()));
-		handlers.add(new KeyMapping(Input.KEY_V, new ToggleRenderMoreDebugInfo()));
-		handlers.add(new KeyMapping(Input.KEY_P, new PauseToogle()));
-		
 	}
 
 	@Override
@@ -64,7 +54,8 @@ public class KeyHandler implements KeyListener {
 	}
 
 	@Override
-	public void setInput(Input arg0) {}
+	public void setInput(Input arg0) {
+	}
 
 	@Override
 	public void keyPressed(int keyCode, char c) {
@@ -91,12 +82,12 @@ public class KeyHandler implements KeyListener {
 		}
 		return null;
 	}
-	
+
 	private static class KeyMapping {
 		private int _keyCode;
 		private InputKey _key;
 		private boolean pressed;
-		
+
 		public KeyMapping(int keyCode, InputKey key) {
 			_keyCode = keyCode;
 			_key = key;
[…]

### 2014-11-25 src/main/java/ar/edu/itba/pedestriansim/front/PedestrianAreaRenderer.java

@@ -4,6 +4,8 @@ import org.newdawn.slick.Color;
 import org.newdawn.slick.GameContainer;
 import org.newdawn.slick.Graphics;
 import org.newdawn.slick.geom.Circle;
+import org.newdawn.slick.geom.Line;
+import org.newdawn.slick.geom.Vector2f;
 
 import ar.edu.itba.pedestriansim.back.entity.PedestrianArea;
 import ar.edu.itba.pedestriansim.back.entity.PedestrianSource;
@@ -30,13 +32,17 @@ public class PedestrianAreaRenderer extends ShapeRenderer {
 			fill(g, _sourceShape);
 		}
 		_pedestrianRenderer.render(gc, g, pedestrianArea.pedestrians());
-		g.setColor(Color.white);
 		for (Wall wall : pedestrianArea.obstacles()) {
+			g.setColor(Color.white);
 			draw(g, wall.line());
-			if (wall.isThick()) {
-				draw(g, wall.thickBorder());
-			}
+//			if (wall.isThick()) {
+//				g.setColor(Color.yellow);
+//				Vector2f start = new Vector2f(wall.line().getPoint(0));
+//				Line line = new Line(start, start.copy().add(wall.normal().get()));
+//				draw(g, line);
+//			}
 		}
+		g.setColor(Color.white);
 		g.drawString(pedestrianArea.elapsedTime().toString(), gc.getScreenWidth() * 0.8f, gc.getScreenHeight() * 0.85f);
 	}
 

### 2014-12-02 src/main/java/ar/edu/itba/pedestriansim/back/config/CrossingConfig.java
Elimino if extraño en FutureForceUpdaterComponent que verificaba que el angulo entre ii' i jj' sea mayor a 120 para aplicar la fuerza de repulsion future pedestrian body. Configuro por cada mapa, los parametros adecuados de alpha y beta. otros cambios menores.

@@ -1,5 +1,6 @@
 package ar.edu.itba.pedestriansim.back.config;
 
+import org.apache.commons.lang3.tuple.Pair;
 import org.newdawn.slick.geom.Line;
 import org.newdawn.slick.geom.Vector2f;
 
@@ -10,6 +11,8 @@ import ar.edu.itba.pedestriansim.back.entity.PedestrianSource;
 import ar.edu.itba.pedestriansim.back.entity.Wall;
 import ar.edu.itba.pedestriansim.back.entity.mision.PedestrianMision;
 import ar.edu.itba.pedestriansim.back.entity.mision.PedestrianTargetArea;
+
+import com.google.common.collect.Range;
 
 public class CrossingConfig implements ApplicationConfigBuilder {
 
@@ -26,6 +29,7 @@ public class CrossingConfig implements ApplicationConfigBuilder {
 	@Override
 	public PedestrianAppConfig get() {
 		PedestrianAppConfig config = _defaultBuilder.get();
+		config.pedestrianFactory().setPedestrianAlphaBeta(Pair.of(1000f, Range.closed(0.5f, 0.6f)));
 		addWalls(config.pedestrianArea());
 		addSource1(config.pedestrianArea());
 		addSource2(config.pedestrianArea());

### 2014-12-02 src/main/java/ar/edu/itba/pedestriansim/back/config/DefaultPedestrianAppConfig.java

@@ -18,9 +18,9 @@ public class DefaultPedestrianAppConfig implements ApplicationConfigBuilder {
 		Range<Float> mass = Range.closed(60f, 80f);
 		Range<Float> velocity = Range.closed(1.2f, 1.4f);
 		Range<Float> r = Range.closed(0.25f, 0.29f);
-		Pair<Float, Range<Float>> pedestrianAlphaBeta = Pair.of(1000f, Range.closed(0.60f, 0.70f));
+		Pair<Float, Range<Float>> pedestrianAlphaBeta = Pair.of(1000f, Range.closed(0.3f, 0.6f));
 		Pair<Float, Float> wallAlphaBeta = Pair.of(5000f, .15f);
-		Pair<Float, Float> futurePedestrianAlphaBeta = Pair.of(5000f, 0.2f);
+		Pair<Float, Float> futurePedestrianAlphaBeta = Pair.of(1000f, 0.2f);
 		return new PedestrianAppConfig()
 			.makeNewRun(true)
 			.setTimeStep(new BigDecimal(1 / 1000f).setScale(5, RoundingMode.UP))

### 2014-12-02 src/main/java/ar/edu/itba/pedestriansim/back/config/HallwayConfig.java

@@ -1,5 +1,6 @@
 package ar.edu.itba.pedestriansim.back.config;
 
+import org.apache.commons.lang3.tuple.Pair;
 import org.newdawn.slick.geom.Line;
 import org.newdawn.slick.geom.Vector2f;
 
@@ -10,6 +11,8 @@ import ar.edu.itba.pedestriansim.back.entity.PedestrianSource;
 import ar.edu.itba.pedestriansim.back.entity.Wall;
 import ar.edu.itba.pedestriansim.back.entity.mision.PedestrianMision;
 import ar.edu.itba.pedestriansim.back.entity.mision.PedestrianTargetArea;
+
+import com.google.common.collect.Range;
 
 public class HallwayConfig implements ApplicationConfigBuilder {
 
@@ -28,6 +31,7 @@ public class HallwayConfig implements ApplicationConfigBuilder {
 	@Override
 	public PedestrianAppConfig get() {
 		PedestrianAppConfig config = _defaultBuilder.get();
+		config.pedestrianFactory().setPedestrianAlphaBeta(Pair.of(1000f, Range.closed(0.3f, 0.4f)));
 		addWalls(config.pedestrianArea());
 		addSource1(config.pedestrianArea());
 		addSource2(config.pedestrianArea());

### 2014-12-02 src/main/java/ar/edu/itba/pedestriansim/back/config/SquareRoomConfig.java

@@ -1,7 +1,10 @@
 package ar.edu.itba.pedestriansim.back.config;
 
+import org.apache.commons.lang3.tuple.Pair;
 import org.newdawn.slick.geom.Line;
 import org.newdawn.slick.geom.Vector2f;
+
+import com.google.common.collect.Range;
 
 import ar.edu.itba.common.rand.UniformRandomGenerator;
 import ar.edu.itba.pedestriansim.back.entity.PedestrianAppConfig;
@@ -39,6 +42,7 @@ public class SquareRoomConfig implements ApplicationConfigBuilder {
 	@Override
 	public PedestrianAppConfig get() {
 		PedestrianAppConfig config = _defaultBuilder.get();
+		config.pedestrianFactory().setPedestrianAlphaBeta(Pair.of(1000f, Range.closed(0.3f, 0.4f)));
 		addWalls(config.pedestrianArea());
 		addSource1(config.pedestrianArea());
 		return config;

### 2014-12-02 src/main/java/ar/edu/itba/pedestriansim/back/factory/PedestrianFactory.java

@@ -32,14 +32,14 @@ public class PedestrianFactory {
 		_massGenerator = new UniformRandomGenerator(mass);
 		_velocityGenerator = new UniformRandomGenerator(velocity);
 		_radiusGenerator = new UniformRandomGenerator(r);
-		setPedestrianAlphaBeta(pedestrianAlphaBeta.getLeft(), pedestrianAlphaBeta.getRight());
+		setPedestrianAlphaBeta(pedestrianAlphaBeta);
 		setWallAlphaBeta(wallAlphaBeta.getLeft(), wallAlphaBeta.getRight());
 		setFuturePedestrianAlphaBeta(futurePedestrianAlphaBeta.getLeft(), futurePedestrianAlphaBeta.getRight());
 	}
 
-	public PedestrianFactory setPedestrianAlphaBeta(float alpha, Range<Float> beta) {
-		_pedestrianAlpha = alpha;
-		_pedestrianBetaGenerator = new UniformRandomGenerator(beta);
+	public PedestrianFactory setPedestrianAlphaBeta(Pair<Float, Range<Float>> pedestrianAlphaBeta) {
+		_pedestrianAlpha = pedestrianAlphaBeta.getLeft();
+		_pedestrianBetaGenerator = new UniformRandomGenerator(pedestrianAlphaBeta.getRight());
 		return this;
 	}
 

### 2014-12-02 src/main/java/ar/edu/itba/pedestriansim/back/logic/FutureForceUpdaterComponent.java

@@ -34,21 +34,11 @@ public class FutureForceUpdaterComponent extends PedestrianAreaStep {
 		for (Pedestrian subject : input.pedestrians()) {
 			Vector2f repulsion = new Vector2f();
 			Vector2f future1Center = subject.getFuture().getBody().getCenter();
-			Vector2f futureVector1 = subject.getFuture().getBody().getCenter().copy().sub(subject.getBody().getCenter());
 			for (Pedestrian other : input.pedestrians()) {
 				if (subject != other && !isOnBack(subject, other)) {
 					Vector2f future2Center = other.getFuture().getBody().getCenter();
-					repulsion.add(
-						repulsionForce.between(future1Center, future2Center, subject.pedestrianRepulsionForceValues())
-					);
-					Vector2f futureVector2 = other.getFuture().getBody().getCenter().copy().sub(other.getBody().getCenter());
-					double angle = Vectors.angle(futureVector1, futureVector2);
-					if (angle > 120) {
-						Vector2f body2Center = other.getBody().getCenter();
-						repulsion.add(
-							repulsionForce.between(future1Center, body2Center, subject.futurePedestrianRepulsionForceValues())
-						);
-					}
+					repulsion.add(repulsionForce.between(future1Center, future2Center, subject.pedestrianRepulsionForceValues()));
+					repulsion.add(repulsionForce.between(future1Center, other.getBody().getCenter(), subject.futurePedestrianRepulsionForceValues()));
 				}
 			}
 			repulsion.add(obstacleCollitionForces(subject, input));

### 2014-12-02 src/main/java/ar/edu/itba/pedestriansim/metric/RunsGenerator.java

@@ -7,6 +7,8 @@ import java.util.List;
 import java.util.concurrent.ExecutorService;
 import java.util.concurrent.Executors;
 
+import org.apache.commons.lang3.tuple.Pair;
+
 import ar.edu.itba.command.CommandParam;
 import ar.edu.itba.command.CommandParser;
 import ar.edu.itba.command.ParsedCommand;
@@ -98,7 +100,7 @@ public class RunsGenerator {
 			PedestrianAppConfig config = new CrossingConfig().get();
 			config.setStaticfile(new File(runsDirectory + File.separator + fileId + "-static.txt"));
 			config.setDynamicfile(new File(runsDirectory + File.separator + fileId + "-dynamic.txt"));
-			config.pedestrianFactory().setPedestrianAlphaBeta(alpha, beta);
+			config.pedestrianFactory().setPedestrianAlphaBeta(Pair.of(alpha, beta));
 			config.setExternalForceThreshold(threshold);
 			if (_newRun) {
 				new PedestrianSimApp(config).run();

### 2014-12-02 src/main/java/ar/edu/itba/pedestriansim/metric/VelocityByDensity.java

@@ -125,7 +125,7 @@ public class VelocityByDensity {
 			PedestrianAppConfig config = new HallwayConfig().get();
 			config.setStaticfile(new File(runsDirectory + File.separator + fileId + "-static.txt"));
 			config.setDynamicfile(new File(runsDirectory + File.separator + fileId + "-dynamic.txt"));
-			config.pedestrianFactory().setPedestrianAlphaBeta(alpha, beta);
+			config.pedestrianFactory().setPedestrianAlphaBeta(Pair.of(alpha, beta));
 			config.setExternalForceThreshold(threshold);
 			if (_newRun) {
 				new PedestrianSimApp(config).run();

### 2014-12-04 doc/informe/paper.tex
actualizo .tex
agrego explicaciones faltantes al paper.

@@
 \documentclass[english]{article}
-\usepackage[T1]{fontenc}
 \usepackage[latin9]{inputenc}
@@
 \usepackage{float}
+\usepackage{amsthm}
 \usepackage{amsmath}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
+\numberwithin{equation}{section}
+\numberwithin{figure}{section}
+
 \makeatother
@@
 
-\title{A Pedestrian Simulation}
-
-\title{Future Virtual Particle Force Model}
+\title{Future Virtual Particle Method for Pedestrian Navigation}
 
@@
 {[}Helbing 1995, 2000{]} presents a Model in which each pedestrian
-feels a ``desire force'' towards his objective and a ``repulsion
-force'' towards other pedestrians. On a lower level, a collission
-force is present.
+is subject to ``social forces''. This forces are a measure for the
+internal motivations of the individual to perform certain actions.
+In its simplest form, the Social Force Model consist on three main
+terms. Each of there term represent a force that a pedestrian will
+suffer in order to reach his objective.
 
-Collision force (Granular):
+The first term describes the acceleration that a pedestrian keeps
+towards his desired velocity of motion. This term is known as the
+``Desire Force'' and it's calculated as follows:
+
+\[
+F_{D_{i}}=m_{i}\frac{v_{di}e_{i}-v_{i}}{\tau}
+\]
+
+In this latest formula, $v_{di}$ represents the desire velocity for
+the pedestrian $i$, $v_{i}$ is the current velocity and $e_{i}$
+represents the desired direction of motion of the pedestrian $i$
+and is calculated as follows:
+
+\[
+e_{i}(t)=\frac{r_{i}^{k}-r_{i}(t)}{||r_{i}^{k}-r_{i}(t)||}
+\]
+
+where $r_{\alpha}(t)$ denotes the actual position of the pedestrian
+$i$ at the time $t$. The goal is represented as an area, and the
+vector $e_{i}$ will be pointing towards the closest pont. Figure
+$1.1$ shows en example of a pedestrian currenty moving in direction
+of $v$ but correcting its trayectory towards $e$.
+
+\begin{figure}[H]
+\begin{centering}
+\includegraphics[scale=0.4]{sfm/drivingforce}
+\par\end{centering}
+
+\protect\caption{Driving force}
+\end{figure}
+
+\vspace{1cm}
+
+The second term represents the fact that a pedestrian keeps a certain
+distance to other pedestrians and borders. This term is known as the
+``Social Force'' and it's caluclated as follows:
+
+\[
+F_{S_{i}}=\sum_{j=1,j\ne i}^{N_{P}}Aexp(-\frac{\epsilon_{ij}}{B})\, e_{ij}^{n}
+\]
+
+In this formula the terms $A$ and $B$ represents constants that
+where determined by simulations and $\epsilon_{ij}$ represents the
+distance from pedestrian $i$ towards pedestrian $j$. Figure $1.2$
+shows this vector grafically.
+
+\begin{figure}[H]
+\begin{centering}
+\includegraphics[scale=0.4]{sfm/sf}
+\par\end{centering}
+
+\protect\caption{Social Force}
+\end{figure}
+
+\vspace{1cm}
+
+The third terms represents the granular force. This force represents
+the physical force that a pedestrians feels when in collision with
+another objects (pedestrian or wall). This granular force term is
+defined as follows:
 
@@
 
-\protect\caption{Fuerza de contact granular}
+\protect\caption{Example of two pedestrians in collision}
 
@@
 
-Social Force:
-\[
-F_{S_{i}}=\sum_{j=1,j\ne i}^{N_{P}}Aexp(-\frac{\epsilon_{ij}}{B})\, e_{ij}^{n}
-\]
-
-\vspace{1cm}
-
-\begin{figure}[H]
-\begin{centering}
-\includegraphics[scale=0.4]{sfm/sf}
-\par\end{centering}
-
-\protect\caption{Social Force}
-\end{figure}
-
-Desire Force:
-
-\[
-F_{D_{i}}=m_{i}\frac{v_{di}e_{i}-v_{i}}{\tau}
-\]
-
-\begin{figure}[H]
-\begin{centering}
-\includegraphics[scale=0.4]{sfm/drivingforce}
-\par\end{centering}
-
-\protect\caption{Driving force}
-\end{figure}
-
-\vspace{1cm}
-
-Afterwards $F_{i}=F_{G_{i}}+F_{S_{i}}+F_{D_{i}}$is calculated
+Afterwards $F_{i}=F_{G_{i}}+F_{S_{i}}+F_{D_{i}}$is calculated for
+each of the pedestrians on each simulation step and applyed to the
+pedestrian until it reaches his goal.
 
@@
 
-In each iteration, the FVP from pedestrian $i$ feels a force generated
-by the other pedestrians and FVPs. First of all, we filter de pedestrians
-$j$ who are not in the range of sight of pedestrian $i$ as follows:
+For each pedestrian $i$, the force that his future $i'$ will suffer
+is calculated in this step. The magnitude of this force will depend
+on two factors: by each of the other pedestrians and the walls that
+might exists surronding $i$. The final value of the force applied
+over the future $i'$ will be the addition of the latest two factors.
+
+The fist factor is caluclated for each of the pedestrian $j$ ($j\neq i$).
+First, we filter all pedestrians who are not in the range of sight
+of pedestrian $i$. This condition is verified using the following
+formula:
 
 \[
-k=i+\begin{pmatrix}0 & -1\\
-1 & 0
-\end{pmatrix}\overrightarrow{ii'}
+\overrightarrow{ii'}\bullet\overrightarrow{ij'}<0
 \]
-The following must be valid:
+
+This filter is represents the fact that a pedestrian (in most cases)
+is not aware of what each of the pedestrians that are behind him are
+doing. Hence, they are ignored. Once filtered, the pedestrian will
+try to face towards the direction that think is best for avoiding
+all the obstacles. This factor is represented using the social force
+formula from Helbing's model.
 
 \[
-(k_{x}-i_{x})*(j_{y}-i_{y})-(k_{y}-i_{y})*(j_{x}-i_{x})>0
+F_{ext}(i)=\sum_{j}F_{i',j'}+F_{i'j}=\sum_{j}(\alpha_{ff}e^{-dist(i',j')/\beta_{ff}}+\alpha_{fp}e^{-dist(i',j')/\beta_{fp}})
 \]
 
-Once filtered, the force is calculated for every other FVP. The repulsion
-force between i' and j' is defined as follows:
+where $\alpha_{x}$ and $\beta_{x}$ are predefined constants.
 
-\[
-F_{ext}(i)=\sum_{j}F_{i',j'}=\sum_{j}\alpha e^{-dist(i',j')/\beta}
-\]
-
-where $\alpha$ and $\beta$ are predefined constants. Afterwards,
-we calculate the repulsion force between i' and j using the same formula
-but different $\alpha$ and $\beta$. Afterwards, we calculate the
-force between pedestrian i and his FVP i', this is a force that pushes
-i' to be in its desired relative distance from the pedestrian. This
-force is represented with a spring of length ``reaction distance''
-and constant $K$. When we sum all these, we get the final $F_{ext}$.
-
-Fig 2: FVP force calculation.
+Here there are two terms in the $sum$. The first term represents
+the fact that $i$ does not want to be in the same location as $j$
+in the near future. Note that $j'$ represents the predicted location
+of $j$ inferred by another pedestrian (in this case, $i$) and because
+of this, it moves it's near future away of that predicted location.
+The seocond term, represents the same fact but taking in mind the
+current location of the pedestrian $j$. The same law applies to each
+of the walls on the simulation, the difference is that the closest
+point on the wall and and the future has to be calculated before applying
+the formula. Also, the constants $\alpha_{fw}$ and $\beta_{fw}$
+have different values.
 
 \begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{pedestrian-top-forces}\protect\caption{Fuerzas que actúan sobre el Future $i'$}
+\centering{}\includegraphics[scale=0.5]{pedestrian-top-forces}\protect\caption{External forces affecting future $i'$}
 \end{figure}
 
-\begin{enumerate}
+Then, the desire force that pedestrian $i$ will aply to his future
+is calculated. This force is modelled using two springs. The first
+spring hast its origin attached on $i$ and its end attached on $i'$
+and has a spring constant $K_{1}$. This spring will regulate the
+velocity that will be calculated on a previous step at witch the pedestrian
+$i$ will advance. The second spring, has its origin on $i'$ and
+the end attached to the closest point on the pedestrian target area
+and has a spring constant $K_{2}$. In order to avoid an oscilatory
+movement (in example, with a single pedestrian), a damping $\gamma$
+was added to this second spring. This spring represents how much te
+pedestrian wants to reach his target. A larger spring constant will
+force a more straight path, but possible with more collitions on its
+way.
+
+\begin{figure}[H]
+\centering{}\includegraphics[scale=0.5]{pedestrian-internal-forces}\protect\caption{Pedestrian internal forces}
+\end{figure}
+
+Because a pedestrian always tryes to reach his goal in in the sortest
+possible path (hipotesis 1). If it has to take a big detour of his
+ideal path, it will try to reduce his velocity drastically in order
+to avoid making a long travel. In orer to recreate this fact, the
+spring constant $K_{2}$ has to be variable and also dependant of
+the deviation angle. This constant is defined as $K_{2}\alpha\frac{1}{\theta},$
+whereas $\theta$is the angle between $\overrightarrow{ii'}$ and
+$\overrightarrow{i-objective_{i}}$. The constant in this relation
+is $\delta$.
+
+After this, the final $F_{i'}$ is computed by adding all the terms.
+$F_{i'}=F_{ext}(i)+F_{i\, s1}+F_{i\, s2}$
+
 \item FVP position update.
@@
 and the forces calculated in the previous step.
-
-\end{enumerate}
 
@@
 \end{itemize}
-\begin{enumerate}
 \item Pedestrian forces calculation.
@@
 and its magnitude is defined as Fd or desire force:
-
-\end{enumerate}
 
@@
 Where $\tau=0.5$
-\begin{enumerate}
+
 \item Pedestrian position update.
@@
 
-\end{enumerate}
 \end{enumerate}
@@
 
-//TODO todos los demás parámetros
+//TODO todos los demas parametros
 

### 2014-12-04 doc/informe/paper.tex
me olvide subir la ultima foto de pictures.pptx arreglo errores menores en el paper.tex. actualizo pdf.

@@
 of this, it moves it's near future away of that predicted location.
-The seocond term, represents the same fact but taking in mind the
-current location of the pedestrian $j$. The same law applies to each
-of the walls on the simulation, the difference is that the closest
-point on the wall and and the future has to be calculated before applying
+The second term, represents the same fact but taking in mind the current
+location of the pedestrian $j$. The same law applies to each of the
+walls on the simulation, the difference is that the closest point
+on the wall and and the future has to be calculated before applying
 the formula. Also, the constants $\alpha_{fw}$ and $\beta_{fw}$
 have different values.
+
+Figure 2.2 shows the external forces that a pedestrian $i$ suffers
+because of another pedestrian ($j$) and also the direction in wich
+$i$ desires to move.
 
@@
 
-Then, the desire force that pedestrian $i$ will aply to his future
-is calculated. This force is modelled using two springs. The first
-spring hast its origin attached on $i$ and its end attached on $i'$
-and has a spring constant $K_{1}$. This spring will regulate the
-velocity that will be calculated on a previous step at witch the pedestrian
+Then, the desire force that pedestrian $i$ will apply to his future
+is calculated. This force is modeled using two springs. The first
+spring has its origin attached on $i$ and its end attached on $i'$
+with a spring constant $K_{1}$. This spring will regulate the velocity
+that will be calculated on a posterior step at witch the pedestrian
 $i$ will advance. The second spring, has its origin on $i'$ and
-the end attached to the closest point on the pedestrian target area
-and has a spring constant $K_{2}$. In order to avoid an oscilatory
-movement (in example, with a single pedestrian), a damping $\gamma$
-was added to this second spring. This spring represents how much te
-pedestrian wants to reach his target. A larger spring constant will
-force a more straight path, but possible with more collitions on its
-way.
+the end attached to $objective_{i}$ and has a spring constant $K_{2}$.
+In order to avoid an oscilatory movement (in example, with a single
+pedestrian), a damping $\gamma$ was added to this second spring.
+This spring represents how much te pedestrian wants to reach his target.
+A larger spring constant will force a more straight path, but possible
+with more collitions on its way.
 

### 2014-12-07 src/main/java/ar/edu/itba/pedestriansim/back/config/CrossingConfig.java
todos los mapas ahora usan los mismos parametros. aplico los cambios hablados con daniel en la ultima reunion.

@@ -1,6 +1,5 @@
 package ar.edu.itba.pedestriansim.back.config;
 
-import org.apache.commons.lang3.tuple.Pair;
 import org.newdawn.slick.geom.Line;
 import org.newdawn.slick.geom.Vector2f;
 
@@ -11,8 +10,6 @@ import ar.edu.itba.pedestriansim.back.entity.PedestrianSource;
 import ar.edu.itba.pedestriansim.back.entity.Wall;
 import ar.edu.itba.pedestriansim.back.entity.mision.PedestrianMision;
 import ar.edu.itba.pedestriansim.back.entity.mision.PedestrianTargetArea;
-
-import com.google.common.collect.Range;
 
 public class CrossingConfig implements ApplicationConfigBuilder {
 
@@ -29,7 +26,6 @@ public class CrossingConfig implements ApplicationConfigBuilder {
 	@Override
 	public PedestrianAppConfig get() {
 		PedestrianAppConfig config = _defaultBuilder.get();
-		config.pedestrianFactory().setPedestrianAlphaBeta(Pair.of(1000f, Range.closed(0.5f, 0.6f)));
 		addWalls(config.pedestrianArea());
 		addSource1(config.pedestrianArea());
 		addSource2(config.pedestrianArea());

### 2014-12-07 src/main/java/ar/edu/itba/pedestriansim/back/config/DefaultPedestrianAppConfig.java

@@ -18,9 +18,9 @@ public class DefaultPedestrianAppConfig implements ApplicationConfigBuilder {
 		Range<Float> mass = Range.closed(60f, 80f);
 		Range<Float> velocity = Range.closed(1.2f, 1.4f);
 		Range<Float> r = Range.closed(0.25f, 0.29f);
-		Pair<Float, Range<Float>> pedestrianAlphaBeta = Pair.of(1000f, Range.closed(0.3f, 0.6f));
-		Pair<Float, Float> wallAlphaBeta = Pair.of(5000f, .15f);
-		Pair<Float, Float> futurePedestrianAlphaBeta = Pair.of(1000f, 0.2f);
+		Pair<Float, Range<Float>> pedestrianAlphaBeta = Pair.of(1000f, Range.closed(0.4f, 0.5f));
+		Pair<Float, Float> wallAlphaBeta = Pair.of(10000f, 0.1f);
+		Pair<Float, Float> futurePedestrianAlphaBeta = Pair.of(1000f, 0.1f);
 		return new PedestrianAppConfig()
 			.makeNewRun(true)
 			.setTimeStep(new BigDecimal(1 / 1000f).setScale(5, RoundingMode.UP))

### 2014-12-07 src/main/java/ar/edu/itba/pedestriansim/back/config/HallwayConfig.java

@@ -1,6 +1,5 @@
 package ar.edu.itba.pedestriansim.back.config;
 
-import org.apache.commons.lang3.tuple.Pair;
 import org.newdawn.slick.geom.Line;
 import org.newdawn.slick.geom.Vector2f;
 
@@ -11,8 +10,6 @@ import ar.edu.itba.pedestriansim.back.entity.PedestrianSource;
 import ar.edu.itba.pedestriansim.back.entity.Wall;
 import ar.edu.itba.pedestriansim.back.entity.mision.PedestrianMision;
 import ar.edu.itba.pedestriansim.back.entity.mision.PedestrianTargetArea;
-
-import com.google.common.collect.Range;
 
 public class HallwayConfig implements ApplicationConfigBuilder {
 
@@ -31,7 +28,6 @@ public class HallwayConfig implements ApplicationConfigBuilder {
 	@Override
 	public PedestrianAppConfig get() {
 		PedestrianAppConfig config = _defaultBuilder.get();
-		config.pedestrianFactory().setPedestrianAlphaBeta(Pair.of(1000f, Range.closed(0.3f, 0.4f)));
 		addWalls(config.pedestrianArea());
 		addSource1(config.pedestrianArea());
 		addSource2(config.pedestrianArea());

### 2014-12-07 src/main/java/ar/edu/itba/pedestriansim/back/config/SquareRoomConfig.java

@@ -1,10 +1,7 @@
 package ar.edu.itba.pedestriansim.back.config;
 
-import org.apache.commons.lang3.tuple.Pair;
 import org.newdawn.slick.geom.Line;
 import org.newdawn.slick.geom.Vector2f;
-
-import com.google.common.collect.Range;
 
 import ar.edu.itba.common.rand.UniformRandomGenerator;
 import ar.edu.itba.pedestriansim.back.entity.PedestrianAppConfig;
@@ -42,7 +39,6 @@ public class SquareRoomConfig implements ApplicationConfigBuilder {
 	@Override
 	public PedestrianAppConfig get() {
 		PedestrianAppConfig config = _defaultBuilder.get();
-		config.pedestrianFactory().setPedestrianAlphaBeta(Pair.of(1000f, Range.closed(0.3f, 0.4f)));
 		addWalls(config.pedestrianArea());
 		addSource1(config.pedestrianArea());
 		return config;

### 2014-12-07 src/main/java/ar/edu/itba/pedestriansim/back/entity/Pedestrian.java

@@ -90,10 +90,9 @@ public class Pedestrian {
 	public void recenterFuture() {
 		Vector2f targetCenter = getTargetSelection().getTarget().getClosesPoint(getBody().getCenter());
 		float distance = _reactionDistance;
-		Vector2f cache = new Vector2f();
-		Vectors.pointBetween(getBody().getCenter(), targetCenter, distance, cache);
-		getFuture().getBody().setCenter(cache);
-		
+		Vector2f result = new Vector2f();
+		Vectors.pointBetween(getBody().getCenter(), targetCenter, distance, result);
+		getFuture().getBody().setCenter(result);
 	}
 
 	public float getReactionDistance() {

### 2014-12-07 src/main/java/ar/edu/itba/pedestriansim/back/entity/PedestrianForces.java

@@ -12,11 +12,6 @@ public class PedestrianForces {
 	private RepulsionForce repulsionForceModel;
 
 	/**
-	 * Fuerza de repulsion entre una pared y una pocision
-	 */
-	private RepulsionForce wallRepulsionForceModel;
-
-	/**
 	 * Limite inferior para la aplicacion de la suma de los valores obtenidos
 	 * con @repulsionForceModel
 	 */
@@ -85,13 +80,5 @@ public class PedestrianForces {
 
 	public PedestrianForce getForceOnFuture() {
 		return forceOnFuture;
-	}
-	
-	public void setWallRepulsionForceModel(RepulsionForce wallRepulsionForceModel) {
-		this.wallRepulsionForceModel = wallRepulsionForceModel;
-	}
-	
-	public RepulsionForce getWallRepulsionForceModel() {
-		return wallRepulsionForceModel;
 	}
 }

### 2014-12-07 src/main/java/ar/edu/itba/pedestriansim/back/entity/force/PedestrianFutureAdjustmentForce.java

@@ -6,8 +6,6 @@ import ar.edu.itba.pedestriansim.back.entity.Pedestrian;
 import ar.edu.itba.pedestriansim.back.entity.PedestrianFuture;
 import ar.edu.itba.pedestriansim.back.entity.physics.Vectors;
 
-import com.google.common.base.Preconditions;
-
 public class PedestrianFutureAdjustmentForce implements PedestrianForce {
 
 	private final float _kAlign;
@@ -23,46 +21,38 @@ public class PedestrianFutureAdjustmentForce implements PedestrianForce {
 
 	@Override
 	public Vector2f apply(Pedestrian input) {
-		return new Vector2f()
-			.add(springAlignmentForce(input))
-			.add(springSeparationPosition(input));
-	}
-
-	private Vector2f springAlignmentForce(Pedestrian input) {
-		PedestrianFuture future = input.getFuture();
 		Vector2f position = input.getBody().getCenter();
 		Vector2f target = input.getTargetSelection().getTarget().getClosesPoint(position);
+		return new Vector2f()
+			.add(springAlignmentForce(input, target))
+			.add(springSeparationPosition(input, target));
+	}
+
+	private Vector2f springAlignmentForce(Pedestrian input, Vector2f target) {
+		PedestrianFuture future = input.getFuture();
+		Vector2f position = input.getBody().getCenter();
 		return Vectors.pointBetween(position, target, input.getReactionDistance(), positionCache)
 			.sub(future.getBody().getCenter())
 			.scale(_kAlign)
 			.add(new Vector2f(future.getBody().getVelocity()).scale(-_sigma));
 	}
 
-	private Vector2f springSeparationPosition(Pedestrian input) {
-		Vector2f pedestrianCenter = input.getBody().getCenter();
+	private Vector2f springSeparationPosition(Pedestrian input, Vector2f target) {
 		Vector2f pedestrianFutureCenter = input.getFuture().getBody().getCenter();
-		Vector2f target = input.getTargetSelection().getTarget().getClosesPoint(pedestrianCenter); 
-		float deviationAngle = angle(pedestrianCenter, target, pedestrianFutureCenter);
+		Vector2f position = input.getBody().getCenter();
+		float deviationAngle = angle(position, target, pedestrianFutureCenter);
 		float angleDeviationDecay = 1;
-		if (deviationAngle > 1) {
-			// XXX: careful with 0 division here!! 
[…]

### 2014-12-07 src/main/java/ar/edu/itba/pedestriansim/back/factory/PedestrianForcesFactory.java

@@ -13,11 +13,10 @@ public class PedestrianForcesFactory {
 	public PedestrianForces build(PedestrianAppConfig config) {
 		PedestrianForces forces = new PedestrianForces();
 		forces.setRepulsionForceModel(new ExponentialRepulsionForce());
-		forces.setWallRepulsionForceModel(new ExponentialRepulsionForce());
 		forces.setExternalForceRadiusThreshold(config.getExternalForceRadiusThreshold());
 		forces.setExternalForceThreshold(config.getExternalForceThreshold());
 		forces.setDesireForce(new ReactionDistanceDesireForce(FunctionType.LINEAR));
-		forces.setForceOnFuture(new PedestrianFutureAdjustmentForce(150, 10, 100));
+		forces.setForceOnFuture(new PedestrianFutureAdjustmentForce(100, 10, 100));
 		forces.setCollisitionModel(new SpringForceModel());
 		return forces;
 	}

### 2014-12-07 src/main/java/ar/edu/itba/pedestriansim/back/logic/FutureForceUpdaterComponent.java

@@ -53,13 +53,13 @@ public class FutureForceUpdaterComponent extends PedestrianAreaStep {
 
 	private Vector2f obstacleCollitionForces(Pedestrian subject, PedestrianArea input) {
 		final Vector2f totalRepulsionForce = new Vector2f();
-		RepulsionForce repulsionForce = _forces.getWallRepulsionForceModel();
+		RepulsionForce repulsionForce = _forces.getRepulsionForceModel();
 		for (Wall wall : input.obstacles()) {
 			Line line = wall.line();
 			RigidBody future = subject.getFuture().getBody();
 			line.getClosestPoint(future.getCenter(), _wallClosestPointCache);
 			totalRepulsionForce
-				.add(_forces.getCollisitionModel().getForce(future, wall))
+//				.add(_forces.getCollisitionModel().getForce(future, wall))
 				.add(repulsionForce.between(future.getCenter(), _wallClosestPointCache, subject.wallRepulsionForceValues()))
 			;
 		}

### 2014-12-07 doc/informe/paper.tex
agrego secciones habladas con daniel en la ultima reunion. correciones varias.

@@
 
-\subsection{Definition}
+\subsection{Geometrical definition}
 
@@
 
-Fig 1: Pedestrian and his FVP.
+Figure \ref{fig:Pedestrian-top-view} shows a pedestrian geomtrical
+definition:
 
 \begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{pedestrian-top}\protect\caption{Pedestrian top view}
+\centering{}\includegraphics[scale=0.5]{pedestrian-top}\protect\caption{\label{fig:Pedestrian-top-view}Pedestrian top view}
 \end{figure}
 
-In the document, we will call pedestrians with a letter and FVP of
-pedestrian x will be called x'.\\
+Figure \ref{fig:Pedestrian-vectors} shows all the vectorial definition
+that will be used:
 
-\subsection{Algorithm}
+\begin{figure}[H]
+\centering{}\includegraphics[scale=0.5]{geometry}\protect\caption{\label{fig:Pedestrian-vectors}Vectorial definitions}
+\end{figure}
+
+\vspace{1cm}
+
+\subsection{Dynamics of the FPV Model}
 
@@
 
-The pedestrian movement is calculated in four steps:
-\begin{enumerate}
-\item Calculate forces for each FVP.
-\item Update positions for each FVP.
-\item Calculate forces for each pedestrian.
-\item Update positions for each pedestrian.\\
+Each step is defined as follows:
 
-\end{enumerate}
-Each step is defined as follows:
-\begin{enumerate}
-\item FVP force calculation.
+\subsubsection{Forces}
+\begin{itemize}
+\item Dyamic of the FVP
 
 For each pedestrian $i$, the force that his future $i'$ will suffer
-is calculated in this step. The magnitude of this force will depend
-on two factors: by each of the other pedestrians and the walls that
-might exists surronding $i$. The final value of the force applied
-over the future $i'$ will be the addition of the latest two factors.
+is calculated in this step. The magnitude of this force is calculated
+using two factors:
 
-The fist factor is caluclated for each of the pedestrian $j$ ($j\neq i$).
-First, we filter all pedestrians who are not in the range of sight
-of pedestrian $i$. This condition is verified using the following
-formula:
+The fist factor is caluclated for each of the pedestrian $j$ ($j\neq i$)
+who is in the range of sight of pedestrian $i$. This restriction
+is verified using the following condition:
 
 \[
-\overrightarrow{ii'}\bullet\overrightarrow{ij'}<0
+\mathbf{r_{ii'}}\bullet\mathbf{r_{ij'}}<0
 \]
@@
 is not aware of what each of the pedestrians that are behind him are
-doing. Hence, they are ignored. Once filtered, the pedestrian will
-try to face towards the direction that think is best for avoiding
-all the obstacles. This factor is represented using the social force
-formula from Helbing's model.
+doing. Hence, they are ignored. The formula for
 
@@
 
-Figure 2.2 shows the external forces that a pedestrian $i$ suffers
-because of another pedestrian ($j$) and also the direction in wich
-$i$ desires to move.
+Figure \ref{fig:External-forces-affecting} shows the external forces
+that a pedestrian $i$ suffers because of another pedestrian ($j$)
+and also the direction in wich $i$ desires to move.
 
 \begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{pedestrian-top-forces}\protect\caption{External forces affecting future $i'$}
+\centering{}\includegraphics[scale=0.5]{pedestrian-top-forces}\protect\caption{\label{fig:External-forces-affecting}External forces affecting future
+$i'$}
 \end{figure}
@@
 After this, the final $F_{i'}$ is computed by adding all the terms.
-$F_{i'}=F_{ext}(i)+F_{i\, s1}+F_{i\, s2}$
-
-\item FVP position update.
-
-In this stage, the position of the FVP is updated with Euler's formula
-and the forces calculated in the previous step.
+$F_{i'}=F_{ext}(i)+F_{i\, s1}+F_{i\, s2}$.\\
 
@@
 
-At last, we find $F'_{i'}=F_{i'}+FL_{i'}+FA_{i'}$ and apply euler's
-movement equations.
+At last, we find $F'_{i'}=F_{i'}+FL_{i'}+FA_{i'}$ and apply movement
+equations.
 
 \end{itemize}
-\item Pedestrian forces calculation.
+\item Dynamic of the pedestrian
 
 The pedestrian always wants to move in the direction his FVP is pointing
-and its magnitude is defined as Fd or desire force:
+and its magnitude is defined as $F_{d}$ or desire force:
 
@@
 
-\item Pedestrian position update.
+\end{itemize}
 
-The new position of the pedestrian will be calculated using Euler's
-formula and the desire force calculated in the previous step.
+\subsubsection{Algorithm}
 
+The pedestrian movement is calculated in four steps:
+\begin{enumerate}
+\item Calculate forces for each FVP.
+\item Update positions for each FVP.
+\item Calculate forces for each pedestrian.
+\item Update positions for each pedestrian.
 \end{enumerate}
@@
 \begin{table}[H]
-{\scriptsize{}}%
+\centering{}{\scriptsize{}}%
 \begin{tabular}{|c|c|c|c|c|c|c|}
@@
 \hline 
-{\scriptsize{}$\alpha=800,\,\beta=[0.65,\,0.85]$} & {\scriptsize{}(1.800, 0.748) } & {\scriptsize{}(34.600, 8.333) } & {\scriptsize{}(1.024, 0.016) } & {\scriptsize{}(1.910, 0.022) } & {\scriptsize{}(2.392, 0.005) } & {\scriptsize{}(111.062, 19.122)}\tabularnewline
+{\scriptsize{}$\alpha=1000,\,\beta=[0.4,\,0.5]$} & {\scriptsize{}(1.800, 0.748) } & {\scriptsize{}(34.600, 8.333) } & {\scriptsize{}(1.024, 0.016) } & {\scriptsize{}(1.910, 0.022) } & {\scriptsize{}(2.392, 0.005) } & {\scriptsize{}(111.062, 19.122)}\tabularnewline
 \hline 

### 2015-01-24 doc/informe/paper.tex
actualizo carpeta informe con todo lo que esta subido en shareslatex

@@
-% Preview source code
-
-%% LyX 2.1.1 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
 \documentclass[english]{article}
@@
 
-Modelling and simulating the displacement of agents througth arbitrarily
-complex enviroments may be stated in an hierachical structure of mecahnisms
-depending mianly on the distance from the agent. This level has been
-named, from closer to further, as operational (walking, lowst level
-physical-computaitnal model for displacement), tactical (wayfinding,
-route chocie) and strategic (general activity planning) {[}Hoogonen
-and Bovy 2004{]}. These levels are not independient, factors affecting
-one level may impact in the following and vice versa, for example,
-the route choice may vary due to congestion of agents producing from
-previous route chice and walking behavior. Also, obstacles can impact
+Modelling and simulating the displacement of agents through arbitrarily
+complex environments may be stated in an hierarchical structure of mechanisms
+depending mainly on the distance from the agent. This level has been
+named, from closer to further, as operational (walking, lowest level
+physical-computational model for displacement), tactical (way-finding,
+route choice) and strategic (general activity planning) {[}Hoogonen
+and Bovy 2004{]}. These levels are not independent, factors affecting
+one level may impact in the following and vice-versa, for example,
+the route choice may vary due to congestion of agents produced from
+previous route choice and walking behavior. Also, obstacles can impact
 on the operational level or tactical level depending on the particular
-geometry of the enviroment. The particular mechanism we want to address
+geometry of the environment. The particular mechanism we want to address
 is the avoidance of obstacles being fixed or moving (another agent)
@@
 it with a higher level model which allows better and smoother collision
-avoidance behavior. Exisiting low level models can be taken from pedestrian
+avoidance behavior. Existing low level models can be taken from pedestrian
 dynamics field and in general this models can be classified into rule
@@
 
-A famous example of continuos and force based model is the Social
+A famous example of continuous and force based model is the Social
 Force Model {[}Helbing 1995, 2000{]}. In this model the dynamic for
 virtual pedestrians is derived from the Newton equation\textquoteright s
-considering the total force exceterd over each agent is the result
+considering the total force exerted over each agent is the result
 of three forces: Contact, Social and Driving Force. While the driving
@@
 force is repulsive and acts as a kind of collision avoidance force.
-However this social force term introduce several artefacts in some
+However this social force term introduces several artifices in some
 configurations {[}see for example Lakoba et al. 2005, Parisi et al
@@
 
-Cellular automata models make use of a spacial grid, which can be
-occuied or empty, along with a set of rules determining the evolution
+Cellular automaton models make use of a spatial grid, which can be
+occupied or empty, along with a set of rules determining the evolution
 and conflict resolution of virtual pedestrians moving over the cells
-of the grid. An emblematic celluar automata model is the one proposed
+of the grid. An emblematic cellular automaton model is the one proposed
 by Kirchner and Schadschneider {[}2002{]}.
 
-It have been also proposed hibrid models such as the Contractile Particle
-Model {[}Baglietto and Parisi, 2011{]} in which a continuos description
-of the space is combined with a set of simple rules governig the dynamcis
+Hybrid models have also been proposed such as the Contractile Particle
+Model {[}Baglietto and Parisi, 2011{]} in which a continuous description
+of the space is combined with a set of simple rules governing the dynamics
 of the system.
 
-The basic operational model as the ones described above can be improved
+The basic operational model -as the ones described above- can be improved
 if higher level mechanisms were added to manage more complex issues
-as eficient avoidance. Some recent examples can be found in the literature.
+as efficient avoidance. Some recent examples can be found in the literature.
 
@@
 force term by a new \textquotedblleft evasive\textquotedblright{}
-force which tends to avoid future collisions. The magnitud and direction
-of this force is calculaed considering the predictions of these possible
+force which tends to avoid future collisions. The magnitude and direction
+of this force is calculated considering the predictions of these possible
 collisions.
@@
 social force model is the driving force instead of interaction force,
-so in this work the authors propose a method for dinamically adjust
+so in this work the authors propose a method for dynamically adjusting
 the desired velocity following the gradient of a field given by a
-time map, in other words, the desired velocity is choosen as the quickest
+time map, in other words, the desired velocity is chosen as the quickest
 path to the objective taking into account the geometry and other agents
-(collision, congestions, jams, etc.). Also mounted on the SFM, Moussaïd
-et al. {[}2011{]} have presented a model using a \textquotedblleft cognitive
+(collision, congestion, jams, etc.). Also mounted on the SFM, Moussaïd
+et al. {[}2011{]} presented a model using \textquotedblleft cognitive
 heuristics\textquotedblright{} to determine the norm and direction
-of the desired velocity for each agent dinamically during the evolution
+of the desired velocity for each agent dynamically during the evolution
 of the system.
@@
 virtual agents should be concentrated in the on-line decision of the
-desired velocity. Similar to this approach, we postulate a new method
-derived from the methods used in robotics/artificial inteligence\dots{}
-The method deals with two aspects of the navigation mechanism. The
-first one is geometrical problem of finding intermediate goals when
-the final goal is not visible from the current position of the virtual
-agent. The second aspect is the local avoidance of other agents, which
-is performed via a reactive mechanism inspired in (robot navigation
-/ artificial inteligence) aproaches ¿?¿?¿\dots ..?¿?¿ {[} Ref.???
-??? {]}.
+desired velocity. Both direction and magnitude calculation of the desired velocity
+are the key differences with the SFM.
 
 The method proposed could be mounted on different basic displacement
-models like de SFM or the CPM, in the present work we have chosen
+models like the SFM or the CPM, in the present work we have chosen
 the first one.
@@
 
+//Hay que citar la de 1995 pero la que estamos describiendo es la del 2000
 {[}Helbing 1995, 2000{]} presents a Model in which each pedestrian
@@
 In its simplest form, the Social Force Model consist on three main
-terms. Each of there term represent a force that a pedestrian will
+terms. Each of them represents a force that a pedestrian will
 suffer in order to reach his objective.
@@
 towards his desired velocity of motion. This term is known as the
-``Desire Force'' and it's calculated as follows:
+``Driving Force'' and it's calculated as follows:
 
-\[
+\begin{equation}
+\label{eq:driving-force}
 F_{D_{i}}=m_{i}\frac{v_{di}e_{i}-v_{i}}{\tau}
-\]
+\end{equation}
 
-In this latest formula, $v_{di}$ represents the desire velocity for
+In this latest formula, $v_{di}$ represents the desire speed for
 the pedestrian $i$, $v_{i}$ is the current velocity and $e_{i}$
@@
 
-\[
+\begin{equation}
+\label{eq:desired-direction}
 e_{i}(t)=\frac{r_{i}^{k}-r_{i}(t)}{||r_{i}^{k}-r_{i}(t)||}
-\]
+\end{equation}
 
-where $r_{\alpha}(t)$ denotes the actual position of the pedestrian
-$i$ at the time $t$. The goal is represented as an area, and the
-vector $e_{i}$ will be pointing towards the closest pont. Figure
-$1.1$ shows en example of a pedestrian currenty moving in direction
-of $v$ but correcting its trayectory towards $e$.
+where $r_{i}(t)$ denotes the actual position of the pedestrian
+$i$ at the time $t$ and $r_{i}^{k}$ is the closest point from the goal
+(represented as an area) to the pedestrian. The unit vector $e_{i}$ will 
+be pointing towards the closest point. Figure \ref{fig:driving-force} shows an 
+example of a pedestrian currently moving in direction of $v$ but correcting its 
+trajectory towards $x$.
 
@@
 \begin{centering}
-\includegraphics[scale=0.4]{sfm/drivingforce}
+\includegraphics[scale=0.4]{pics/sfm/drivingforce}
 \par\end{centering}
 
-\protect\caption{Driving force}
+\protect\caption{\label{fig:driving-force}Driving force}
 \end{figure}
@@
 distance to other pedestrians and borders. This term is known as the
-``Social Force'' and it's caluclated as follows:
+``Social Force'' and it's calculated as follows:
 
@@
 
-In this formula the terms $A$ and $B$ represents constants that
-where determined by simulations and $\epsilon_{ij}$ represents the
+In this formula the terms $A$ and $B$ represent constants that
+were determined by simulations and $\epsilon_{ij}$ represents the
 distance from pedestrian $i$ towards pedestrian $j$. Figure $1.2$
-shows this vector grafically.
+shows this vector graphically.
 
@@
 \begin{centering}
-\includegraphics[scale=0.4]{sfm/sf}
+\includegraphics[scale=0.4]{pics/sfm/sf}
 \par\end{centering}
@@
 
-The third terms represents the granular force. This force represents
-the physical force that a pedestrians feels when in collision with
-another objects (pedestrian or wall). This granular force term is
+The third term represents the granular force. This force represents
+the physical force that a pedestrian feels when colliding with
+another object (pedestrian or wall). This granular force term is
 defined as follows:
@@
 \begin{centering}
-\includegraphics[scale=0.4]{sfm/ganular}
+\includegraphics[scale=0.4]{pics/sfm/ganular}
 \par\end{centering}
@@
 Afterwards $F_{i}=F_{G_{i}}+F_{S_{i}}+F_{D_{i}}$is calculated for
-each of the pedestrians on each simulation step and applyed to the
+each of the pedestrians on each simulation step and applied to the
 pedestrian until it reaches his goal.
@@
 
-Given that the SFM adds a fictional force on pedestrians, navigation
-stops imitating reality when there's a big quantity of pedestrians.
-Pedestrians also show a collision avoidance method that resembles
-magnetism, with movements that are clearly governed by the squared
-distance to the other pedestrian. Also, SFM didn't have the same values
-as well known metrics for real-case scenarios such as the flow of
-pedestrians going out a door and the fundamental diagram.
+Given that the SFM adds a fictional force on pedestrians, navigation doesn't resemble reality for high pedestrian densities.
+Also, SFM didn't have the same values as well known metrics for real-case scenarios such as the flow of pedestrians going out a door and the fundamental diagram.
 
-Because of this, we present a new model.
+Because of this, we present a new model in which the social force from equation \ref{eq:driving-force} affecting directly on each pedestrian is eliminated and replaced with a desire force facing a short term objective.
+This force is created using equation \ref{eq:desired-direction} replacing $r_{i}^{k}$ with the vector facing the closest point on the short term objective area.
 
@@
 \item The pedestrian's movement is influenced by other pedestrians. Depending
-on the distance between the two of them and the predicted trayectory,
+on the distance between the two of them and the predicted trajectory,
 the pedestrian will feel the need to change his route to be able to
@@
 
-Called FVP, it represents a point at a relative distance from the
-pedestrian's center. It's a dynamic objective.
+Called future virtual particle (FVP), it represents a point at a
+relative distance from the pedestrian's center. It's a dynamic objective.
 
-It is defined as a$1$ $[kg]$ mass. Not collisionable.
+It is defined as a $1\,[kg]$ mass. Not collisionable.
 
@@
 Represents the speed the pedestrian would walk if he was alone. Varies
-randomly between$[1.2,1.4]$ $[m/s]$.
+with a uniform distribution between $[1.2,1.4]\,[m/s]$.
 
-\item Reaction distance
+\item Reaction distance ($RD$)
 
@@
 
-Figure \ref{fig:Pedestrian-top-view} shows a pedestrian geomtrical
+Figure \ref{fig:Pedestrian-top-view} shows a pedestrian geometrical
 definition:
@@
 \begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{pedestrian-top}\protect\caption{\label{fig:Pedestrian-top-view}Pedestrian top view}
+\centering{}\includegraphics[scale=0.5]{pics/pedestrian-top}\protect\caption{\label{fig:Pedestrian-top-view}Pedestrian top view}
 \end{figure}
+\vspace{1cm}
+Pedestrians will be named after a letter (i.e: $i$ or $j$) and the same letter with a apostrophe will represent it's FVP (i.e: $i'$ or $j'$)\\
 
@@
 \begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{geometry}\protect\caption{\label{fig:Pedestrian-vectors}Vectorial definitions}
+\centering{}\includegraphics[scale=0.5]{pics/geometry}\protect\caption{\label{fig:Pedestrian-vectors}Vectorial definitions}
 \end{figure}
@@
 
-\subsection{Dynamics of the FPV Model}
+\subsection{Dynamics of the FVP Model}
+
+In this section all the forces acting on the FVPM will be defined
+
+\subsubsection{Forces}
+\begin{itemize}
+\item Dynamic of the FVP
 
 Each pedestrian has to reach the long term objective at some point,
-to ensure this, the FVP always feels the need to be aligned with the
-shortest path to the long term objective. On the other hand, there
+to ensure this, the FVP needs to be aligned with the
+shortest path to the long term objective $\mathbf{o}$. On the other hand, there
 are sometimes obstacles in the way, which will make this impossible,
@@
 
-Each step is defined as follows:
+To model this situations, two types of forces act over the FVP:
 
-\subsubsection{Forces}
 \begin{itemize}
-\item Dyamic of the FVP
+\item Internal force
+\\
+\\
+This force will guide the pedestrian on the shortest path $\mathbf{ox_i}$ and minimize the time needed to reach the long term goal. This force is modeled using two springs:
+\\
+\iffalse
+This forces will try to keep the FVP aligned with $\mathbf{o}$ and at the same time, 
+keep the FVP at $RD$ from the pedestrian.
 
-For each pedestrian $i$, the force that his future $i'$ will suffer
-is calculated in this step. The magnitude of this force is calculated
-using two factors:
+This (first) spring will regulate the velocity
+that will be calculated on a posterior step at which the pedestrian
+$i$ will advance. 
+...
+which pushes the FVP towards its desired length.
+At the same time, a force pushing the FVP towards his original
+alingment, defined
 
-The fist factor is caluclated for each of the pedestrian $j$ ($j\neq i$)
+\fi
+
+The first spring starts on $x_{i'}$ and ends on the point at distance $RD$ on vector $\mathbf{x_{i}o}$ with a spring constant $K_{1}$.
+This spring represents how much the pedestrian wants to reach his target.
+A larger spring constant will force a more straight path, but possible
+with more collisions on its way.
+In order to avoid an oscillatory movement (i.e: with a single pedestrian), a 
+damping $\gamma$ was added to this spring.
+
+The second spring starts on $x_i$, ends on $x_i'$ and has a steady 
+distance of $RD$ with a spring constant $K_s(\theta)$ 
+where $\theta$ is the angle between $\mathbf{u}$ and $\mathbf{r}$.
+With this spring the FVP will tend to always be at $RD$ distance 
+from the pedestrian.
+Because a pedestrian always tries to reach his goal in the shortest
+possible path (hypothesis 1), if it has to take a big detour of his
+ideal path, it will try to reduce his velocity drastically in order
+to avoid making a long travel. To recreate this, the
+spring constant has to be dependant of the deviation angle. 
+\[
+K_s(\theta) = \frac{K_{2}}{\theta}
+\]
+
+Given pedestrian $i$, the equation for his internal force is:
+
+\begin{equation}
+\iffalse
+F_s(r,\theta)=K_s(\theta)\frac{\vec{ii'}}{\mid\vec{ii'}\mid}(r_{max}-r_{ii'})
+\fi
+F_{internal}(i)=K_{1}*(|r|-RD)+K_{2}(\theta_{i})+K_{2}(\theta_{i})*(???)
+\end{equation}
+
+\begin{figure}[H]
+\centering{}\includegraphics[scale=0.5]{pics/pedestrian-internal-forces}\protect\caption{Pedestrian internal forces}
+\end{figure}
+
+\item Avoidance forces
+\\
+\\
+This force will produce avoidance movements when obstactes are detected on the path.
+The magnitude of this force is calculated using two factors:
+\\
+The first factor is calculated for each of the pedestrian $j$ ($j\neq i$)
 who is in the range of sight of pedestrian $i$. This restriction
@@
 
-This filter is represents the fact that a pedestrian (in most cases)
-is not aware of what each of the pedestrians that are behind him are
-doing. Hence, they are ignored. The formula for
+This filter represents the fact that a pedestrian (in most cases)
+does not make decisions based on obstacles behind him. Hence,
+they are ignored. The formula for the external forces that the
+FVP $i$ feels is defined as follows
 
 \[
-F_{ext}(i)=\sum_{j}F_{i',j'}+F_{i'j}=\sum_{j}(\alpha_{ff}e^{-dist(i',j')/\beta_{ff}}+\alpha_{fp}e^{-dist(i',j')/\beta_{fp}})
+F_{ext}(i)=\sum_{j}F_{i',j'}+F_{i'j}=\sum_{j}(\alpha_{ff}e^{-dist(i',j')/\beta_{ff}})+\sum_{j}(\alpha_{fp}e^{-dist(i',j')/\beta_{fp}})
 \]
@@
 
-Here there are two terms in the $sum$. The first term represents
+The first term of the sum acts as a repulsion force between $i$ and $j$
+FVPs, resulting in the avoidance of a future collision.
+The second term uses this same principle but calculates the repulsion
+force between $j's$ FVP and $i$.
+Repulsion against walls is calculated in the same way, by using the
+closest point between the FVP and the wall and special values for
+$\alpha_{fw}$ and $\beta_{fw}$ for the calculation.
+
+\iffalse
+The first term of the sum represents
 the fact that $i$ does not want to be in the same location as $j$
@@
 have different values.
+\fi
 
@@
 that a pedestrian $i$ suffers because of another pedestrian ($j$)
-and also the direction in wich $i$ desires to move.
+and also the direction in which $i$ desires to move.
 
 \begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{pedestrian-top-forces}\protect\caption{\label{fig:External-forces-affecting}External forces affecting future
+\centering{}\includegraphics[scale=0.5]{pics/pedestrian-top-forces}\protect\caption{\label{fig:External-forces-affecting}External forces affecting future
 $i'$}
@@
 
-Then, the desire force that pedestrian $i$ will apply to his future
-is calculated. This force is modeled using two springs. The first
-spring has its origin attached on $i$ and its end attached on $i'$
-with a spring constant $K_{1}$. This spring will regulate the velocity
-that will be calculated on a posterior step at witch the pedestrian
-$i$ will advance. The second spring, has its origin on $i'$ and
-the end attached to $objective_{i}$ and has a spring constant $K_{2}$.
-In order to avoid an oscilatory movement (in example, with a single
-pedestrian), a damping $\gamma$ was added to this second spring.
-This spring represents how much te pedestrian wants to reach his target.
-A larger spring constant will force a more straight path, but possible
-with more collitions on its way.
-
-\begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{pedestrian-internal-forces}\protect\caption{Pedestrian internal forces}
-\end{figure}
-
-Because a pedestrian always tryes to reach his goal in in the sortest
-possible path (hipotesis 1). If it has to take a big detour of his
-ideal path, it will try to reduce his velocity drastically in order
-to avoid making a long travel. In orer to recreate this fact, the
-spring constant $K_{2}$ has to be variable and also dependant of
-the deviation angle. This constant is defined as $K_{2}\alpha\frac{1}{\theta},$
-whereas $\theta$is the angle between $\overrightarrow{ii'}$ and
-$\overrightarrow{i-objective_{i}}$. The constant in this relation
-is $\delta$.
+\end{itemize}
 
@@
 
-To avoid high simetry situations, a low noise $P=10\%$ is added to
+To avoid high symetry situations, a low noise $P=10\%$ is added to
 $F$. There are two ways to apply this noise:
@@
 \[
-F_{desire_{i}}=m_{i}\frac{\frac{dist(i',i)}{dist_{react}}e_{i}-v_{i}}{\tau}
+F_{desire_{i}}=m_{i}\frac{\frac{|\vec{ii'}|}{|\vec{r}_{max}|}\vec{e_{i}}-\vec{v}_{i}}{\tau}
 \]
@@
 Where $\tau=0.5$
+
+\textit{*It is important to note that the only deviation from the SFM in this
+equation is the $k\vec{e}_i$ term. As described above, this model focuses on improving
+the SFM through dynamically adjusting the desired velocity.}
 
@@
 
-The results where compared to the SFM using the values propposed by
+The results where compared to the SFM using the values proposed by
 Dirk Helbing {[}2{]}. The test scenarios where crossing and hallway
-for they present the main two types of simmetry (90 degrees and 180
+for they present the main two types of symmetry (90 degrees and 180
 degrees).

### 2015-02-05 doc/informe/paper.tex

@@
+% Preview source code
+
+%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
+%% Do not edit unless you really know what you are doing.
 \documentclass[english]{article}
@@
 \usepackage{float}
-\usepackage{amsthm}
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{graphicx}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
+
+\usepackage{amsthm}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+%% Because html converters don't know tabularnewline
+\providecommand{\tabularnewline}{\\}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
@@
 \numberwithin{figure}{section}
+
+\usepackage{babel}
 
@@
 Modelling and simulating the displacement of agents through arbitrarily
-complex environments may be stated in an hierarchical structure of mechanisms
-depending mainly on the distance from the agent. This level has been
-named, from closer to further, as operational (walking, lowest level
-physical-computational model for displacement), tactical (way-finding,
+complex environments may be stated in an hierarchical structure of
+mechanisms depending mainly on the distance from the agent. This level
+has been named, from closer to further, as operational (walking, lowest
+level physical-computational model for displacement), tactical (way-finding,
 route choice) and strategic (general activity planning) {[}Hoogonen
@@
 Force Model {[}Helbing 1995, 2000{]}. In this model the dynamic for
-virtual pedestrians is derived from the Newton equation\textquoteright s
-considering the total force exerted over each agent is the result
-of three forces: Contact, Social and Driving Force. While the driving
-force points towards the final objective of each pedestrian, the social
-force is repulsive and acts as a kind of collision avoidance force.
-However this social force term introduces several artifices in some
-configurations {[}see for example Lakoba et al. 2005, Parisi et al
-2009{]}.
+virtual pedestrians is derived from the Newton equation's considering
+the total force exerted over each agent is the result of three forces:
+Contact, Social and Driving Force. While the driving force points
+towards the final objective of each pedestrian, the social force is
+repulsive and acts as a kind of collision avoidance force. However
+this social force term introduces several artifices in some configurations
+{[}see for example Lakoba et al. 2005, Parisi et al 2009{]}.
 
@@
 Model {[}Baglietto and Parisi, 2011{]} in which a continuous description
-of the space is combined with a set of simple rules governing the dynamics
-of the system.
+of the space is combined with a set of simple rules governing the
+dynamics of the system.
 
@@
 modifying the social force model, basically, replacing the social
-force term by a new \textquotedblleft evasive\textquotedblright{}
-force which tends to avoid future collisions. The magnitude and direction
-of this force is calculated considering the predictions of these possible
-collisions.
+force term by a new ``evasive\textquotedblright{} force which tends
+to avoid future collisions. The magnitude and direction of this force
+is calculated considering the predictions of these possible collisions.
 
@@
 path to the objective taking into account the geometry and other agents
-(collision, congestion, jams, etc.). Also mounted on the SFM, Moussaïd
-et al. {[}2011{]} presented a model using \textquotedblleft cognitive
-heuristics\textquotedblright{} to determine the norm and direction
-of the desired velocity for each agent dynamically during the evolution
-of the system.
+(collision, congestion, jams, etc.). Also mounted on the SFM, Moussaad
+et al. {[}2011{]} presented a model using ``cognitive heuristics''
+to determine the norm and direction of the desired velocity for each
+agent dynamically during the evolution of the system.
 
@@
 virtual agents should be concentrated in the on-line decision of the
-desired velocity. Both direction and magnitude calculation of the desired velocity
-are the key differences with the SFM.
+desired velocity. Both direction and magnitude calculation of the
+desired velocity are the key differences with the SFM.
 
@@
 
-//Hay que citar la de 1995 pero la que estamos describiendo es la del 2000
-{[}Helbing 1995, 2000{]} presents a Model in which each pedestrian
-is subject to ``social forces''. This forces are a measure for the
-internal motivations of the individual to perform certain actions.
-In its simplest form, the Social Force Model consist on three main
-terms. Each of them represents a force that a pedestrian will
-suffer in order to reach his objective.
+The Social Force is a model presented by Helbing \cite{key-0,key-1}
+in several publications. This paper will focus on the latest version
+of the model \cite{key-1}. In his model, each pedestrian $i$ occupies
+a circular area of radius $r_{i}$ and is governed by thee forces.
+\[
+\vec{F_{i}}=\vec{F_{D_{i}}}+\vec{F_{S_{i}}}+\vec{F_{G_{i}}}
+\]
 
-The first term describes the acceleration that a pedestrian keeps
-towards his desired velocity of motion. This term is known as the
-``Driving Force'' and it's calculated as follows:
+This forces are a measure for the internal motivations of the individual
+to perform certain actions.
+
+The first term is known as the ``Driving Force''. It's calculated
+as follows:
 
 \begin{equation}
-\label{eq:driving-force}
-F_{D_{i}}=m_{i}\frac{v_{di}e_{i}-v_{i}}{\tau}
+\vec{F_{D_{i}}}=m_{i}\frac{v_{di}\vec{e_{i}}-\vec{v_{i}}}{\tau}\label{eq:driving-force}
 \end{equation}
 
-In this latest formula, $v_{di}$ represents the desire speed for
-the pedestrian $i$, $v_{i}$ is the current velocity and $e_{i}$
-represents the desired direction of motion of the pedestrian $i$
-and is calculated as follows:
-
 \begin{equation}
-\label{eq:desired-direction}
-e_{i}(t)=\frac{r_{i}^{k}-r_{i}(t)}{||r_{i}^{k}-r_{i}(t)||}
+\vec{e_{i}}=\frac{\vec{x}_{i}^{k}-\vec{x}_{i}(t)}{||\vec{x}_{i}^{k}-\vec{x}_{i}(t)||}\label{eq:desired-direction}
 \end{equation}
 
-where $r_{i}(t)$ denotes the actual position of the pedestrian
-$i$ at the time $t$ and $r_{i}^{k}$ is the closest point from the goal
-(represented as an area) to the pedestrian. The unit vector $e_{i}$ will 
-be pointing towards the closest point. Figure \ref{fig:driving-force} shows an 
-example of a pedestrian currently moving in direction of $v$ but correcting its 
-trajectory towards $x$.
+$\vec{F}_{D_{i}}$ represents the force that a pedestrian $i$ keeps
+towards his desired velocity of motion.
+
+$v_{di}$ is the desired speed for the pedestrian $i$.
+
+$\vec{e}{}_{i}$ is the desired direction of motion of the pedestrian
+$i$.
+
+$\vec{v}{}_{i}$ is the current velocity of the pedestrian $i$.
+
+$\vec{x}_{i}(t)$ is the actual position of the pedestrian $i$ at
+the time $t$.
+
+$x_{i}^{k}$ is the closest point from the goal (represented as an
+area) to pedestrian $i$. \\
+
+Figure \ref{fig:driving-force} shows an example of a pedestrian currently
+moving in direction of $\vec{v}$ but adjusting its trajectory towards
+\textbf{$X$}.
 
@@
 
-\protect\caption{\label{fig:driving-force}Driving force}
+\caption{\label{fig:driving-force}Driving force}
 \end{figure}
@@
 
-The second term represents the fact that a pedestrian keeps a certain
-distance to other pedestrians and borders. This term is known as the
-``Social Force'' and it's calculated as follows:
+The second term is known as the ``Social force''. It's calculated
+as follows:
 
-\[
-F_{S_{i}}=\sum_{j=1,j\ne i}^{N_{P}}Aexp(-\frac{\epsilon_{ij}}{B})\, e_{ij}^{n}
-\]
+\begin{equation}
+\vec{F}_{S_{i}}=\sum_{j=1,j\ne i}^{N_{P}}Aexp(-\frac{\epsilon_{ij}}{B})\,\vec{e}_{ij}^{n}\label{eq:social-force}
+\end{equation}
 
-In this formula the terms $A$ and $B$ represent constants that
-were determined by simulations and $\epsilon_{ij}$ represents the
-distance from pedestrian $i$ towards pedestrian $j$. Figure $1.2$
-shows this vector graphically.
+$\vec{F}_{S_{i}}$ represents the fact that a pedestrian keeps a certain
+distance to other pedestrians and borders.
+
+$N_{p}$ is the number of existing pedestrians.
+
+$A$ and $B$ are constants determined by simulations.
+
+$\epsilon_{ij}$ is the distance from $x_{i}$ towards $x_{j}$.
+
+$\vec{e}_{ij}^{n}$ is the unit vector from $x_{i}$ towards $x_{j}$.\\
+
+Figure \ref{fig:Social-Force} shows \ref{eq:social-force} graphically.
 
@@
 
-\protect\caption{Social Force}
+\caption{Social Force\label{fig:Social-Force}}
 \end{figure}
@@
 
-The third term represents the granular force. This force represents
-the physical force that a pedestrian feels when colliding with
-another object (pedestrian or wall). This granular force term is
-defined as follows:
+The third term is known as the ``Granular force''. It's calculated
+as follows:
 
-\[
-F_{G_{i}}=\sum_{j=1,j\ne i}^{N_{P}}[-\epsilon_{ij}k_{n}e_{ij}^{n}+v_{ij}^{t}\epsilon_{ij}k_{t}e_{ij}^{t}]\, g(\epsilon_{ij})
-\]
+\begin{equation}
+\vec{F}_{G_{i}}=\sum_{j=1,j\ne i}^{N_{P}}[-\epsilon_{ij}k_{n}\vec{e}_{ij}^{n}+v_{ij}^{t}\epsilon_{ij}k_{t}\vec{e}_{ij}^{t}]\, g(\epsilon_{ij})\label{eq:granular-force}
+\end{equation}
 
-Where: $\epsilon_{ij}=r_{ij}-(R_{i}+R_{j})$
+$\vec{F}_{G_{i}}$ represents the physical force that a pedestrian
+suffers when colliding with another object (pedestrian or wall).
+
+$k_{n}$ and $k_{t}$ are the normal and tangential friction coeficient
+respectively.
+
+$g$ is ???\\
+
+Figure \ref{fig:colliding-pedestrians} shows \ref{eq:granular-force}
+graphically.
 
@@
 
-\protect\caption{Example of two pedestrians in collision}
-
+\caption{Colliding pedestrians\label{fig:colliding-pedestrians}}
 \end{figure}
@@
 
-Afterwards $F_{i}=F_{G_{i}}+F_{S_{i}}+F_{D_{i}}$is calculated for
-each of the pedestrians on each simulation step and applied to the
-pedestrian until it reaches his goal.
+Afterwards $\vec{F}_{i}$ is calculated on each simulation step for
+each of the pedestrians and applied until all of them had reached
+their goal.
 
-Fixed parameter values: $A=2000\,[N]$, $B=0.08\,[m]$, $k_{n}=1.2\,10^{5}\,[\frac{N}{m}]$,
-$k_{t}=2.4\,10^{5}\,[\frac{kg}{m/s}]$ y $\tau=0.5\,[s]$.
+Fixed parameter values:
 
-While this model doesn't present a very real behaviour for pedestrians,
-it worked as a starting point for numerous projects.
+\begin{center}
+\begin{tabular}{|c|c|}
+\hline 
+Name & Value\tabularnewline
+\hline 
+\hline 
+$A$ & $2000\,[N]$\tabularnewline
+\hline 
+$B$ & $0.08\,[m]$\tabularnewline
+\hline 
+$k_{n}$ & $1.2\,10^{5}\,[\frac{N}{m}]$\tabularnewline
+\hline 
+$k_{t}$ & $2.4\,10^{5}\,[\frac{kg}{m/s}]$\tabularnewline
+\hline 
+$\tau$ & $0.5\,[s]$\tabularnewline
+\hline 
+\end{tabular}
+\par\end{center}
 
@@
 
-Given that the SFM adds a fictional force on pedestrians, navigation doesn't resemble reality for high pedestrian densities.
-Also, SFM didn't have the same values as well known metrics for real-case scenarios such as the flow of pedestrians going out a door and the fundamental diagram.
+Given that the SFM adds a fictional force on pedestrians, navigation
+doesn't resemble reality for high pedestrian densities. Also, SFM
+didn't have the same values as well known metrics for real-case scenarios
+such as the flow of pedestrians going out a door and the fundamental
+diagram.
 
-Because of this, we present a new model in which the social force from equation \ref{eq:driving-force} affecting directly on each pedestrian is eliminated and replaced with a desire force facing a short term objective.
-This force is created using equation \ref{eq:desired-direction} replacing $r_{i}^{k}$ with the vector facing the closest point on the short term objective area.
+Because of this, we present a new model in which the social force
+from equation \ref{eq:driving-force} affecting directly on each pedestrian
+is eliminated and replaced with a desire force facing a short term
+objective. This force is created using equation \ref{eq:desired-direction}
+replacing $r_{i}^{k}$ with the vector facing the closest point on
+the short term objective area.
 
@@
 The main effects that govern the motion of a pedestrian are the same
-as Helbin's:
+as Helbin's \cite{key-0,key-1}: 
 \begin{enumerate}
@@
 on the distance between the two of them and the predicted trajectory,
-the pedestrian will feel the need to change his route to be able to
-avoid the other pedestrians. It is because of this effect that pedestrians
+the pedestrian feels the need to change his route to be able to avoid
+the other pedestrians. It is because of this effect that pedestrians
 will need to recalculate their route as new pedestrians get closer
 to them. 
-\item Movement speed will be influenced by needs.
+\item Movement speed will be influenced by the presence of other pedestrians
+and obstacles.
 \end{enumerate}
@@
 
-Represents the space that this pedestrian occupies. Circle's radio
-is generated randomly to represent different types of pedestrians.
-The range of values is distributed uniformly in $[0.25,0.29]$$[cm]$.
+Represents the personal space of a pedetrian. The value of the radio
+is generated randomly for each pedestrian. The range of values is
+distributed uniformly in $[0.25,0.29]$$[cm]$.
 
@@
 Represented by a static area. When it is touched by a pedestrian,
-it is considered as accomplished. Multiple objectives can by defined
+it is considered as accomplished. Multiple objectives may by defined
 in a list, in this case, each of them must be reached in order.
@@
 
-Called future virtual particle (FVP), it represents a point at a
-relative distance from the pedestrian's center. It's a dynamic objective.
+Called future virtual particle (FVP), it represents a point at a relative
+distance from the pedestrian's center. It's a dynamic objective.
 
@@
 
-Represents the speed the pedestrian would walk if he was alone. Varies
-with a uniform distribution between $[1.2,1.4]\,[m/s]$.
+This is the speed the pedestrian would walk if he/she was alone. This
+represents the constant $v_{di}$ in ecuation \ref{eq:driving-force}.
+It takes a different value for each pedestrian. Varies with a uniform
+distribution between $[1.2,1.4]\,[m/s]$.
 
@@
 
-Figure \ref{fig:Pedestrian-top-view} shows a pedestrian geometrical
-definition:
+\begin{figure}[H]
+\centering{}\includegraphics[scale=0.5]{pics/pedestrian-top}\caption{\label{fig:pedestrian-geometry}Pedestrian geometry}
+\end{figure}
 
-\begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{pics/pedestrian-top}\protect\caption{\label{fig:Pedestrian-top-view}Pedestrian top view}
-\end{figure}
-\vspace{1cm}
-Pedestrians will be named after a letter (i.e: $i$ or $j$) and the same letter with a apostrophe will represent it's FVP (i.e: $i'$ or $j'$)\\
+For the sake of clarity. A single pedestrian will be named after a
+letter (i.e: $i$ or $j$) and the same letter with a apostrophe will
+represent it's FVP (i.e: $i'$ or $j'$)\\
 
-Figure \ref{fig:Pedestrian-vectors} shows all the vectorial definition
+Figure \ref{fig:pedestrian-vectors} shows all the vectorial definition
 that will be used:
@@
 \begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{pics/geometry}\protect\caption{\label{fig:Pedestrian-vectors}Vectorial definitions}
+\centering{}\includegraphics[scale=0.5]{pics/geometry}\caption{\label{fig:pedestrian-vectors}Vectorial definitions}
 \end{figure}
@@
 
-\subsubsection{Forces}
+\subsubsection{Calculatin of forces}
 \begin{itemize}
@@
 Each pedestrian has to reach the long term objective at some point,
-to ensure this, the FVP needs to be aligned with the
-shortest path to the long term objective $\mathbf{o}$. On the other hand, there
+to ensure this, the FVP needs to be aligned with the shortest path
+to the long term objective $\mathbf{o}$. On the other hand, there
 are sometimes obstacles in the way, which will make this impossible,
@@
 To model this situations, two types of forces act over the FVP:
+\begin{itemize}
+\item Internal force \\
+ \\
+ This force will guide the pedestrian on the shortest path $\mathbf{ox_{i}}$.
+This force is modeled using two springs:
 
-\begin{itemize}
-\item Internal force
-\\
-\\
-This force will guide the pedestrian on the shortest path $\mathbf{ox_i}$ and minimize the time needed to reach the long term goal. This force is modeled using two springs:
-\\
-\iffalse
-This forces will try to keep the FVP aligned with $\mathbf{o}$ and at the same time, 
-keep the FVP at $RD$ from the pedestrian.
-
-This (first) spring will regulate the velocity
-that will be calculated on a posterior step at which the pedestrian
-$i$ will advance. 
-...
-which pushes the FVP towards its desired length.
-At the same time, a force pushing the FVP towards his original
-alingment, defined
-
-\fi
-
-The first spring starts on $x_{i'}$ and ends on the point at distance $RD$ on vector $\mathbf{x_{i}o}$ with a spring constant $K_{1}$.
-This spring represents how much the pedestrian wants to reach his target.
-A larger spring constant will force a more straight path, but possible
-with more collisions on its way.
-In order to avoid an oscillatory movement (i.e: with a single pedestrian), a 
-damping $\gamma$ was added to this spring.
-
-The second spring starts on $x_i$, ends on $x_i'$ and has a steady 
-distance of $RD$ with a spring constant $K_s(\theta)$ 
-where $\theta$ is the angle between $\mathbf{u}$ and $\mathbf{r}$.
-With this spring the FVP will tend to always be at $RD$ distance 
-from the pedestrian.
+The first spring starts on $x_{i}$, ends on $x_{i}'$ and has a steady
+distance of $RD$ with a spring constant $K_{s}(\theta)$ where $\theta$
+is the angle between $\mathbf{u}$ and $\mathbf{r}$. With this spring
+the FVP will tend to always be at $RD$ distance from the pedestrian.
 Because a pedestrian always tries to reach his goal in the shortest
@@
 ideal path, it will try to reduce his velocity drastically in order
-to avoid making a long travel. To recreate this, the
-spring constant has to be dependant of the deviation angle. 
+to avoid making a long travel. To recreate this, the spring constant
+has to be dependant of the deviation angle. 
 \[
-K_s(\theta) = \frac{K_{2}}{\theta}
+K_{s}(\theta)=\frac{K_{2}}{\theta}
 \]
+
+The second spring starts on $x_{i'}$ and ends on the point at distance
+$RD$ on vector $\mathbf{x_{i}o}$ with a spring constant $K_{1}$.
+This spring represents how much the pedestrian wants to reach his
+target. A larger spring constant will force a more straight path,
+but possible with more collisions on its way. In order to avoid an
+oscillatory movement (i.e: with a single pedestrian), a damping $\gamma$
+was added to this spring.\\
 
@@
 \begin{equation}
-\iffalse
-F_s(r,\theta)=K_s(\theta)\frac{\vec{ii'}}{\mid\vec{ii'}\mid}(r_{max}-r_{ii'})
-\fi
 F_{internal}(i)=K_{1}*(|r|-RD)+K_{2}(\theta_{i})+K_{2}(\theta_{i})*(???)
@@
 
+$\iffalse F_{s}(r,\theta)=K_{s}(\theta)\frac{\vec{ii'}}{\mid\vec{ii'}\mid}(r_{max}-r_{ii'})\fi$
+
 \begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{pics/pedestrian-internal-forces}\protect\caption{Pedestrian internal forces}
+\centering{}\includegraphics[scale=0.5]{pics/pedestrian-internal-forces}\caption{Pedestrian internal forces}
 \end{figure}
 
-\item Avoidance forces
+\item Avoidance forces \\
  \\
-\\
-This force will produce avoidance movements when obstactes are detected on the path.
-The magnitude of this force is calculated using two factors:
+ This force will produce avoidance movements when obstactes are detected
+on the path. The magnitude of this force is calculated using two factors:
 \\
@@
 This filter represents the fact that a pedestrian (in most cases)
-does not make decisions based on obstacles behind him. Hence,
-they are ignored. The formula for the external forces that the
-FVP $i$ feels is defined as follows
+does not make decisions based on obstacles behind him. Hence, they
+are ignored. The formula for the external forces that the FVP $i$
+feels is defined as follows
 
@@
 
-The first term of the sum acts as a repulsion force between $i$ and $j$
-FVPs, resulting in the avoidance of a future collision.
-The second term uses this same principle but calculates the repulsion
-force between $j's$ FVP and $i$.
-Repulsion against walls is calculated in the same way, by using the
-closest point between the FVP and the wall and special values for
-$\alpha_{fw}$ and $\beta_{fw}$ for the calculation.
+The first term of the sum acts as a repulsion force between $i$ and
+$j$ FVPs, resulting in the avoidance of a future collision. The second
+term uses this same principle but calculates the repulsion force between
+$j's$ FVP and $i$. Repulsion against walls is calculated in the
+same way, by using the closest point between the FVP and the wall
+and special values for $\alpha_{fw}$ and $\beta_{fw}$ for the calculation.
 
-\iffalse
-The first term of the sum represents
-the fact that $i$ does not want to be in the same location as $j$
-in the near future. Note that $j'$ represents the predicted location
-of $j$ inferred by another pedestrian (in this case, $i$) and because
-of this, it moves it's near future away of that predicted location.
-The second term, represents the same fact but taking in mind the current
-location of the pedestrian $j$. The same law applies to each of the
-walls on the simulation, the difference is that the closest point
-on the wall and and the future has to be calculated before applying
-the formula. Also, the constants $\alpha_{fw}$ and $\beta_{fw}$
-have different values.
-\fi
+\iffalse The first term of the sum represents the fact that $i$
+does not want to be in the same location as $j$ in the near future.
+Note that $j'$ represents the predicted location of $j$ inferred
+by another pedestrian (in this case, $i$) and because of this, it
+moves it's near future away of that predicted location. The second
+term, represents the same fact but taking in mind the current location
+of the pedestrian $j$. The same law applies to each of the walls
+on the simulation, the difference is that the closest point on the
+wall and and the future has to be calculated before applying the formula.
+Also, the constants $\alpha_{fw}$ and $\beta_{fw}$ have different
+values. \fi
 
@@
 \begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{pics/pedestrian-top-forces}\protect\caption{\label{fig:External-forces-affecting}External forces affecting future
+\centering{}\includegraphics[scale=0.5]{pics/pedestrian-top-forces}\caption{\label{fig:External-forces-affecting}External forces affecting future
 $i'$}
@@
 The pedestrian always wants to move in the direction his FVP is pointing
-and its magnitude is defined as $F_{d}$ or desire force:
+and its magnitude is defined as $F_{d}$ or driving force:
 
 \[
-F_{desire_{i}}=m_{i}\frac{\frac{|\vec{ii'}|}{|\vec{r}_{max}|}\vec{e_{i}}-\vec{v}_{i}}{\tau}
+\vec{F}_{desire_{i}}=m_{i}\frac{\frac{|\vec{ii'}|}{|\vec{r}_{max}|}\vec{e_{i}}-\vec{v}_{i}}{\tau}
 \]
@@
 
-\textit{*It is important to note that the only deviation from the SFM in this
-equation is the $k\vec{e}_i$ term. As described above, this model focuses on improving
-the SFM through dynamically adjusting the desired velocity.}
+\textit{{*}It is important to note that the only deviation from the
+SFM in this equation is the $k\vec{e}_{i}$ term. As described above,
+this model focuses on improving the SFM through dynamically adjusting
+the desired velocity.}
 
@@
 
-The results where compared to the SFM using the values proposed by
-Dirk Helbing {[}2{]}. The test scenarios where crossing and hallway
-for they present the main two types of symmetry (90 degrees and 180
-degrees).
+The results where compared to the SFM \cite{key-1}. The test scenarios
+where crossing and hallway for they present the main types of symmetry
+(90 degrees and 180 degrees respectively).
 
@@
 
-When a pedestrian's body is touching another one, a counter is incremented,
-it won't be incremented again unless it separates and touch again.
-This counter represents the amount of collisions.
+The total amount of collisions between pedestrians.
 
@@
 
-When a pedestrian's body is touching another one, a counter is incremented
-by the time step of the simulation. This counter will represent the
-total time pedestrians were colliding.
+The sum of the duration of each collision.
 
@@
 
-//TODO
+The average of the average speed of each pedestrian.
 
@@
 
-When a pedestrian appears in the map, this time is recorded, once
-he reaches his goal, the travel time is calculated with this value.
-The average of all this times represents the average travel time.
+The average time that a pedestrian needed unit it reached the goal.
 
@@
 
-Each step, the distance a pedestrian has traveled from the source
-is saved. When this pedestrian reaches his goal, that distance is
-considered as finished and it is saved elsewhere. Afterwards, an average
-of all finished distances is calculated.
+The average distance that a pedestrian traveled unit it reached the
+goal.
 
@@
 
-Each step, the angle of the previous velocity of a pedestrian and
-the current one is saved and added to a total. When this pedestrians
-reaches his goal, this total is considered as finished and it is saved
-elsewhere. Afterwards, an average of all finished turn angles is calculated.
+The average angle turned by a pedestrian unit it reached the goal.
 
@@
 \begin{table}[H]
-\centering{}{\scriptsize{}}%
+\centering{}%
 \begin{tabular}{|c|c|c|c|c|c|c|}
 \hline 
-{\scriptsize{}Values} & {\scriptsize{}1} & {\scriptsize{}2} & {\scriptsize{}3} & {\scriptsize{}4} & {\scriptsize{}5} & {\scriptsize{}6}\tabularnewline
+{\scriptsize{Values}}  & {\scriptsize{1}}  & {\scriptsize{2}}  & {\scriptsize{3}}  & {\scriptsize{4}}  & {\scriptsize{5}}  & {\scriptsize{6}}\tabularnewline
 \hline 
 \hline 
-{\scriptsize{}$\alpha=1000,\,\beta=[0.4,\,0.5]$} & {\scriptsize{}(1.800, 0.748) } & {\scriptsize{}(34.600, 8.333) } & {\scriptsize{}(1.024, 0.016) } & {\scriptsize{}(1.910, 0.022) } & {\scriptsize{}(2.392, 0.005) } & {\scriptsize{}(111.062, 19.122)}\tabularnewline
+{\scriptsize{$\alpha=1000,\,\beta=[0.4,\,0.5]$}}  & {\scriptsize{(1.800, 0.748) }}  & {\scriptsize{(34.600, 8.333) }}  & {\scriptsize{(1.024, 0.016) }}  & {\scriptsize{(1.910, 0.022) }}  & {\scriptsize{(2.392, 0.005) }}  & {\scriptsize{(111.062, 19.122)}}\tabularnewline
 \hline 
-{\scriptsize{}$\alpha=2000,\,\beta=0.08$} & {\scriptsize{}(5.333, 2.625)} & {\scriptsize{}(12.333, 8.340) } & {\scriptsize{}(1.052, 0.003) } & {\scriptsize{}(1.876, 0.003) } & {\scriptsize{}(2.391, 0.002) } & {\scriptsize{}(106.185, 13.778)}\tabularnewline
+{\scriptsize{$\alpha=2000,\,\beta=0.08$}}  & {\scriptsize{(5.333, 2.625)}}  & {\scriptsize{(12.333, 8.340) }}  & {\scriptsize{(1.052, 0.003) }}  & {\scriptsize{(1.876, 0.003) }}  & {\scriptsize{(2.391, 0.002) }}  & {\scriptsize{(106.185, 13.778)}}\tabularnewline
 \hline 
-\end{tabular}\protect\caption{Metrics comparing SFM vs FVPM. Average of $10$ runs.}
+\end{tabular}\caption{Metrics comparing SFM vs FVPM. Average of $10$ runs.}
 \end{table}
@@
 \pagebreak{}
+\begin{thebibliography}{1}
+\bibitem{key-0}Helbing, Dirk; Molnár, Péter (1995). ``Social force
+model for pedestrian dynamics''.
 
-\section{References}
-\begin{itemize}
-\item {[}1{]} ... Karamouzas ...
-\item {[}2{]} ...Helbing ...\end{itemize}
+\bibitem{key-1}Helbing, Dirk; Farkas, Illés; Vicsek, Tamás (2000).
+``Simulating dynamical features of escape panic''
+
+\bibitem{key-2}I. Karamouzas (2009). ``A Predictive Collision Avoidance
+Model for Pedestrian Simulation''\end{thebibliography}
 

### 2015-03-15 doc/informe/informe.tex
actualizo las imagenes del informe. ahora el informe ya no tiene mas formato paper. elimino arhcivos temporales.

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{graphicx}

\makeatletter

%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

\usepackage{babel}

\makeatother

\usepackage{babel}
\begin{document}

\title{Future Virtual Particle Method for Pedestrian Navigation}

\author{
  Castiglione, Gonzalo\\
  \texttt{gcastigl@gmail.com}
  \and
  Marseillan, Agustin\\
  \texttt{agustinmarseillan@gmail.com}
  \and
  Parisi, Daniel\\
  \texttt{danielparisi@xxxxx.com}
}
\date{}

\maketitle

\vspace{10cm}
\begin{center}
    \includegraphics[scale=0.08]{pics/ITBA}
    \par
\end{center}

\pagebreak{}

\begin{abstract}
Pedestrians are modeled as passive objects affected by repulsive and
attractive forces in the Social Force Model (SFM). This force governed
model leads to unnatural behaviors that don't resemble reality. This
paper presents an avoidance collision method based in pedestrian self
governed decisions, by calculating the position of every pedestrian
in the future, a given pedestrian can adjust his velocity vector to
avoid collisions instead of a repulsive force.

\textbf{keywords:} pedestrian, collision avoidance, future virtual
particle, force model.
\end{abstract}

\section{Introduction}

\subsection{Motivation and previous work}

Navigation of biological, sinthetic or virtual agents is a relevant
problem in several fields such as pedestrian dynamics, moving robots
and animation of characters for videogames and motion pictures.

Modelling and simulating the displacement of agents through arbitrarily
complex environments may be stated in an hierarchical structure of
mechanisms depending mainly on the distance from the agent. This level
has been named, from closer to further, as operational (walking, lowest
level physical-computational model for displacement), tactical (way-finding,
route choice) and strategic (general activity planning) \cite{key-hoog2004}.
These levels are not independent, factors affecting one level may
impact in the following and vice-versa, for example, the route choice
may vary due to congestion of agents produced from previous route
choice and walking behavior. Also, obstacles can impact on the operational
level or tactical level depending on the particular geometry of the
environment. The particular mechanism we want to address is the avoidance
of obstacles being fixed or moving (another agent) which involves
operational and tactical aspects of the navigation.

A general approach is to take an existing operational model and equip
it with a higher level model which allows better and smoother collision
avoidance behavior. Existing low level models can be taken from pedestrian
dynamics field and in general this models can be classified into rule
based and force based, discrete and continuous space description,
etc. \cite{key-scha2009}.

A famous example of continuous and force based model is the Social
Force Model \cite{key-helb1995,key-helb2000}. In this model the dynamic
for virtual pedestrians is derived from the Newton equation's considering
the total force exerted over each agent is the result of three forces:
Contact, Social and Driving Force. While the driving force points
towards the final objective of each pedestrian, the social force is
repulsive and acts as a kind of collision avoidance force. However
this social force term introduces several artifices in some configurations.
See for example Lakoba \cite{key-tara2005}, Parisi \cite{key-pari2009}.

Cellular automaton models make use of a spatial grid, which can be
occupied or empty, along with a set of rules determining the evolution
and conflict resolution of virtual pedestrians moving over the cells
of the grid. An emblematic cellular automaton model is the one proposed
by Kirchner and Schadschneider \cite{key-kirc2002}.

Hybrid models have also been proposed such as the Contractile Particle
Model \cite{key-pari2011} in which a continuous description of the
space is combined with a set of simple rules governing the dynamics
of the system.

The basic operational model -as the ones described above- can be improved
if higher level mechanisms were added to manage more complex issues
as efficient avoidance. Some recent examples can be found in the literature.

Karamouzas \cite{key-kara2009} proposed a method for collision avoidance
modifying the social force model, basically, replacing the social
force term by a new ``evasive\textquotedblright{} force which tends
to avoid future collisions. The magnitude and direction of this force
is calculated considering the predictions of these possible collisions.

Kretz \cite{key-kret2001} have arrised the point that the key ingredient
in social force model is the driving force instead of interaction
force, so in this work the authors propose a method for dynamically
adjusting the desired velocity following the gradient of a field given
by a time map, in other words, the desired velocity is chosen as the
quickest path to the objective taking into account the geometry and
other agents (collision, congestion, jams, etc.). Also mounted on
the SFM, Moussaad \cite{key-mous2009} presented a model using ``cognitive
heuristics'' to determine the norm and direction of the desired velocity
for each agent dynamically during the evolution of the system.

This paper proposes that the navigation capacity of virtual agents
is concentrated in the pedestrian's decision of his desired velocity,
its calculation is the key difference with the SFM.

The method proposed could be mounted on different basic displacement
models like the SFM or the CPM, in the present work we have chosen
the first one.

\subsection{Social Force Model}

The Social Force is a model presented by Helbing \cite{key-helb1995,key-helb2000}
in several publications. This paper will focus on the latest version
of the model \cite{key-helb2000}. In this model, each pedestrian
$i$ occupies a circular area of radius $r_{i}$ and is governed by
thee forces. 
\[
\vec{F_{i}}=\vec{F_{D_{i}}}+\vec{F_{S_{i}}}+\vec{F_{G_{i}}}
\]

This forces are a measure for the internal motivations of the individual
to perform certain actions.

The first term is known as the ``Driving Force''. It's calculated
as follows:

\begin{equation}
\vec{F_{D}}(i)=m_{i}\frac{v_{di}\vec{e_{i}}-\vec{v_{i}}}{\tau}\label{eq:driving-force}
\end{equation}

\begin{equation}
\vec{e_{i}}=\frac{\vec{x}_{i}^{k}-\vec{x}_{i}(t)}{||\vec{x}_{i}^{k}-\vec{x}_{i}(t)||}\label{eq:desired-direction}
\end{equation}

$\vec{F}_{D_{i}}$ represents the force that a pedestrian $i$ keeps
towards his desired velocity of motion.

$v_{di}$ is the desired speed for the pedestrian $i$.

$\vec{e}{}_{i}$ is the desired direction of motion of the pedestrian
$i$.

$\vec{v}{}_{i}$ is the current velocity of the pedestrian $i$.

$\vec{x}_{i}(t)$ is the actual position of the pedestrian $i$ at
the time $t$.

$x_{i}^{k}$ is the closest point from the goal (represented as an
area) to pedestrian $i$. \\

Figure \ref{fig:driving-force} shows a pedestrian moving with $\vec{v}$
velocity but adjusting its trajectory towards \textbf{$X$}.

\begin{figure}[h]
\begin{centering}
\includegraphics[scale=0.4]{pics/sfm/drivingforce} 
\par\end{centering}

\caption{\label{fig:driving-force}Driving force}
\end{figure}

The second term is known as the ``Social force''. It's calculated
as follows:

\begin{equation}
\vec{F}_{S_{i}}=\sum_{j=1,j\ne i}^{N_{P}}Aexp(-\frac{\epsilon_{ij}}{B})\,\vec{e}_{ij}^{n}\label{eq:social-force}
\end{equation}

$\vec{F}_{S_{i}}$ represents the fact that a pedestrian keeps a certain
distance to other pedestrians and borders.

$N_{p}$ is the number of existing pedestrians.

$A$ and $B$ are constants determined by simulations.

$\epsilon_{ij}$ is the distance from $x_{i}$ towards $x_{j}$.

$\vec{e}_{ij}^{n}$ is the unit vector from $x_{i}$ towards $x_{j}$.\\

Figure \ref{fig:Social-Force} shows \ref{eq:social-force} graphically.

\begin{figure}[h]
\begin{centering}
\includegraphics[scale=0.4]{pics/sfm/sf} 
\par\end{centering}

\caption{Social Force\label{fig:Social-Force}}
\end{figure}

The third term is known as the ``Granular force''. It's calculated
as follows:

\begin{equation}
\vec{F}_{G_{i}}=\sum_{j=1,j\ne i}^{N_{P}}[-\epsilon_{ij}k_{n}\vec{e}_{ij}^{n}+v_{ij}^{t}\epsilon_{ij}k_{t}\vec{e}_{ij}^{t}]\, g(\epsilon_{ij})\label{eq:granular-force}
\end{equation}

$\vec{F}_{G_{i}}$ represents the physical force that a pedestrian
suffers when colliding with another object (pedestrian or wall).

$k_{n}$ and $k_{t}$ are the normal and tangential friction coeficient
respectively.

$g$ is $0$ if $\epsilon_{ij}\leq0$ or $\epsilon_{ij}$ otherwise\\

Figure \ref{fig:colliding-pedestrians} shows \ref{eq:granular-force}
graphically.

\begin{figure}[h]
\begin{centering}
\includegraphics[scale=0.4]{pics/sfm/ganular} 
\par\end{centering}

\caption{Colliding pedestrians\label{fig:colliding-pedestrians}}
\end{figure}

Afterwards $\vec{F}_{i}$ is calculated on each simulation step for
each of the pedestrians and applied until all of them had reached
their goal.

Fixed parameter values:

\begin{center}
\begin{tabular}{|c|c|}
\hline 
Name  & Value\tabularnewline
\hline 
\hline 
$A$  & $2000\,[N]$\tabularnewline
\hline 
$B$  & $0.08\,[m]$\tabularnewline
\hline 
$k_{n}$  & $1.2\,10^{5}\,[\frac{N}{m}]$\tabularnewline
\hline 
$k_{t}$  & $2.4\,10^{5}\,[\frac{kg}{m/s}]$\tabularnewline
\hline 
$\tau$  & $0.5\,[s]$\tabularnewline
\hline 
\end{tabular}
\par\end{center}

\subsection{Future Virtual Particle Model}

Given that the SFM adds a fictional force on pedestrians, navigation
is unnatural and doesn't resemble reality. SFM isn't validated using
well known metrics for real-case scenarios such as the flow of pedestrians
going out a door and the fundamental diagram \cite{key-pari2009}.

In the FVPM, the social force in equation \ref{eq:driving-force}
is eliminated and replaced with a dynamic driving force towards a
short term objective, which is equal to equation \ref{eq:desired-direction}
replacing $\vec{x}_{i}^{k}$ with $\vec{x_{i'}}$, where $\vec{x_{i'}}$
is an estimation of the location of pedestrian $i$ in the near future.
$i'$ will be called Future Virtual Particle.

AGREGADO POR PARISI: LLEGAMOS A POSTULAR ESTE MODELO DESPUES DE VARIOS CICLOS DE ITERACIONES Y NUMEROSAS PRUEBAS DE DE VARIANTES HASTA CONVERGER AL MODELO PRESENTADO QUE MODELA ADECUADAMENTE VARIAS SITUACIONES

\section{The Model}

\subsection{Hipotesis}

The heuristics that govern the motion of a pedestrian are the same
as Helbin's \cite{key-helb1995,key-helb2000}:

\begin{enumerate}
    \item The pedestrian wants to reach his goal in the shortest possible path. 
    \item The pedestrian's movement is influenced by other pedestrians. Depending
    on the distance between the two of them and the predicted trajectory,
    the pedestrian needs to change his route to be able to avoid obstacles. 
    \item Movement speed will be influenced by the presence of other pedestrians
    and obstacles. 
\end{enumerate}

\subsection{Geometrical definition}

A pedestrian is defined as follows:

\begin{itemize}
    \item Circular shape

    Represents the personal space of a pedetrian. The value of the radio
    is generated randomly for each pedestrian. The range of values is
    distributed uniformly in $[0.25,0.29]$ $[cm]$ between pedestrians.

    \item Long term target

    Represented by a static area. It is considered as accomplished when
    the pedestrian touches this area. Multiple objectives could be defined
    in a list, in this case, each of them must be reached in order.

    \item Short term target

    Called future virtual particle (FVP), it represents a point at a relative
    distance from the pedestrian's center. It's a dynamic objective.

    It is defined as a $1\,[kg]$ mass. Not collisionable.

    \item Desired speed

    The speed the pedestrian would walk if he/she was alone. This represents
    the constant $v_{di}$ in ecuation \ref{eq:driving-force}. It takes
    a different value for each pedestrian. Varies with a uniform distribution
    between $[1.2,1.4]\,[m/s]$.

    \item Reaction distance ($RD$)

    Maximum distance between a pedestrian and his FVP, it represents the
    distance at which a real pedestrian would react from an obstacle.

\end{itemize}

\vspace{1cm}

\begin{figure}[h]
    \centering{}
    \includegraphics[scale=0.4]{pics/pedestrian-top} 
    \caption{\label{fig:pedestrian-geometry}Illustration of pedestrian $i$ and its FVP ($i'$).}
\end{figure}

The naming used is shown in illustration \ref{fig:pedestrian-vectors}.

\begin{figure}[h]
    \centering{}
    \includegraphics[scale=0.4]{pics/geometry}
    \caption{\label{fig:pedestrian-vectors}Vectorial definitions}
\end{figure}

\subsection{Dynamics}

\subsubsection{Force calculation}

\begin{itemize}
\item Dynamic of the FVP

Each pedestrian has to reach the long term objective at some point,
to ensure this, the FVP needs to be aligned with the shortest path
to the long term objective $\mathbf{x_{o}}$. On the other hand, there
are sometimes obstacles in the way, which will make this impossible,
in this cases, the route will have to change depending on the situation.

To model this situations, two types of forces act over the FVP: 
\begin{itemize}
\item Internal force \\

This force will guide the pedestrian on the shortest path $\mathbf{x_{o}x_{i}}$.
This force is modeled using two springs:

The first spring starts on $x_{i}$, ends on $x_{i'}$ and has a stationary
distance of $RD$ with a spring constant $K_{s}(\theta)$ where $\theta$
is the angle between $\mathbf{u}$ and $\mathbf{r}$. With this spring
the FVP will tend to always be at $RD$ distance from the pedestrian.
Because a pedestrian always tries to reach his goal in the shortest
possible path (hypothesis 1), if it has to take a big detour of his
ideal path, it will try to reduce his velocity drastically in order
to avoid making a long travel. To recreate this, the spring constant
has to be dependant of the deviation angle. 
\[
K_{s}(\theta)=\frac{K_{2}}{\theta}
\]

The second spring starts on $x_{i'}$ and ends on $x_{i}+RD\frac{\vec{x_{i}x_{o}}}{\mid\vec{x_{i}x_{o}}\mid}$
with a spring constant $K_{1}$. This spring represents the pedestrian's
desire to reach his target. A greater spring constant will force a
straighter path. In order to avoid an oscillatory movement, a damping
$\gamma$ was added to the spring.\\

For any pedestrian $i$, its internal force is

\begin{equation}
    F_{internal}(i)=F_{S1}(i)+F_{S2}(i)
\end{equation}

where

\[
    F_{S1}(i)=K_{1}\cdot(|\vec{r}|-RD)\cdot\hat{r}
\]
\[
    F_{S2}(i)=\, K_{2}(\theta_{i})\cdot(\vec{x_{i'}}-(\vec{x_{i}}+\hat{x_{i}o}\cdot RD))
\]

\begin{figure}[h]
    \centering{}\includegraphics[scale=0.35]{pics/pedestrian-internal-forces}
    \caption{Pedestrian internal forces}
\end{figure}

\item Avoidance forces \\
 This force will produce avoidance movements when obstacles are detected
on the path. The magnitude of this force is calculated using two factors:
\\
 The first factor is calculated for each of the pedestrian $j$ ($j\neq i$)
who is in the range of sight of pedestrian $i$. This restriction
is verified using the following condition:

\[
    \mathbf{r_{ii'}}\bullet\mathbf{r_{ij}}<0
\]

This condition represents the fact that pedestrians make decisions
based only on obstacles in his range of vision. The formula for the
external force that affects the FVP $i'$ is

\[
    F_{ext}(i')=FF(i')+FP(i')+FW(i')
\]
where 
\[
    FF_{(}i')=\sum_{j}(\alpha_{ff}e^{-s/\beta_{ff}})
\]
\[
    FP_{(}i')=\sum_{j}(\alpha_{fp}e^{-t/\beta_{fp}})
\]
\[
    FW_{(}i')=\sum_{w}(\alpha_{fw}e^{-dist(w,i')/\beta_{fw}})
\]

where $\alpha_{x}$ and $\beta_{x}$ are constants.

The first term of the sum acts as a repulsion force between $i'$
and $j'$, resulting in the avoidance of a future collision. The second
term uses this same principle but calculates the repulsion force between
$j'$ and $i$. The third term adds the repulsion against walls, using
the closest point between $i'$ and the wall.

Figure \ref{fig:External-forces-affecting} shows the external forces
that a pedestrian $i$ suffers because of another pedestrian ($j$)
and also the direction in which $i$ desires to move.

\begin{figure}[h]
    \centering{}
    \includegraphics[scale=0.4]{pics/pedestrian-top-forces}
    \caption{\label{fig:External-forces-affecting}External forces affecting future$i'$}
\end{figure}

\end{itemize}

After this, the final $F_{i'}$ is computed by adding all the terms.
$F_{i'}=F_{ext}(i)+F_{i\, s1}+F_{i\, s2}$.\\

To avoid high symetry situations, a low noise $P=10\%$ is added to
$F$. There are two ways to apply this noise: 
\begin{itemize}

\item Radial noise:

\begin{itemize}
\item A value $p$ is taken randomly from a uniform distribution $[-P,\, P]$
and calculate: $FL_{i'}=F_{i'}*p$ 
\item Angular noise:

    \begin{itemize}
        \item A value $sgn=\{-1,\,1\}$ is taken randomly from a uniform distribution
        and a value $p$ from $[-P,\, P]$. Then \\
        \[
            M=\left(\begin{array}{cc}
            \cos(\pi*sgn) & -\sin(\pi*sgn)\\
            \sin(\pi*sgn) & \cos(\pi*sgn)
            \end{array}\right)
        \]
        \[
            FA_{i'}=F_{i'}*p*M
        \]
    \end{itemize}
\end{itemize}

At last, we find $F'_{i'}=F_{i'}+FL_{i'}+FA_{i'}$ and apply movement
equations.
\end{itemize}
\item Dynamic of the pedestrian

The pedestrian always wants to move in the direction his FVP is pointing
and its magnitude is defined as $F_{d}$ or driving force:

\[
    \vec{F}_{desire_{i}}=m_{i}\frac{\frac{|\vec{ii'}|}{|\vec{r}_{max}|}\vec{e_{i}}-\vec{v}_{i}}{\tau}
\]

Where $\tau=0.5$

\textit{{*}It is important to note that the only deviation from the
SFM in this equation is the $k\vec{e}_{i}$ term. As described above,
this model focuses on improving the SFM through dynamically adjusting
the desired velocity.}

\end{itemize}

\subsubsection{Algorithm}

The pedestrian movement is calculated in four steps: 
\begin{enumerate}
    \item Calculate forces for each FVP. 
    \item Update positions for each FVP. 
    \item Calculate forces for each pedestrian. 
    \item Update positions for each pedestrian. 
\end{enumerate}

\section{Calibration}

\subsection{Metrics}

The results where compared to the SFM model \cite{key-helb2000}.
The test scenarios where crossing and hallway for they present the
main types of symmetry (90 degrees and 180 degrees respectively). \\

Hallway scenario: A $15[m]$ by $4[m]$ hallway. Pedestrians are generated
from each end at a pace of 1 pedestrian per second with the other
end as target. \\
 This scenario is shown in figure \ref{fig:hallway-scenario}.

\begin{figure}[h]
    \centering{}
    \includegraphics[scale=0.35]{pics/scenarios/hallway}
    \caption{\label{fig:hallway-scenario}Hallway Scenario}
\end{figure}

Crossing scenario: Two hallways of $25[m]$ lenght by $5[m]$ width
put toghether in the center forming a cross. Pedestrians are generated
from the top, targeting the bottom, and from the right end, targeting
the left end, at a pace of 1 pedestrian per second. \\
 This scenario is shown in figure \ref{fig:cross-scenario}.

\begin{figure}[h]
    \centering{}
    \includegraphics[scale=0.3]{pics/scenarios/cross}
    \caption{\label{fig:cross-scenario}Cross Scenario}
\end{figure}

The metrics used to validate and verify the model against the defined
two previous scenarios are defined as follows:
\begin{enumerate}
\item Number of collisions: The equation for this metric is defined as:
\\

\begin{eqnarray*}
    \sum\#\{(i,j)\,/\, id_{i}<id_{j}\wedge\\
    x_{i,t_{n}}-x_{j,t_{n}}<R_{i}+R_{j}\wedge\\
    x_{i,t_{n-1}}-x_{j,t_{n-1}}>R_{i}+R_{j}\}\,\,\forall t_{n}
\end{eqnarray*}

\item Amount of collitions per instant: The equation for this metric is
defined as: \\

\begin{eqnarray*}
    \sum\#\{(i,j)\,/\, id_{i}<id_{j}\wedge\\
    x_{i,t_{n}}-x_{j,t_{n}}<R_{i}+R_{j}\}\,\,\forall t_{n}
\end{eqnarray*}

\item Average walking speed: The equation for this metric is defined as:
\\

\begin{eqnarray*}
    \sum v_{i,t_{n}}/\#\{i_{t_{n}}\}\,\,\forall t_{n}
\end{eqnarray*}

\item Average travel time: The average time that a pedestrian needed until
it reached the goal. The equation for this metric is defined as: \\

\begin{eqnarray*}
\sum\#\{i_{t_{n}}\}*\triangle t\,\,\forall t_{n}/\#\{i\}
\end{eqnarray*}

\item Average travel distance: The average distance that a pedestrian traveled
until it reached the goal. The equation for this metric is defined
as: \\

\begin{eqnarray*}
\sum\#\{v_{i,t_{n}}\}*\triangle t\,\,\forall t_{n}/\#\{i\}
\end{eqnarray*}

\item Average turn angle: The average angle turned by a pedestrian until
it reached the goal.\\

\begin{eqnarray*}
    \sum\arccos(v_{t_{n}}\bullet v_{t_{n-1}}/|v_{t_{n}}\bullet v_{t_{n-1}}|)\,\,\forall t_{n}/\#\{i\}
\end{eqnarray*}

\end{enumerate}
Escape room: A $20x20[m]$ room with a single $1.2[m]$ exit door
centered at the bottom. At the beginning, $100$ pedestrians are distributed
across the room and target the exit. When the first pedestrians exits
the room, a counter starts, and when the last one croses, it stops.
This way we can measure the flow of pedestrians leaving a room, which
is known to be between $0.69$ and $1$ for pedestrians without emergencies
\cite{key-pedEvDyn2012}. \\
 This scenario is shown in figure \ref{fig:room}.

\begin{figure}[h]
    \centering{}
    \includegraphics[scale=0.3]{pics/scenarios/room}
    \caption{\label{fig:room}Room Scenario}
\end{figure}

The metrics used where: 
\begin{enumerate}
    \item Escape flow: 
    \begin{eqnarray*}
    \sum\arccos(v_{t_{n}}\bullet v_{t_{n-1}}/|v_{t_{n}}\bullet v_{t_{n-1}}|)\,\,\forall t_{n}/\#\{i\}
\end{eqnarray*}

\end{enumerate}

\subsection{Values}

To calibrate the model, runs varying parameters were made. A wide
spectrum of values was covered, testing every combination of every
possible one. After seeing clear preferences towards certain values,
the values were refined within that scope. After numerous iterations
of this process, the values that best suit these metrics are:

\begin{itemize}
    \item Pedestrian

    \begin{itemize}
        \item $K_{1}=100$ {[}N/m{]}, 
        \item $\gamma=10$ 
        \item $K_{2}=150$ {[}N/m{]} 
    \end{itemize}
    \item FVP-FVP interaction

    \begin{itemize}
        \item $\alpha=1000$ 
        \item $\beta=[0.4,\,0.5]$ (Uniform distribution) 
        \end{itemize}
    \item Pedestrian-FVP interaction

    \begin{itemize}
        \item $\alpha=1000$ 
        \item $\beta=0.1$ 
    \end{itemize}
    \item FVP-Wall interaction

    \begin{itemize}
        \item $\alpha=10000$ 
        \item $\beta=0.1$ 
    \end{itemize}
\end{itemize}

\section{Results}

Metric results for crossing scenario:

\begin{tabular}{|c|c|c|}
    \hline 
    Metric  & {\scriptsize{FVPM}} & {\scriptsize{SFM ($\alpha=2000,\,\beta=0.08$)}}\tabularnewline
    \hline 
    \hline 
    $1$  & {\scriptsize{$1.800\pm20.748$}} & {\scriptsize{$5.333\pm2.625$}}\tabularnewline
    \hline 
    $2$  & {\scriptsize{$34.600\pm8.333$}} & {\scriptsize{$12.333\pm8.340$}}\tabularnewline
    \hline 
    $3$  & {\scriptsize{$1.024\pm0.016$ $[m/s]$}} & {\scriptsize{$1.052\pm0.003$ $[m/s]$}}\tabularnewline
    \hline 
    $4$  & {\scriptsize{$1.910\pm0.022$ $[s]$}} & {\scriptsize{$1.876\pm0.003$ $[s]$}}\tabularnewline
    \hline 
    $5$  & {\scriptsize{$2.392\pm0.005$ $[m]$}} & {\scriptsize{$2.391\pm0.002$ $[m]$}}\tabularnewline
    \hline 
    $6$  & {\scriptsize{$91.062\pm12.122$ $[rad]$}} & {\scriptsize{$106.185\pm13.778$ $[rad]$}}\tabularnewline
    \hline 
\end{tabular}

\vspace{1cm}

\begin{figure}[h]
    \begin{centering}
    \includegraphics[width=6cm]{pics/program/crossing-no-future} 
    \par\end{centering}
    \caption{\label{fig:crossing-no-future}Crossing visualization}
\end{figure}

\begin{figure}[h]
    \centering{} \includegraphics[width=6cm]{pics/program/crossing-future}
    \caption{\label{fig:crossing-future}Crossing visualization with visible future}
\end{figure}

Metric results for hallway scenario:

\begin{tabular}{|c|c|c|}
    \hline 
    Metric  & {\scriptsize{FVPM}} & {\scriptsize{SFM ($\alpha=2000,\,\beta=0.08$)}}\tabularnewline
    \hline 
    \hline 
    $1$  & {\scriptsize{$24.400\pm2.653$}} & {\scriptsize{$52.400\pm4.543$}}\tabularnewline
    \hline 
    $2$  & {\scriptsize{$190.800\pm28.701$}} & {\scriptsize{$252.800\pm28.764$}}\tabularnewline
    \hline 
    $3$  & {\scriptsize{$1.237\pm0.014$ $[m/s]$}} & {\scriptsize{$1.235\pm0.002$ $[m/s]$}}\tabularnewline
    \hline 
    $4$  & {\scriptsize{$0.919\pm0.009$ $[s]$}} & {\scriptsize{$0.920\pm0.003$ $[s]$}}\tabularnewline
    \hline 
    $5$  & {\scriptsize{$20.922\pm0.132$ $[m]$}} & {\scriptsize{$22.823\pm0.077$ $[m]$}}\tabularnewline
    \hline 
    $6$  & {\scriptsize{$142.495\pm11.511$ $[rad]$}} & {\scriptsize{$160.950\pm7.749$ $[rad]$}}\tabularnewline
    \hline 
\end{tabular}

\vspace{1cm}

\begin{figure}[h]
    \begin{centering}
    \includegraphics[width=6.5cm]{pics/program/hallway-no-future} 
    \par\end{centering}

    \caption{\label{fig:hallway-no-future}Hallway visualization}
\end{figure}

\begin{figure}[h]
    \begin{centering}
    \includegraphics[width=6.5cm]{pics/program/hallway-future} 
    \par\end{centering}

    \caption{\label{fig:hallway-future}Hallway visualization with visible future}
\end{figure}

The number of collisions is decresead compared to the SFM. The fact
that the time of collision (metric \#2) is bigger than in the SFM,
resembles reality, pedestrians don't shoot out at great velocities
when colliding. The average travel distance is similar in the crossing
scenario but much smaller in the hallway, this shows the problem of
SFM in high simmetry scenarios (inverse velocities). \\
 Each pedestrian turns (in average) $10\%$ less with the FVPM than
with the SFM in both scenarios. \\

\begin{figure}[h]
    \begin{centering}
    \includegraphics[width=8.5cm]{pics/steps/room} 
    \par\end{centering}

    \caption{\label{fig:room-flow}Pedestrian exit flow in room scenario}
\end{figure}

In the case of the escape room, figure \ref{fig:room-flow} shows
that the first pedestrian leaves the room at the $5$ seconds mark,
while the last one does it at the $90$ seconds mark, so the flow
is: 
\[
    flow=\frac{100}{1.2*(90-5)}=\frac{100}{102}=0.98\,\,[ped/sec]
\]

\begin{figure}[h]
    \begin{centering}
    \includegraphics[width=6.5cm]{pics/program/room-no-future} 
    \par\end{centering}

    \caption{\label{fig:room-no-future} Room visualization}
\end{figure}

\begin{figure}[h]
    \centering{} \includegraphics[width=6.5cm]{pics/program/room-future}
    \caption{\label{fig:room-future} Room visualization with visible future}
\end{figure}

\section{Conclusion}

Pedestrians can adjust their desired velocity at will, based on the
data they perceive. We proposed a model that calculates the desired
velocity of the social force model by conceptually moving the social
force into the near future (FVP). The results look more natural than
the original SFM and have been validated with experimental data. We
used real-life metrics to validate our model, the results show that
our model resembles reality with high fidelity. The proposed model
produces a more natural navigation, but, at high densities, this isn't
true, we still need further analysis of this scenario to adjust our
model for both cases. In future work, the paths our virtual pedestrians
make need to be compared and validated with real-life pedestrians
paths to complement the use of metrics for the mean of pedestrians.
Parameters should be revalidated with more metrics and analyzed in
more detail.

\newpage{}
\begin{thebibliography}{10}

\bibitem{key-hoog2004} Hoogonen and Bovy (2004).

\bibitem{key-scha2009} A. Schadschneider (2009). \textquotedbl{}Evacuation
Dynamics: Empirical Results, Modeling and Applications\textquotedbl{}.

\bibitem{key-scha2002} A. Schadschneider (2009). \textquotedbl{}Traffic
flow: A statistical physics point of view\textquotedbl{}.

\bibitem{key-helb1995} Helbing, Dirk; Molnr, Pter (1995). ``Social
force model for pedestrian dynamics``.

\bibitem{key-helb2000} Helbing, Dirk; Farkas, Ills; Vicsek, Tams
(2000). ``Simulating dynamical features of escape panic``.

\bibitem{key-tara2005} Taras I. Lakoba (2005). \textquotedbl{}Modifications
of the Helbing-Molnar-Farkas-Vicsek Social Force Model for Pedestrian
Evolution\textquotedbl{}.

\bibitem{key-pari2009} Parisi (2009). \textquotedbl{}A modification
of the Social Force Model can reproduce experimental data of pedestrian
flows in normal conditions\textquotedbl{}.

\bibitem{key-kirc2002} Kirchner and Schadschneider (2002). \textquotedbl{}Simulation
ofevacuation processes using a bionics-inspired cellular automaton
model for pedestrian dynamics\textquotedbl{}.

\bibitem{key-pari2011} Baglietto and Parisi, (2011). \textquotedbl{}Continuous-space
automaton model for pedestrian dynamics\textquotedbl{}.

\bibitem{key-kara2009} I. Karamouzas (2009). \textquotedbl{}A Predictive
Collision Avoidance Model for Pedestrian Simulation\textquotedbl{}.

\bibitem{key-kret2001} Kretz (2011). \textquotedbl{}Quickest Paths
in Simulations of Pedestrians\textquotedbl{}.

\bibitem{key-mous2009} Moussad M, Helbing D, Garnier S, Johansson
A, Combe M and aulaz G (2009).

\bibitem{key-pedEvDyn2012} Ulrich Weidmann, Uwe Kirsch, Michael Schreckenberg
(2012). Pedestrian and Evacuation Dynamics 2012.\end{thebibliography}

\end{document}

### 2015-03-15 doc/informe/paper/main.tex
actualizo las imagenes del informe. ahora el informe ya no tiene mas formato paper. elimino arhcivos temporales.

--- 2015-03-15 doc/informe/informe.tex
@@
-\documentclass[english]{article}
-\usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
+% Note that the a4paper option is mainly intended so that authors in
+% countries using A4 can easily print to A4 and see how their papers will
+% look in print - the typesetting of the document will not typically be
+% affected with changes in paper size (but the bottom and side margins will).
+% Use the testflow package mentioned above to verify correct handling of
+% both paper sizes by the user's LaTeX system.
+%
+% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
+% should be used if it is desired that the figures are to be displayed in
+% draft mode.
+% conference
+\documentclass[draftclsnofoot]{IEEEtran}
 \usepackage{graphicx}
+% Add the compsoc option for Computer Society conferences.
 
-\makeatletter
+% Sin esto los captions no aparecen centrados, no se porque!!!
+\usepackage{caption}
 
-%% Because html converters don't know tabularnewline
-\providecommand{\tabularnewline}{\\}
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[conference]{../sty/IEEEtran}
 
-\usepackage{babel}
+% *** CITATION PACKAGES ***
+%
+%\usepackage{cite}
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
+% not currently provide for hyperlinked citations.
+% The latest version can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
+% The documentation is contained in the cite.sty file itself.
 
-\makeatother
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+  % \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  % \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
 
-\usepackage{babel}
+% *** MATH PACKAGES ***
+%
+%\usepackage[cmex10]{amsmath}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics. If using
+% it, be sure to load this package with the cmex10 option to ensure that
+% only type 1 fonts will utilized at all point sizes. Without this option,
+% it is possible that some math symbols, particularly those within
+% footnotes, will be rendered in bitmap form which will result in a
+% document that can not be IEEE Xplore compliant!
+%
+% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+%\usepackage{algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
+% There is also a support site at:
+% http://algorithms.berlios.de/index.html
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
+
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/required/tools/
+
+%\usepackage{mdwmath}
+%\usepackage{mdwtab}
+% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
+% especially mdwmath.sty and mdwtab.sty which are used to format equations
+% and tables, respectively. The MDWtools set is already installed on most
+% LaTeX systems. The lastest version and documentation is available at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+%\usepackage{eqparbox}
+% Also of notable interest is Scott Pakin's eqparbox package for creating
+% (automatically sized) equal width boxes - aka "natural width parboxes".
+% Available at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
+
+% *** SUBFIGURE PACKAGES ***
+%\usepackage[tight,footnotesize]{subfigure}
+% subfigure.sty was written by Steven Douglas Cochran. This package makes it
+% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
+% work, it is a good idea to load it with the tight package option to reduce
+% the amount of white space around the subfigures. subfigure.sty is already
+% installed on most LaTeX systems. The latest version and documentation can
+% be obtained at:
+% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
+% subfigure.sty has been superceeded by subfig.sty.
+
+%\usepackage[caption=false]{caption}
+%\usepackage[font=footnotesize]{subfig}
+% subfig.sty, also written by Steven Douglas Cochran, is the modern
+% replacement for subfigure.sty. However, subfig.sty requires and
+% automatically loads Axel Sommerfeldt's caption.sty which will override
+% IEEEtran.cls handling of captions and this will result in nonIEEE style
+% figure/table captions. To prevent this problem, be sure and preload
+% caption.sty with its "caption=false" package option. This is will preserve
+% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
+% (recommended due to many improvements over 1.2) of subfig.sty supports
+% the caption=false option directly:
+%\usepackage[caption=false,font=footnotesize]{subfig}
+%
+% The latest version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
+% The latest version and documentation of caption.sty can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure. The latest version and documentation can be found at:
+% http://www.ctan.org/tex-archive/macros/latex/base/
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
+% Documentation is contained in the stfloats.sty comments as well as in the
+% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
+% does not allow \baselineskip to stretch. Authors submitting work to the
+% IEEE should note that IEEE rarely uses double column equations and
+% that authors should try to avoid such use. Do not be tempted to use the
+% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
+% not format its papers in such ways.
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+%\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
+% Read the url.sty source comments for usage information. Basically,
+% \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
+
 \begin{document}
@@
 \author{
-  Castiglione, Gonzalo\\
-  \texttt{gcastigl@gmail.com}
+    \IEEEauthorblockN{Castiglione Gonzalo,}
+    \IEEEauthorblockA{Instituto Tecnológico de Buenos Aires\\
+    }
     \and
-  Marseillan, Agustin\\
-  \texttt{agustinmarseillan@gmail.com}
+    \IEEEauthorblockN{Marseillan Agustin,}
+    \IEEEauthorblockA{Instituto Tecnológico de Buenos Aires\\
+    }
     \and
-  Parisi, Daniel\\
-  \texttt{danielparisi@xxxxx.com}
+    \IEEEauthorblockN{Parisi Daniel,}
+    \IEEEauthorblockA{Instituto Tecnológico de Buenos Aires\\
     }
-\date{}
+}
 
+% make the title area
 \maketitle
 
-\vspace{10cm}
-\begin{center}
-    \includegraphics[scale=0.08]{pics/ITBA}
-    \par
-\end{center}
+\begin{abstract}
+%\boldmath
+Pedestrians are modeled as passive objects affected by repulsive and attractive forces in the Social Force Model (SFM).
+This force governed model leads to unnatural behaviors that don't resemble reality.
+This paper presents an avoidance collision method based in pedestrian self governed decisions, by calculating the position of every pedestrian in the future, a given pedestrian can adjust his velocity vector to avoid collisions instead of a repulsive force.
+\end{abstract}
+% IEEEtran.cls defaults to using nonbold math in the Abstract.
+% This preserves the distinction between vectors and scalars. However,
+% if the journal you are submitting to favors bold math in the abstract,
+% then you can use LaTeX's standard command \boldmath at the very start
+% of the abstract to achieve this. Many IEEE journals frown on math
+% in the abstract anyway.
 
-\pagebreak{}
+% Note that keywords are not normally used for peerreview papers.
+\begin{IEEEkeywords}
+pedestrian, collision avoidance, future virtual particle, force model
+\end{IEEEkeywords}
 
-\begin{abstract}
-Pedestrians are modeled as passive objects affected by repulsive and
-attractive forces in the Social Force Model (SFM). This force governed
-model leads to unnatural behaviors that don't resemble reality. This
-paper presents an avoidance collision method based in pedestrian self
-governed decisions, by calculating the position of every pedestrian
-in the future, a given pedestrian can adjust his velocity vector to
-avoid collisions instead of a repulsive force.
-
-\textbf{keywords:} pedestrian, collision avoidance, future virtual
-particle, force model.
-\end{abstract}
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
 
 \section{Introduction}
-
 \subsection{Motivation and previous work}
@@
 route choice) and strategic (general activity planning) \cite{key-hoog2004}. 
-These levels are not independent, factors affecting one level may
-impact in the following and vice-versa, for example, the route choice
-may vary due to congestion of agents produced from previous route
-choice and walking behavior. Also, obstacles can impact on the operational
-level or tactical level depending on the particular geometry of the
-environment. The particular mechanism we want to address is the avoidance
-of obstacles being fixed or moving (another agent) which involves
-operational and tactical aspects of the navigation.
+These levels are not independent, factors affecting
+one level may impact in the following and vice-versa, for example,
+the route choice may vary due to congestion of agents produced from
+previous route choice and walking behavior. Also, obstacles can impact
+on the operational level or tactical level depending on the particular
+geometry of the environment. The particular mechanism we want to address
+is the avoidance of obstacles being fixed or moving (another agent)
+which involves operational and tactical aspects of the navigation.
 
@@
 A famous example of continuous and force based model is the Social
-Force Model \cite{key-helb1995,key-helb2000}. In this model the dynamic
-for virtual pedestrians is derived from the Newton equation's considering
+Force Model \cite{key-helb1995, key-helb2000}. In this model the dynamic for
+virtual pedestrians is derived from the Newton equation's considering
 the total force exerted over each agent is the result of three forces:
@@
 Hybrid models have also been proposed such as the Contractile Particle
-Model \cite{key-pari2011} in which a continuous description of the
-space is combined with a set of simple rules governing the dynamics
-of the system.
+Model \cite{key-pari2011} in which a continuous description
+of the space is combined with a set of simple rules governing the
+dynamics of the system.
 
@@
 
-Kretz \cite{key-kret2001} have arrised the point that the key ingredient
-in social force model is the driving force instead of interaction
-force, so in this work the authors propose a method for dynamically
-adjusting the desired velocity following the gradient of a field given
-by a time map, in other words, the desired velocity is chosen as the
-quickest path to the objective taking into account the geometry and
-other agents (collision, congestion, jams, etc.). Also mounted on
-the SFM, Moussaad \cite{key-mous2009} presented a model using ``cognitive
-heuristics'' to determine the norm and direction of the desired velocity
-for each agent dynamically during the evolution of the system.
+Kretz \cite{key-kret2001} have arrised the point that the key ingredient in
+social force model is the driving force instead of interaction force,
+so in this work the authors propose a method for dynamically adjusting
+the desired velocity following the gradient of a field given by a
+time map, in other words, the desired velocity is chosen as the quickest
+path to the objective taking into account the geometry and other agents
+(collision, congestion, jams, etc.). Also mounted on the SFM, Moussaad
+\cite{key-mous2009} presented a model using ``cognitive heuristics''
+to determine the norm and direction of the desired velocity for each
+agent dynamically during the evolution of the system.
 
-This paper proposes that the navigation capacity of virtual agents
-is concentrated in the pedestrian's decision of his desired velocity,
-its calculation is the key difference with the SFM.
+This paper proposes that the navigation capacity of
+virtual agents is concentrated in the pedestrian's decision of his
+desired velocity, its calculation is the key difference with the SFM.
 
@@
 in several publications. This paper will focus on the latest version
-of the model \cite{key-helb2000}. In this model, each pedestrian
-$i$ occupies a circular area of radius $r_{i}$ and is governed by
-thee forces. 
+of the model \cite{key-helb2000}. In this model, each pedestrian $i$ occupies
+a circular area of radius $r_{i}$ and is governed by thee forces.
 \[
@@
 
-Figure \ref{fig:driving-force} shows a pedestrian moving with $\vec{v}$
-velocity but adjusting its trajectory towards \textbf{$X$}.
+Figure \ref{fig:driving-force} shows a pedestrian moving with $\vec{v}$ velocity but adjusting its trajectory towards
+\textbf{$X$}.
 
@@
     \includegraphics[scale=0.4]{pics/sfm/drivingforce} 
-\par\end{centering}
-
+    \par
+    \end{centering}
     \caption{\label{fig:driving-force}Driving force}
@@
     \includegraphics[scale=0.4]{pics/sfm/sf} 
-\par\end{centering}
-
+    \par
+    \end{centering}
     \caption{Social Force\label{fig:Social-Force}}
@@
 
-$g$ is $0$ if $\epsilon_{ij}\leq0$ or $\epsilon_{ij}$ otherwise\\
+$g$ is $0$ if $\epsilon_{ij} \leq 0$  or $\epsilon_{ij}$ otherwise\\
 
@@
     \par\end{centering}
-
     \caption{Colliding pedestrians\label{fig:colliding-pedestrians}}
@@
     \end{tabular}
-\par\end{center}
+    \par
+\end{center}
 
@@
 
-Given that the SFM adds a fictional force on pedestrians, navigation
-is unnatural and doesn't resemble reality. SFM isn't validated using
-well known metrics for real-case scenarios such as the flow of pedestrians
-going out a door and the fundamental diagram \cite{key-pari2009}.
+Given that the SFM adds a fictional force on pedestrians, navigation is unnatural and doesn't resemble reality.
+SFM isn't validated using well known metrics for real-case scenarios
+such as the flow of pedestrians going out a door and the fundamental diagram {Parisi et al. 2009}.
 
-In the FVPM, the social force in equation \ref{eq:driving-force}
-is eliminated and replaced with a dynamic driving force towards a
-short term objective, which is equal to equation \ref{eq:desired-direction}
-replacing $\vec{x}_{i}^{k}$ with $\vec{x_{i'}}$, where $\vec{x_{i'}}$
-is an estimation of the location of pedestrian $i$ in the near future.
-$i'$ will be called Future Virtual Particle.
-
-AGREGADO POR PARISI: LLEGAMOS A POSTULAR ESTE MODELO DESPUES DE VARIOS CICLOS DE ITERACIONES Y NUMEROSAS PRUEBAS DE DE VARIANTES HASTA CONVERGER AL MODELO PRESENTADO QUE MODELA ADECUADAMENTE VARIAS SITUACIONES
+In the FVPM, the social force in equation \ref{eq:driving-force} is eliminated and replaced with a dynamic driving force towards a short term objective, which is equal to \ref{eq:desired-direction} replacing $\vec{x}_{i}^{k}$ with $\vec{x_{i'}}$, where $\vec{x_{i'}}$ is an estimation of the location
+of pedestrian $i$ in the near future. $i'$ will bbe called Future Virtual Particle.
 
@@
     on the distance between the two of them and the predicted trajectory,
-    the pedestrian needs to change his route to be able to avoid obstacles. 
+    the pedestrian needs to change his route to be able to avoid
+    obstacles.
     \item Movement speed will be influenced by the presence of other pedestrians
@@
 A pedestrian is defined as follows: 
+\begin{itemize}
 
-\begin{itemize}
     \item Circular shape
@@
 
-    The speed the pedestrian would walk if he/she was alone. This represents
-    the constant $v_{di}$ in ecuation \ref{eq:driving-force}. It takes
-    a different value for each pedestrian. Varies with a uniform distribution
-    between $[1.2,1.4]\,[m/s]$.
+    The speed the pedestrian would walk if he/she was alone. This
+    represents the constant $v_{di}$ in ecuation \ref{eq:driving-force}.
+    It takes a different value for each pedestrian. Varies with a uniform
+    distribution between $[1.2,1.4]\,[m/s]$.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[!ht]
     \centering{}
@@
 \subsubsection{Force calculation}
-
 \begin{itemize}
@@
 to ensure this, the FVP needs to be aligned with the shortest path
-to the long term objective $\mathbf{x_{o}}$. On the other hand, there
+to the long term objective $\mathbf{x_o}$. On the other hand, there
 are sometimes obstacles in the way, which will make this impossible,
@@
 \begin{itemize}
+
     \item Internal force \\
@@
 
-The second spring starts on $x_{i'}$ and ends on $x_{i}+RD\frac{\vec{x_{i}x_{o}}}{\mid\vec{x_{i}x_{o}}\mid}$
-with a spring constant $K_{1}$. This spring represents the pedestrian's
-desire to reach his target. A greater spring constant will force a
-straighter path. In order to avoid an oscillatory movement, a damping
-$\gamma$ was added to the spring.\\
+    The second spring starts on $x_{i'}$ and ends on 
+    $x_i + RD \frac{\vec{x_{i}x_{o}}}{\mid \vec{x_{i}x_{o}} \mid}$
+    with a spring constant $K_{1}$.
+    This spring represents the pedestrian's desire to reach his
+    target. A greater spring constant will force a straighter path.
+    In order to avoid an oscillatory movement,
+    a damping $\gamma$ was added to the spring.\\
 
@@
     \begin{equation}
-    F_{internal}(i)=F_{S1}(i)+F_{S2}(i)
+        F_{internal}(i)= F_{S1}(i) + F_{S2}(i)
     \end{equation}
@@
     \[
-    F_{S1}(i)=K_{1}\cdot(|\vec{r}|-RD)\cdot\hat{r}
+        F_{S1}(i) = K_{1} \cdot (|\vec{r}|-RD) \cdot \hat{r}
     \]
     \[
-    F_{S2}(i)=\, K_{2}(\theta_{i})\cdot(\vec{x_{i'}}-(\vec{x_{i}}+\hat{x_{i}o}\cdot RD))
+        F_{S2}(i) = \,K_{2}(\theta_{i}) \cdot (\vec{x_{i'}}-(\vec{x_{i}}+\hat{x_{i}o}\cdot RD))
     \]
@@
     \begin{figure}[h]
-    \centering{}\includegraphics[scale=0.35]{pics/pedestrian-internal-forces}
+        \centering{}
+        \includegraphics[scale=0.35]{pics/pedestrian-internal-forces}
         \caption{Pedestrian internal forces}
@@
     \item Avoidance forces \\
+    \\
     This force will produce avoidance movements when obstacles are detected
@@
     \[
-    \mathbf{r_{ii'}}\bullet\mathbf{r_{ij}}<0
+        \mathbf{r_{ii'}}\bullet\mathbf{r_{ij}} < 0
     \]
@@
     \[
-    F_{ext}(i')=FF(i')+FP(i')+FW(i')
+        F_{ext}(i') = FF(i') + FP(i') + FW(i')
     \]
@@
     \[
-    FF_{(}i')=\sum_{j}(\alpha_{ff}e^{-s/\beta_{ff}})
+        FF_(i') = \sum_{j}(\alpha_{ff}e^{-s/\beta_{ff}})
     \]
     \[
-    FP_{(}i')=\sum_{j}(\alpha_{fp}e^{-t/\beta_{fp}})
+        FP_(i') = \sum_{j}(\alpha_{fp}e^{-t/\beta_{fp}})
     \]
     \[
-    FW_{(}i')=\sum_{w}(\alpha_{fw}e^{-dist(w,i')/\beta_{fw}})
+        FW_(i') = \sum_{w}(\alpha_{fw}e^{-dist(w,i')/\beta_{fw}})
     \]
@@
 
-The first term of the sum acts as a repulsion force between $i'$
-and $j'$, resulting in the avoidance of a future collision. The second
+    The first term of the sum acts as a repulsion force between $i'$ and
+    $j'$, resulting in the avoidance of a future collision. The second
     term uses this same principle but calculates the repulsion force between
-$j'$ and $i$. The third term adds the repulsion against walls, using
-the closest point between $i'$ and the wall.
+    $j'$ and $i$. The third term adds the repulsion against walls, using the
+    closest point between $i'$ and the wall.
+
+    \iffalse The first term of the sum represents the fact that $i$
+    does not want to be in the same location as $j$ in the near future.
+    Note that $j'$ represents the predicted location of $j$ inferred
+    by another pedestrian (in this case, $i$) and because of this, it
+    moves it's near future away of that predicted location. The second
+    term, represents the same fact but taking in mind the current location
+    of the pedestrian $j$. The same law applies to each of the walls
+    on the simulation, the difference is that the closest point on the
+    wall and and the future has to be calculated before applying the formula.
+    Also, the constants $\alpha_{fw}$ and $\beta_{fw}$ have different
+    values. \fi
 
@@
 
-\begin{figure}[h]
+    \begin{figure}[!ht]
         \centering{}
         \includegraphics[scale=0.4]{pics/pedestrian-top-forces}
-    \caption{\label{fig:External-forces-affecting}External forces affecting future$i'$}
+        \caption{\label{fig:External-forces-affecting}External forces affecting future $i'$}
     \end{figure}
@@
 \begin{itemize}
-
 \item Radial noise:
@@
 \item A value $sgn=\{-1,\,1\}$ is taken randomly from a uniform distribution
-        and a value $p$ from $[-P,\, P]$. Then \\
-        \[
-            M=\left(\begin{array}{cc}
-            \cos(\pi*sgn) & -\sin(\pi*sgn)\\
-            \sin(\pi*sgn) & \cos(\pi*sgn)
-            \end{array}\right)
-        \]
-        \[
-            FA_{i'}=F_{i'}*p*M
-        \]
+and a value $p$ from $[-P,\, P]$. Then $FA_{i'}=rotation(F_{i'},\,\pi*sgn)*p$
+is calculated. 
 \end{itemize}
@@
 equations.
+
 \end{itemize}
@@
 
-The results where compared to the SFM model \cite{key-helb2000}.
-The test scenarios where crossing and hallway for they present the
-main types of symmetry (90 degrees and 180 degrees respectively). \\
-
-Hallway scenario: A $15[m]$ by $4[m]$ hallway. Pedestrians are generated
-from each end at a pace of 1 pedestrian per second with the other
-end as target. \\
- This scenario is shown in figure \ref{fig:hallway-scenario}.
-
-\begin{figure}[h]
-    \centering{}
-    \includegraphics[scale=0.35]{pics/scenarios/hallway}
-    \caption{\label{fig:hallway-scenario}Hallway Scenario}
-\end{figure}
-
-Crossing scenario: Two hallways of $25[m]$ lenght by $5[m]$ width
-put toghether in the center forming a cross. Pedestrians are generated
-from the top, targeting the bottom, and from the right end, targeting
-the left end, at a pace of 1 pedestrian per second. \\
- This scenario is shown in figure \ref{fig:cross-scenario}.
-
-\begin{figure}[h]
-    \centering{}
-    \includegraphics[scale=0.3]{pics/scenarios/cross}
-    \caption{\label{fig:cross-scenario}Cross Scenario}
-\end{figure}
-
-The metrics used to validate and verify the model against the defined
-two previous scenarios are defined as follows:
-\begin{enumerate}
-\item Number of collisions: The equation for this metric is defined as:
-\\
-
-\begin{eqnarray*}
-    \sum\#\{(i,j)\,/\, id_{i}<id_{j}\wedge\\
-    x_{i,t_{n}}-x_{j,t_{n}}<R_{i}+R_{j}\wedge\\
-    x_{i,t_{n-1}}-x_{j,t_{n-1}}>R_{i}+R_{j}\}\,\,\forall t_{n}
-\end{eqnarray*}
-
-\item Amount of collitions per instant: The equation for this metric is
-defined as: \\
-
-\begin{eqnarray*}
-    \sum\#\{(i,j)\,/\, id_{i}<id_{j}\wedge\\
-    x_{i,t_{n}}-x_{j,t_{n}}<R_{i}+R_{j}\}\,\,\forall t_{n}
-\end{eqnarray*}
-
-\item Average walking speed: The equation for this metric is defined as:
-\\
-
-\begin{eqnarray*}
-    \sum v_{i,t_{n}}/\#\{i_{t_{n}}\}\,\,\forall t_{n}
-\end{eqnarray*}
-
-\item Average travel time: The average time that a pedestrian needed until
-it reached the goal. The equation for this metric is defined as: \\
-
-\begin{eqnarray*}
-\sum\#\{i_{t_{n}}\}*\triangle t\,\,\forall t_{n}/\#\{i\}
-\end{eqnarray*}
-
-\item Average travel distance: The average distance that a pedestrian traveled
-until it reached the goal. The equation for this metric is defined
-as: \\
-
-\begin{eqnarray*}
-\sum\#\{v_{i,t_{n}}\}*\triangle t\,\,\forall t_{n}/\#\{i\}
-\end{eqnarray*}
-
-\item Average turn angle: The average angle turned by a pedestrian until
-it reached the goal.\\
-
-\begin{eqnarray*}
-    \sum\arccos(v_{t_{n}}\bullet v_{t_{n-1}}/|v_{t_{n}}\bullet v_{t_{n-1}}|)\,\,\forall t_{n}/\#\{i\}
-\end{eqnarray*}
-
-\end{enumerate}
-Escape room: A $20x20[m]$ room with a single $1.2[m]$ exit door
-centered at the bottom. At the beginning, $100$ pedestrians are distributed
-across the room and target the exit. When the first pedestrians exits
-the room, a counter starts, and when the last one croses, it stops.
-This way we can measure the flow of pedestrians leaving a room, which
-is known to be between $0.69$ and $1$ for pedestrians without emergencies
-\cite{key-pedEvDyn2012}. \\
- This scenario is shown in figure \ref{fig:room}.
-
-\begin{figure}[h]
-    \centering{}
-    \includegraphics[scale=0.3]{pics/scenarios/room}
-    \caption{\label{fig:room}Room Scenario}
-\end{figure}
+The results where compared to the SFM \cite{key-helb2000}. The test scenarios
+where crossing and hallway for they present the main types of symmetry
+(90 degrees and 180 degrees respectively).
 
@@
 \begin{enumerate}
-    \item Escape flow: 
-    \begin{eqnarray*}
-    \sum\arccos(v_{t_{n}}\bullet v_{t_{n-1}}/|v_{t_{n}}\bullet v_{t_{n-1}}|)\,\,\forall t_{n}/\#\{i\}
-\end{eqnarray*}
+
+    \item Number of collisions
+    The total amount of collisions between pedestrians.
+
+    \item Total duration of collisions:
+    The sum of the duration of each collision.
+
+    \item Average walking speed:
+    The average of the average speed of each pedestrian.
+
+    \item Average travel time:
+    The average time that a pedestrian needed unit it reached the goal.
+
+    \item Average travel distance:
+    The average distance that a pedestrian traveled unit it reached the
+    goal.
+
+    \item Average turn angle:
+    The average angle turned by a pedestrian unit it reached the goal.
 
@@
 \begin{itemize}
+
 \item Pedestrian
-
 \begin{itemize}
@@
 \end{itemize}
+
 \item FVP-FVP interaction
-
     \begin{itemize}
@@
     \end{itemize}
+
     \item Pedestrian-FVP interaction
-
     \begin{itemize}
@@
     \end{itemize}
+
     \item FVP-Wall interaction
-
     \begin{itemize}
@@
     \hline 
-    Metric  & {\scriptsize{FVPM}} & {\scriptsize{SFM ($\alpha=2000,\,\beta=0.08$)}}\tabularnewline
+    Metric & {\scriptsize{FVPM}} & {\scriptsize{(SFM) $\alpha=2000,\,\beta=0.08$}}\tabularnewline
     \hline 
     \hline 
-    $1$  & {\scriptsize{$1.800\pm20.748$}} & {\scriptsize{$5.333\pm2.625$}}\tabularnewline
+    $1$ & {\scriptsize{$(1.800,0.748)$}} & {\scriptsize{$(5.333,2.625)$}}\tabularnewline
     \hline 
-    $2$  & {\scriptsize{$34.600\pm8.333$}} & {\scriptsize{$12.333\pm8.340$}}\tabularnewline
+    $2$ & {\scriptsize{$(34.600,8.333)$}} & {\scriptsize{$(12.333,8.340)$}}\tabularnewline
     \hline 
-    $3$  & {\scriptsize{$1.024\pm0.016$ $[m/s]$}} & {\scriptsize{$1.052\pm0.003$ $[m/s]$}}\tabularnewline
+    $3$ & {\scriptsize{$(1.024,0.016)$}} & {\scriptsize{$(1.052,0.003)$}}\tabularnewline
     \hline 
-    $4$  & {\scriptsize{$1.910\pm0.022$ $[s]$}} & {\scriptsize{$1.876\pm0.003$ $[s]$}}\tabularnewline
+    $4$ & {\scriptsize{$(1.910,0.022)$}} & {\scriptsize{$(1.876,0.003)$}}\tabularnewline
     \hline 
-    $5$  & {\scriptsize{$2.392\pm0.005$ $[m]$}} & {\scriptsize{$2.391\pm0.002$ $[m]$}}\tabularnewline
+    $5$ & {\scriptsize{$(2.392,0.005)$}} & {\scriptsize{$(2.391,0.002)$}}\tabularnewline
     \hline 
-    $6$  & {\scriptsize{$91.062\pm12.122$ $[rad]$}} & {\scriptsize{$106.185\pm13.778$ $[rad]$}}\tabularnewline
+    $6$ & {\scriptsize{$(91.062,12.122)$}} & {\scriptsize{$(106.185,13.778)$}}\tabularnewline
     \hline 
@@
 
-\begin{figure}[h]
-    \begin{centering}
-    \includegraphics[width=6cm]{pics/program/crossing-no-future} 
-    \par\end{centering}
-    \caption{\label{fig:crossing-no-future}Crossing visualization}
-\end{figure}
-
-\begin{figure}[h]
-    \centering{} \includegraphics[width=6cm]{pics/program/crossing-future}
-    \caption{\label{fig:crossing-future}Crossing visualization with visible future}
-\end{figure}
-
 Metric results for hallway scenario:
@@
     \hline 
-    Metric  & {\scriptsize{FVPM}} & {\scriptsize{SFM ($\alpha=2000,\,\beta=0.08$)}}\tabularnewline
+    Metric & {\scriptsize{FVPM}} & {\scriptsize{(SFM) $\alpha=2000,\,\beta=0.08$}}\tabularnewline
     \hline 
     \hline 
-    $1$  & {\scriptsize{$24.400\pm2.653$}} & {\scriptsize{$52.400\pm4.543$}}\tabularnewline
+    $1$ & {\scriptsize{$(24.400, 2.653)$}} & {\scriptsize{$(52.400, 4.543)$}}\tabularnewline
     \hline 
-    $2$  & {\scriptsize{$190.800\pm28.701$}} & {\scriptsize{$252.800\pm28.764$}}\tabularnewline
+    $2$ & {\scriptsize{$(190.800, 28.701)$}} & {\scriptsize{$(252.800, 28.764)$}}\tabularnewline
     \hline 
-    $3$  & {\scriptsize{$1.237\pm0.014$ $[m/s]$}} & {\scriptsize{$1.235\pm0.002$ $[m/s]$}}\tabularnewline
+    $3$ & {\scriptsize{$(1.237, 0.014)$}} & {\scriptsize{$(1.235, 0.002)$}}\tabularnewline
     \hline 
-    $4$  & {\scriptsize{$0.919\pm0.009$ $[s]$}} & {\scriptsize{$0.920\pm0.003$ $[s]$}}\tabularnewline
+    $4$ & {\scriptsize{$(0.919, 0.009)$}} & {\scriptsize{$(0.920, 0.003)$}}\tabularnewline
     \hline 
-    $5$  & {\scriptsize{$20.922\pm0.132$ $[m]$}} & {\scriptsize{$22.823\pm0.077$ $[m]$}}\tabularnewline
+    $5$ & {\scriptsize{$(20.922, 0.132)$}} & {\scriptsize{$(22.823, 0.077)$}}\tabularnewline
     \hline 
-    $6$  & {\scriptsize{$142.495\pm11.511$ $[rad]$}} & {\scriptsize{$160.950\pm7.749$ $[rad]$}}\tabularnewline
+    $6$ & {\scriptsize{$(142.495, 11.511)$}} & {\scriptsize{$(160.950, 7.749)$}}\tabularnewline
     \hline 
@@
 
-\vspace{1cm}
+% needed in second column of first page if using \IEEEpubid
+%\IEEEpubidadjcol
 
-\begin{figure}[h]
-    \begin{centering}
-    \includegraphics[width=6.5cm]{pics/program/hallway-no-future} 
-    \par\end{centering}
+% An example of a floating figure using the graphicx package.
+% Note that \label must occur AFTER (or within) \caption.
+% For figures, \caption should occur after the \includegraphics.
+% Note that IEEEtran v1.7 and later has special internal code that
+% is designed to preserve the operation of \label within \caption
+% even when the captionsoff option is in effect. However, because
+% of issues like this, it may be the safest practice to put all your
+% \label just after \caption rather than within \caption{}.
+%
+% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
+% option should be used if it is desired that the figures are to be
+% displayed while in draft mode.
+%
+%\begin{figure}[!t]
+%\centering
+%\includegraphics[width=2.5in]{myfigure}
+% where an .eps filename suffix will be assumed under latex, 
+% and a .pdf suffix will be assumed for pdflatex; or what has been declared
+% via \DeclareGraphicsExtensions.
+%\caption{Simulation Results}
+%\label{fig_sim}
+%\end{figure}
 
-    \caption{\label{fig:hallway-no-future}Hallway visualization}
-\end{figure}
+% Note that IEEE typically puts floats only at the top, even when this
+% results in a large percentage of a column being occupied by floats.
 
-\begin{figure}[h]
-    \begin{centering}
-    \includegraphics[width=6.5cm]{pics/program/hallway-future} 
-    \par\end{centering}
+% An example of a double column floating figure using two subfigures.
+% (The subfig.sty package must be loaded for this to work.)
+% The subfigure \label commands are set within each subfloat command, the
+% \label for the overall figure must come after \caption.
+% \hfil must be used as a separator to get equal spacing.
+% The subfigure.sty package works much the same way, except \subfigure is
+% used instead of \subfloat.
+%
+%\begin{figure*}[!t]
+%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
+%\label{fig_first_case}}
+%\hfil
+%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
+%\label{fig_second_case}}}
+%\caption{Simulation results}
+%\label{fig_sim}
+%\end{figure*}
+%
+% Note that often IEEE papers with subfigures do not employ subfigure
+% captions (using the optional argument to \subfloat), but instead will
+% reference/describe all of them (a), (b), etc., within the main caption.
 
-    \caption{\label{fig:hallway-future}Hallway visualization with visible future}
-\end{figure}
-
-The number of collisions is decresead compared to the SFM. The fact
-that the time of collision (metric \#2) is bigger than in the SFM,
-resembles reality, pedestrians don't shoot out at great velocities
-when colliding. The average travel distance is similar in the crossing
-scenario but much smaller in the hallway, this shows the problem of
-SFM in high simmetry scenarios (inverse velocities). \\
- Each pedestrian turns (in average) $10\%$ less with the FVPM than
-with the SFM in both scenarios. \\
-
-\begin{figure}[h]
-    \begin{centering}
-    \includegraphics[width=8.5cm]{pics/steps/room} 
-    \par\end{centering}
-
-    \caption{\label{fig:room-flow}Pedestrian exit flow in room scenario}
-\end{figure}
-
-In the case of the escape room, figure \ref{fig:room-flow} shows
-that the first pedestrian leaves the room at the $5$ seconds mark,
-while the last one does it at the $90$ seconds mark, so the flow
-is: 
-\[
-    flow=\frac{100}{1.2*(90-5)}=\frac{100}{102}=0.98\,\,[ped/sec]
-\]
-
-\begin{figure}[h]
-    \begin{centering}
-    \includegraphics[width=6.5cm]{pics/program/room-no-future} 
-    \par\end{centering}
-
-    \caption{\label{fig:room-no-future} Room visualization}
-\end{figure}
-
-\begin{figure}[h]
-    \centering{} \includegraphics[width=6.5cm]{pics/program/room-future}
-    \caption{\label{fig:room-future} Room visualization with visible future}
-\end{figure}
+% An example of a floating table. Note that, for IEEE style tables, the 
+% \caption command should come BEFORE the table. Table text will default to
+% \footnotesize as IEEE normally uses this smaller font for tables.
+% The \label must come after \caption as always.
+%
+%\begin{table}[!t]
+%% increase table row spacing, adjust to taste
+%\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+%\caption{An Example of a Table}
+%\label{table_example}
+%\centering
+%% Some packages, such as MDW tools, offer better commands for making tables
+%% than the plain LaTeX2e tabular which is used here.
+%\begin{tabular}{|c||c|}
+%\hline
+%One & Two\\
+%\hline
+%Three & Four\\
+%\hline
+%\end{tabular}
+%\end{table}
 
@@
 
-Pedestrians can adjust their desired velocity at will, based on the
-data they perceive. We proposed a model that calculates the desired
-velocity of the social force model by conceptually moving the social
-force into the near future (FVP). The results look more natural than
-the original SFM and have been validated with experimental data. We
-used real-life metrics to validate our model, the results show that
-our model resembles reality with high fidelity. The proposed model
-produces a more natural navigation, but, at high densities, this isn't
-true, we still need further analysis of this scenario to adjust our
-model for both cases. In future work, the paths our virtual pedestrians
-make need to be compared and validated with real-life pedestrians
-paths to complement the use of metrics for the mean of pedestrians.
-Parameters should be revalidated with more metrics and analyzed in
+Pedestrians can adjust their desired velocity at will, based on the data they perceive.
+We proposed a model that calculates the desired velocity of the social force model by
+conceptually moving the social force into the near future (FVP). The results look
+more natural than the original SFM and have been validated with experimental data.
+We used real-life metrics to validate our model, the results show that our model
+resembles reality with high fidelity.
+The proposed model produces a more natural navigation, but, at high densities, this
+isn't true, we still need further analysis of this scenario to adjust our model for
+both cases. In future work, the paths our virtual pedestrians make need to be compared
+and validated with real-life pedestrians paths to complement the use of metrics for the
+mean of pedestrians. Parameters should be revalidated with more metrics and analyzed in
 more detail.
 
-\newpage{}
-\begin{thebibliography}{10}
+\newpage
+
+\appendices
+
+\section{Scenarios}
+
+\begin{figure}[!ht]
+    \begin{centering}
+    \includegraphics[scale=0.25]{./pics/program/hallway-no-future}
+    \par\end{centering}
+    \caption{Hallway}
+\end{figure}
+
+\begin{figure}[!ht]
+    \begin{centering}
+    \includegraphics[scale=0.25]{./pics/program/hallway-future}
+    \par\end{centering}
+    \caption{Hallway with visible future}
+\end{figure}
+
+Explain Hallway scenario measures here
+
+\begin{figure}[!ht]
+    \begin{centering}
+    \includegraphics[scale=0.2]{./pics/program/crossing-no-future}
+    \par\end{centering}
+    \caption{Crossing}
+\end{figure}
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[scale=0.2]{./pics/program/crossing-future}
+    \caption{Crossing with visible future}
+\end{figure}
+
+Explain Crossing scenario measures here
+
+\begin{figure}[!ht]
+    \begin{centering}
+    \includegraphics[scale=0.25]{./pics/program/room-no-future}
+    \par\end{centering}
+    \caption{Room}
+\end{figure}
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[scale=0.25]{./pics/program/room-future}
+    \caption{Room with visible future}
+\end{figure}
+
+Explain Room scenario measures here
+
+\section*{Acknowledgment}
+The authors would like to thank Daniel Parisi, ITBA, .... for ....
+
+\vfill
+
+\begin{thebibliography}{1}
 
 \bibitem{key-hoog2004} Hoogonen and Bovy (2004).
+\bibitem{key-scha2009} A. Schadschneider (2009). "Evacuation Dynamics: Empirical Results, Modeling and Applications".
+\bibitem{key-scha2002} A. Schadschneider (2009). "Traffic flow: A statistical physics point of view".
+\bibitem{key-helb1995} Helbing, Dirk; Molnr, Pter (1995). “Social force model for pedestrian dynamics”.
+\bibitem{key-helb2000} Helbing, Dirk; Farkas, Ills; Vicsek, Tams (2000). “Simulating dynamical features of escape panic”.
+\bibitem{key-tara2005} Taras I. Lakoba (2005). "Modifications of the Helbing-Molnár-Farkas-Vicsek Social Force Model for Pedestrian Evolution".
+\bibitem{key-pari2009} Parisi (2009). "A modification of the Social Force Model can reproduce experimental data of pedestrian flows in normal conditions".
+\bibitem{key-kirc2002} Kirchner and Schadschneider (2002). "Simulation ofevacuation processes using a bionics-inspired cellular automaton model for pedestrian dynamics".
+\bibitem{key-pari2011} Baglietto and Parisi, (2011). "Continuous-space automaton model for pedestrian dynamics".
+\bibitem{key-kara2009} I. Karamouzas (2009). "A Predictive Collision Avoidance Model for Pedestrian Simulation".
+\bibitem{key-kret2001} Kretz (2011). "Quickest Paths in Simulations of Pedestrians".
+\bibitem{key-mous2009} Moussad M, Helbing D, Garnier S, Johansson A, Combe M and aulaz G (2009).
 
-\bibitem{key-scha2009} A. Schadschneider (2009). \textquotedbl{}Evacuation
-Dynamics: Empirical Results, Modeling and Applications\textquotedbl{}.
-
-\bibitem{key-scha2002} A. Schadschneider (2009). \textquotedbl{}Traffic
-flow: A statistical physics point of view\textquotedbl{}.
-
-\bibitem{key-helb1995} Helbing, Dirk; Molnr, Pter (1995). ``Social
-force model for pedestrian dynamics``.
-
-\bibitem{key-helb2000} Helbing, Dirk; Farkas, Ills; Vicsek, Tams
-(2000). ``Simulating dynamical features of escape panic``.
-
-\bibitem{key-tara2005} Taras I. Lakoba (2005). \textquotedbl{}Modifications
-of the Helbing-Molnar-Farkas-Vicsek Social Force Model for Pedestrian
-Evolution\textquotedbl{}.
-
-\bibitem{key-pari2009} Parisi (2009). \textquotedbl{}A modification
-of the Social Force Model can reproduce experimental data of pedestrian
-flows in normal conditions\textquotedbl{}.
-
-\bibitem{key-kirc2002} Kirchner and Schadschneider (2002). \textquotedbl{}Simulation
-ofevacuation processes using a bionics-inspired cellular automaton
-model for pedestrian dynamics\textquotedbl{}.
-
-\bibitem{key-pari2011} Baglietto and Parisi, (2011). \textquotedbl{}Continuous-space
-automaton model for pedestrian dynamics\textquotedbl{}.
-
-\bibitem{key-kara2009} I. Karamouzas (2009). \textquotedbl{}A Predictive
-Collision Avoidance Model for Pedestrian Simulation\textquotedbl{}.
-
-\bibitem{key-kret2001} Kretz (2011). \textquotedbl{}Quickest Paths
-in Simulations of Pedestrians\textquotedbl{}.
-
-\bibitem{key-mous2009} Moussad M, Helbing D, Garnier S, Johansson
-A, Combe M and aulaz G (2009).
-
-\bibitem{key-pedEvDyn2012} Ulrich Weidmann, Uwe Kirsch, Michael Schreckenberg
-(2012). Pedestrian and Evacuation Dynamics 2012.\end{thebibliography}
+\end{thebibliography}
 

### 2015-06-09 doc/informe/informe.tex
elimino varios archivos tex con cosas viejas. Actualizo imagenes. Actualizo informe.

@@
 \usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
+\usepackage[utf8]{inputenc}
 \usepackage{graphicx}
+
+\usepackage{float}
+\usepackage{babel}
+
+\usepackage{array}
+\usepackage{multirow}
+
+\usepackage[font=small,labelfont=bf,labelsep=space]{caption}
+\captionsetup{
+  figurename = Figure,
+  tablename = Table
+}
 
@@
 
-%% Because html converters don't know tabularnewline
 \providecommand{\tabularnewline}{\\}
-
-\usepackage{babel}
 
@@
 
-\usepackage{babel}
 \begin{document}
 
-\title{Future Virtual Particle Method for Pedestrian Navigation}
+\title{
+    Proyecto Final para la obtención del título: Ingeniero en Informática
+    \tabularnewline
+    \large Future Virtual Particle Method for Pedestrian Navigation
+}
 
@@
   \and
-  Parisi, Daniel\\
-  \texttt{danielparisi@xxxxx.com}
+  Dr. Parisi, Daniel Ricardo \\
+  \texttt{dparisi@itba.edu.ar}
 }
@@
 
-\vspace{10cm}
+\vspace{8cm}
 \begin{center}
-    \includegraphics[scale=0.08]{pics/ITBA}
+    \includegraphics[scale=0.1]{pics/ITBA}
     \par
@@
 
+\tableofcontents{}
+
+\pagebreak{}
+
 \begin{abstract}
-Pedestrians are modeled as passive objects affected by repulsive and
-attractive forces in the Social Force Model (SFM). This force governed
-model leads to unnatural behaviors that don't resemble reality. This
-paper presents an avoidance collision method based in pedestrian self
+% Pedestrians are modeled as objects affected by repulsive and attractive forces in the Social Force Model (SFM). 
+This paper presents an avoidance collision method based in pedestrian self
 governed decisions, by calculating the position of every pedestrian
 in the future, a given pedestrian can adjust his velocity vector to
-avoid collisions instead of a repulsive force.
-
+avoid collisions instead of being affected by a repulsive force. \\
+The model was tested using three different scenarios and compared 
+against the Social Force Model obtaining more natural navigation,
+reduced number of collisions, increased average
+speed and reduced average deviation angle of navigating pedestrians.
 \textbf{keywords:} pedestrian, collision avoidance, future virtual
@@
 
-Navigation of biological, sinthetic or virtual agents is a relevant
+    Navigation of biological, synthetic or virtual agents is a relevant
     problem in several fields such as pedestrian dynamics, moving robots
-and animation of characters for videogames and motion pictures.
+    and animation of characters for video games and motion pictures.
 
@@
     \begin{equation}
-\vec{e_{i}}=\frac{\vec{x}_{i}^{k}-\vec{x}_{i}(t)}{||\vec{x}_{i}^{k}-\vec{x}_{i}(t)||}\label{eq:desired-direction}
+    \vec{e_{i}}=\frac{\vec{x}_{i0}-\vec{x}_{i}(t)}{||\vec{x}_{i0}-\vec{x}_{i}(t)||}\label{eq:desired-direction}
     \end{equation}
@@
 
-$x_{i}^{k}$ is the closest point from the goal (represented as an
+    $x_{i0}$ is the closest point from the goal (represented as an
     area) to pedestrian $i$. \\
 
-Figure \ref{fig:driving-force} shows a pedestrian moving with $\vec{v}$
+    Fig. \ref{fig:driving-force} shows a pedestrian moving with $\vec{v}$
     velocity but adjusting its trajectory towards \textbf{$X$}.
@@
         \includegraphics[scale=0.4]{pics/sfm/drivingforce} 
-\par\end{centering}
-
-\caption{\label{fig:driving-force}Driving force}
+        \par
+        \end{centering}
+        \caption{\label{fig:driving-force} Driving force}
     \end{figure}
@@
 
-Figure \ref{fig:Social-Force} shows \ref{eq:social-force} graphically.
+    Fig. \ref{fig:Social-Force} shows equation \ref{eq:social-force} graphically.
 
@@
         \begin{centering}
-\includegraphics[scale=0.4]{pics/sfm/sf} 
-\par\end{centering}
-
+        \includegraphics[scale=0.4]{pics/sfm/sf} \par
+        \end{centering}
         \caption{Social Force\label{fig:Social-Force}}
@@
 
-The third term is known as the ``Granular force''. It's calculated
+    The third term is known as the ``Contact force''. It's calculated
     as follows:
@@
     \begin{equation}
-\vec{F}_{G_{i}}=\sum_{j=1,j\ne i}^{N_{P}}[-\epsilon_{ij}k_{n}\vec{e}_{ij}^{n}+v_{ij}^{t}\epsilon_{ij}k_{t}\vec{e}_{ij}^{t}]\, g(\epsilon_{ij})\label{eq:granular-force}
+        \vec{F}_{G_{i}} = \sum_{j=1,j\ne i}^{N_{P}} [-\epsilon_{ij}k_{n}\vec{e}_{ij}^{n} + v_{ij}^{t} \epsilon_{ij} k_{t} \vec{e}_{ij}^{t}] \, g(\epsilon_{ij})
+        \label{eq:granular-force}
     \end{equation}
@@
 
-Figure \ref{fig:colliding-pedestrians} shows \ref{eq:granular-force}
-graphically.
+    Fig. \ref{fig:colliding-pedestrians} shows \ref{eq:granular-force} graphically.
 
@@
         \begin{centering}
-\includegraphics[scale=0.4]{pics/sfm/ganular} 
-\par\end{centering}
-
+        \includegraphics[scale=0.4]{pics/sfm/ganular} \par
+        \end{centering}
         \caption{Colliding pedestrians\label{fig:colliding-pedestrians}}
@@
     \end{tabular}
-\par\end{center}
+    \par
+    \end{center}
 
@@
     short term objective, which is equal to equation \ref{eq:desired-direction}
-replacing $\vec{x}_{i}^{k}$ with $\vec{x_{i'}}$, where $\vec{x_{i'}}$
+    replacing $\vec{x}_{i}^{0}$ with $\vec{x_{i'}}$, where $\vec{x_{i'}}$
     is an estimation of the location of pedestrian $i$ in the near future.
-$i'$ will be called Future Virtual Particle.
+    $i'$ will be called Future Virtual Particle. \\
 
-AGREGADO POR PARISI: LLEGAMOS A POSTULAR ESTE MODELO DESPUES DE VARIOS CICLOS DE ITERACIONES Y NUMEROSAS PRUEBAS DE DE VARIANTES HASTA CONVERGER AL MODELO PRESENTADO QUE MODELA ADECUADAMENTE VARIAS SITUACIONES
-
+    The presented work demanded a deep understanding of the problem in question, for which a 
+    great study of related work was done. After that, we proposed various different models which
+    were validated and reformed until it converged to this model, which validate against real
+    world scenarios and metrics.
 \section{The Model}
@@
 
-The heuristics that govern the motion of a pedestrian are the same
+    The basic concepts below the model of pedestrian movement are the same
     as Helbin's \cite{key-helb1995,key-helb2000}:
@@
 
-    Represents the personal space of a pedetrian. The value of the radio
+        Represents the personal space of a pedestrian. The value of the radio
         is generated randomly for each pedestrian. The range of values is
@@
         \includegraphics[scale=0.4]{pics/pedestrian-top} 
-    \caption{\label{fig:pedestrian-geometry}Illustration of pedestrian $i$ and its FVP ($i'$).}
+        \caption{\label{fig:pedestrian-geometry} Pedestrian $i$ and its FVP ($i'$).}
     \end{figure}
 
-The naming used is shown in illustration \ref{fig:pedestrian-vectors}.
+    The naming convention used for all vectors related to a pedestrian is shown in 
+    fig. \ref{fig:pedestrian-vectors}.
 
@@
         \includegraphics[scale=0.4]{pics/geometry}
-    \caption{\label{fig:pedestrian-vectors}Vectorial definitions}
+        \caption{\label{fig:pedestrian-vectors} Vectors definitions}
     \end{figure}
@@
         To model this situations, two types of forces act over the FVP:
+
         \begin{itemize}
@@
 
-This force will guide the pedestrian on the shortest path $\mathbf{x_{o}x_{i}}$.
-This force is modeled using two springs:
+            For any pedestrian $i$, its internal force is
 
-The first spring starts on $x_{i}$, ends on $x_{i'}$ and has a stationary
-distance of $RD$ with a spring constant $K_{s}(\theta)$ where $\theta$
-is the angle between $\mathbf{u}$ and $\mathbf{r}$. With this spring
-the FVP will tend to always be at $RD$ distance from the pedestrian.
+            \begin{equation}
+                F_{i'}^{internal} = F_{i'}^{S1} + F_{i'}^{S2}
+            \end{equation}
+            where
+            \[
+                F_{i'}^{S1} = K_{1}(\theta_{i}) * (|\vec{r}| - RD) \hat{r}
+            \]
+            \[
+                F_{i'}^{S2} = K_{2} * (\vec{x_{i'}} - (\vec{x_{i}} + \hat{x_{io}} RD))
+            \]
+
+            This force aligns the future on the path $\mathbf{x_{io}}$ and is modeled using 
+            two springs $S_1$ and $S_2$:\\
+
+            $S_1$ starts on $\mathbf{x_{i}}$, ends on $\mathbf{x_{i'}}$ and 
+            has a stationary distance of $RD$ with a spring constant $K_{1}(\theta)$ 
+            where $\theta$ is the angle between $\mathbf{u}$ and $\mathbf{r}$. With this 
+            spring the FVP will tend to always be at $RD$ distance from the pedestrian.
             Because a pedestrian always tries to reach his goal in the shortest
@@
             \[
-K_{s}(\theta)=\frac{K_{2}}{\theta}
+                K_{1}(\theta) = \frac{K_{1c}}{\theta}
             \]
+            where $K_{1c}$ is a constant value.
 
-The second spring starts on $x_{i'}$ and ends on $x_{i}+RD\frac{\vec{x_{i}x_{o}}}{\mid\vec{x_{i}x_{o}}\mid}$
-with a spring constant $K_{1}$. This spring represents the pedestrian's
-desire to reach his target. A greater spring constant will force a
-straighter path. In order to avoid an oscillatory movement, a damping
-$\gamma$ was added to the spring.\\
+            $S_2$ starts on $\mathbf{x_{i'}}$ and ends on $\mathbf{x_{i}} + RD\mathbf{{\hat{x}_{io}}}$
+            with a spring constant $K_{2c}$. Setting a greater $K_{2c}$ spring constant 
+            will force a straighter path but may result in more collisions. In order to 
+            avoid an oscillatory movement, a damping $\gamma$ is added to the spring $S_2$. \\
+            Fig. \ref{fig:internal-forces} shows the internal forces that a FVP $i'$ suffers 
+            because it has to be aligned with the pedestrian's position $\mathbf{x_{i}}$ and the long 
+            term objective $\mathbf{x_{o}}$ but also at distance $RD$ from $\mathbf{x_{i}}$.
 
-For any pedestrian $i$, its internal force is
+            \begin{figure}[H]
+                \centering{}
+                \includegraphics[scale=0.35]{pics/pedestrian-internal-forces}
+                \caption{\label{fig:internal-forces} Internal forces}
+            \end{figure}
 
+        \item External forces \\
+
+            This force will produce avoidance movements when obstacles are detected
+            on the path. The equation for the external force that affects the FVP $i'$ is
             \begin{equation}
-    F_{internal}(i)=F_{S1}(i)+F_{S2}(i)
+                F_{i'}^{external} = FF_{i'} + FP_{i'} + FW_{i'} \label{eq:externalforce}
             \end{equation}
-
             where 
-
             \[
-    F_{S1}(i)=K_{1}\cdot(|\vec{r}|-RD)\cdot\hat{r}
+                FF_{i'} = \sum_{j}^{N}(\alpha_{ff}e^{-s/\beta_{ff}})
             \]
             \[
-    F_{S2}(i)=\, K_{2}(\theta_{i})\cdot(\vec{x_{i'}}-(\vec{x_{i}}+\hat{x_{i}o}\cdot RD))
-\]
-
-\begin{figure}[h]
-    \centering{}\includegraphics[scale=0.35]{pics/pedestrian-internal-forces}
-    \caption{Pedestrian internal forces}
-\end{figure}
-
-\item Avoidance forces \\
- This force will produce avoidance movements when obstacles are detected
-on the path. The magnitude of this force is calculated using two factors:
-\\
- The first factor is calculated for each of the pedestrian $j$ ($j\neq i$)
-who is in the range of sight of pedestrian $i$. This restriction
-is verified using the following condition:
-
-\[
-    \mathbf{r_{ii'}}\bullet\mathbf{r_{ij}}<0
-\]
-
-This condition represents the fact that pedestrians make decisions
-based only on obstacles in his range of vision. The formula for the
-external force that affects the FVP $i'$ is
-
-\[
-    F_{ext}(i')=FF(i')+FP(i')+FW(i')
-\]
-where 
-\[
-    FF_{(}i')=\sum_{j}(\alpha_{ff}e^{-s/\beta_{ff}})
+                FP_{i'} = \sum_{j}^{N}(\alpha_{fp}e^{-t/\beta_{fp}})
             \]
             \[
-    FP_{(}i')=\sum_{j}(\alpha_{fp}e^{-t/\beta_{fp}})
+                FW_{i'} = \sum_{k}^{walls}(\alpha_{fw}e^{-\zeta_{k} /\beta_{fw}})
             \]
+            having $\zeta_{k} = |x_{i'} - x_{k}|$; $x_{k}$ being the closest point from wall 
+            $k$ to $x_{i'}$. \\
+            $\alpha$ and $\beta$ are constants. \\
+            The term $FF_{i'}$ in equation \ref{eq:externalforce} acts as a repulsion force 
+            between $i'$ and $j'$, resulting in the avoidance of a future collision. The term 
+            $FP_{i'}$ in equation \ref{eq:externalforce} uses this same principle but 
+            calculates the repulsion  force between $i'$ and $j$. The term $FW_{i'}$ in equation 
+            \ref{eq:externalforce} adds the repulsion against walls,  using the closest point 
+            between $i'$ and the wall. \\
+            This force is only applied to each the pedestrian $j$ ($j\neq i$)
+            who is in the range of sight of pedestrian $i$. The restriction
+            is verified using the following condition:
             \[
-    FW_{(}i')=\sum_{w}(\alpha_{fw}e^{-dist(w,i')/\beta_{fw}})
+                \mathbf{r_{ii'}}\bullet\mathbf{r_{ij}} > 0
             \]
-
-where $\alpha_{x}$ and $\beta_{x}$ are constants.
-
-The first term of the sum acts as a repulsion force between $i'$
-and $j'$, resulting in the avoidance of a future collision. The second
-term uses this same principle but calculates the repulsion force between
-$j'$ and $i$. The third term adds the repulsion against walls, using
-the closest point between $i'$ and the wall.
-
-Figure \ref{fig:External-forces-affecting} shows the external forces
-that a pedestrian $i$ suffers because of another pedestrian ($j$)
+            The condition represents the fact that pedestrians make decisions
+            based only on obstacles in his range of vision. \\
+            Fig. \ref{fig:external-forces} shows the external forces
+            that a FVP $i'$ suffers because of another pedestrian ($j$)
             and also the direction in which $i$ desires to move.
 
-\begin{figure}[h]
+            \begin{figure}[H]
                 \centering{}
-    \includegraphics[scale=0.4]{pics/pedestrian-top-forces}
-    \caption{\label{fig:External-forces-affecting}External forces affecting future$i'$}
+                \includegraphics[scale=0.35]{pics/pedestrian-top-forces}
+                \caption{\label{fig:external-forces} External forces}
             \end{figure}
@@
 
-After this, the final $F_{i'}$ is computed by adding all the terms.
-$F_{i'}=F_{ext}(i)+F_{i\, s1}+F_{i\, s2}$.\\
+        After this, $F_{i'}$ is computed by adding all the terms.
 
-To avoid high symetry situations, a low noise $P=10\%$ is added to
-$F$. There are two ways to apply this noise: 
-\begin{itemize}
+        \begin{equation}
+            F_{i'} = F_{i'}^{external} + F_{i'}^{internal} \label{eq:future-force}
+        \end{equation}
 
-\item Radial noise:
-
-\begin{itemize}
-\item A value $p$ is taken randomly from a uniform distribution $[-P,\, P]$
-and calculate: $FL_{i'}=F_{i'}*p$ 
-\item Angular noise:
-
-    \begin{itemize}
-        \item A value $sgn=\{-1,\,1\}$ is taken randomly from a uniform distribution
-        and a value $p$ from $[-P,\, P]$. Then \\
+        To avoid high symmetry situations, a small noise is added to $F$. 
+        This noise is calculated by taking a random value $s$ with a random distribution from $\{-1, 1\}$
+        and applying:
         \[
             M=\left(\begin{array}{cc}
-            \cos(\pi*sgn) & -\sin(\pi*sgn)\\
-            \sin(\pi*sgn) & \cos(\pi*sgn)
+            0 & -s\\
+            s & 0
             \end{array}\right)
         \]
+        in
         \[
-            FA_{i'}=F_{i'}*p*M
+            F'_{i'} = F_{i'} + F_{i'} * M
         \]
-    \end{itemize}
-\end{itemize}
 
-At last, we find $F'_{i'}=F_{i'}+FL_{i'}+FA_{i'}$ and apply movement
-equations.
-\end{itemize}
+        Finally, movement equations are applied using $F'_{i'}$.
+
     \item Dynamic of the pedestrian
 
-The pedestrian always wants to move in the direction his FVP is pointing
-and its magnitude is defined as $F_{d}$ or driving force:
+        The driving force $\vec{F}_{d_{i}}$ makes the pedestrian tend to move towards his FVP at velocity $v_{di}$
+        \[
+            \vec{F}_{d_{i}} = m_{i}\frac{|v_{di}|\frac{\vec{r}}{RD} - \vec{v}_{i}}{\tau}
+        \]
+        where $\tau=0.5$\\
 
-\[
-    \vec{F}_{desire_{i}}=m_{i}\frac{\frac{|\vec{ii'}|}{|\vec{r}_{max}|}\vec{e_{i}}-\vec{v}_{i}}{\tau}
-\]
-
-Where $\tau=0.5$
-
-\textit{{*}It is important to note that the only deviation from the
+        It is important to note that the only deviation from the
         SFM in this equation is the $k\vec{e}_{i}$ term. As described above,
         this model focuses on improving the SFM through dynamically adjusting
-the desired velocity.}
+        the desired velocity.
 
@@
         \item Calculate forces for each FVP. 
+        \item Calculate forces for each pedestrian. 
         \item Update positions for each FVP. 
-    \item Calculate forces for each pedestrian. 
         \item Update positions for each pedestrian. 
@@
 
-\subsection{Metrics}
+    \subsection{Scenarios}
 
-The results where compared to the SFM model \cite{key-helb2000}.
         The test scenarios where crossing and hallway for they present the
@@
         end as target. \\
- This scenario is shown in figure \ref{fig:hallway-scenario}.
+         This scenario is shown in fig. \ref{fig:hallway-scenario}.
 
-\begin{figure}[h]
+        \begin{figure}[H]
             \centering{}
@@
 
-Crossing scenario: Two hallways of $25[m]$ lenght by $5[m]$ width
-put toghether in the center forming a cross. Pedestrians are generated
+        Crossing scenario: Two hallways of $25[m]$ length by $5[m]$ width
+        put together in the center forming a cross. Pedestrians are generated
         from the top, targeting the bottom, and from the right end, targeting
         the left end, at a pace of 1 pedestrian per second. \\
- This scenario is shown in figure \ref{fig:cross-scenario}.
+         This scenario is shown in fig. \ref{fig:cross-scenario}.
 
-\begin{figure}[h]
+        \begin{figure}[H]
             \centering{}
             \includegraphics[scale=0.3]{pics/scenarios/cross}
-    \caption{\label{fig:cross-scenario}Cross Scenario}
+            \caption{\label{fig:cross-scenario} Cross Scenario}
         \end{figure}
 
-The metrics used to validate and verify the model against the defined
-two previous scenarios are defined as follows:
+        Room evacuation: A $20x20[m]$ room with a single exit door
+        centered at the bottom. At the beginning, a fixed number of pedestrians are 
+        distributed across the room. Each of them targeting the exit door. When the 
+        first pedestrian exits the room, a counter starts, and when the last one 
+        crosses, it stops. This way we can measure the flow of pedestrians leaving a 
+        room, which is known to be between $1$ and $4$ [p/m/s] for pedestrians 
+        without emergencies \cite{key-pari2009}. \\
+        The door size will be tested using the following measures: $1.2[m]$, $1.5[m]$ and $1.8[m]$. \\
+        This scenario is shown in fig. \ref{fig:room}.
+        \begin{figure}[H]
+            \centering{}
+            \includegraphics[scale=0.3]{pics/scenarios/room}
+            \caption{\label{fig:room} Room Scenario}
+        \end{figure}
+
+    \subsection{Metrics}
+        The metrics used to validate and verify the model against the hallway and 
+        crossing scenarios are defined as follows:
+
         \begin{enumerate}
-\item Number of collisions: The equation for this metric is defined as:
-\\
+            \item Number of collisions:
 
             \begin{eqnarray*}
-    \sum\#\{(i,j)\,/\, id_{i}<id_{j}\wedge\\
-    x_{i,t_{n}}-x_{j,t_{n}}<R_{i}+R_{j}\wedge\\
-    x_{i,t_{n-1}}-x_{j,t_{n-1}}>R_{i}+R_{j}\}\,\,\forall t_{n}
+                \sum_t\sum_i\sum_j collides(i,j)/2
             \end{eqnarray*}
 
-\item Amount of collitions per instant: The equation for this metric is
-defined as: \\
+            where
 
             \begin{eqnarray*}
-    \sum\#\{(i,j)\,/\, id_{i}<id_{j}\wedge\\
-    x_{i,t_{n}}-x_{j,t_{n}}<R_{i}+R_{j}\}\,\,\forall t_{n}
+            collides(i,j,t) = touching(i,j,t) (1 - touching(i,j,t-1))\\
             \end{eqnarray*}
 
-\item Average walking speed: The equation for this metric is defined as:
-\\
+            \begin{eqnarray*}
+            touching(i,j,t) = 
+            \left \{
+                \begin{tabular}{cc}
+                $0$ & if $t<=0$\\
+                $1$ & if $x_i-x_j<R_i+R_j$\\
+                $0$ & if not
+                \end{tabular}
+            \right .
+            \end{eqnarray*}
+
+            \item Amount of collisions per instant: The equation for this metric is
+            defined as:
 
             \begin{eqnarray*}
-    \sum v_{i,t_{n}}/\#\{i_{t_{n}}\}\,\,\forall t_{n}
+                \sum_t\sum_i\sum_j touching(i,j)/2
+                %\sum\#\{(i,j)\,/\, id_{i}<id_{j}\wedge\\
+                %x_{i,t_{n}}-x_{j,t_{n}}<R_{i}+R_{j}\}\,\,\forall t_{n}
             \end{eqnarray*}
 
-\item Average travel time: The average time that a pedestrian needed until
-it reached the goal. The equation for this metric is defined as: \\
+            \item Average walking speed:
 
             \begin{eqnarray*}
-\sum\#\{i_{t_{n}}\}*\triangle t\,\,\forall t_{n}/\#\{i\}
+                \sum_{t=0}^T((\sum_{i=0}^N v_i)/N)/T
             \end{eqnarray*}
 
-\item Average travel distance: The average distance that a pedestrian traveled
-until it reached the goal. The equation for this metric is defined
-as: \\
+            \item Average travel time: The average time that a pedestrian takes to
+            reach the goal. This is calculated only for pedestrians who reach the goal
+            before the simulation ends.
+
+            \item Average travel distance: The average distance that pedestrians traveled
+            until it reached the goal. This is calculated only for pedestrians who reach the goal
+            before the simulation ends.
+
+            \item Average turn angle: The average angle turned by a pedestrian until
+            it reached the goal. This is calculated only for pedestrians who reach the goal
+            before the simulation ends.\\
+            where the turn angle is:
 
             \begin{eqnarray*}
-\sum\#\{v_{i,t_{n}}\}*\triangle t\,\,\forall t_{n}/\#\{i\}
-\end{eqnarray*}
-
-\item Average turn angle: The average angle turned by a pedestrian until
-it reached the goal.\\
-
-\begin{eqnarray*}
-    \sum\arccos(v_{t_{n}}\bullet v_{t_{n-1}}/|v_{t_{n}}\bullet v_{t_{n-1}}|)\,\,\forall t_{n}/\#\{i\}
-\end{eqnarray*}
-
-\end{enumerate}
-Escape room: A $20x20[m]$ room with a single $1.2[m]$ exit door
-centered at the bottom. At the beginning, $100$ pedestrians are distributed
-across the room and target the exit. When the first pedestrians exits
-the room, a counter starts, and when the last one croses, it stops.
-This way we can measure the flow of pedestrians leaving a room, which
-is known to be between $0.69$ and $1$ for pedestrians without emergencies
-\cite{key-pedEvDyn2012}. \\
- This scenario is shown in figure \ref{fig:room}.
-
-\begin{figure}[h]
-    \centering{}
-    \includegraphics[scale=0.3]{pics/scenarios/room}
-    \caption{\label{fig:room}Room Scenario}
-\end{figure}
-
-The metrics used where: 
-\begin{enumerate}
-    \item Escape flow: 
-    \begin{eqnarray*}
-    \sum\arccos(v_{t_{n}}\bullet v_{t_{n-1}}/|v_{t_{n}}\bullet v_{t_{n-1}}|)\,\,\forall t_{n}/\#\{i\}
+                \arccos(v_{t_{n}}\bullet v_{t_{n-1}}/|v_{t_{n}}\bullet v_{t_{n-1}}|)
             \end{eqnarray*}
@@
 
+        The metric used for the room evacuation scenario is:
+
+        \begin{enumerate}
+            \item Escape flow: The amount of pedestrians coming out of the room by second.
+            \begin{eqnarray*}
+                \frac{N}{\Delta T}
+            \end{eqnarray*}
+
+            where $\Delta T$ is the time when the last pedestrian exits minus
+            the time when the first pedestrian exits.
+
+        \end{enumerate}
+
+        All results were compared to the SFM model \cite{key-helb2000}.
+
     \subsection{Values}
 
-To calibrate the model, runs varying parameters were made. A wide
-spectrum of values was covered, testing every combination of every
-possible one. After seeing clear preferences towards certain values,
-the values were refined within that scope. After numerous iterations
-of this process, the values that best suit these metrics are:
+        To calibrate the model, runs with varying parameters were made.
+        % MARSE TRADUCIR: Los parametros fueron buscados de manera exhaustiva usando una tecnica de barrido.
+        % Se variaron los parametros FVP-FVP: $\alpha$ y $\beta$ realizando incrementos de a 0.2
+
+        All runs used Euler method with a step of $\frac{1}{1000}$ $[s]$. For each scenario 
+        and parameter combination, $10$ runs were made 
+        and their metric results averaged and compared against each set of parameters. \\
+        After numerous iterations of this process, this are the parameters which best fit all scenarios:
 
@@
             \begin{itemize}
-        \item $K_{1}=100$ {[}N/m{]}, 
+                \item $K_{1}=80$ {[}N/m{]}, 
                 \item $\gamma=10$ 
-        \item $K_{2}=150$ {[}N/m{]} 
+                \item $K_{2}=100$ {[}N/m{]} 
             \end{itemize}
@@
                 \item $\alpha=1000$ 
-        \item $\beta=[0.4,\,0.5]$ (Uniform distribution) 
+                \item $\beta=[0.4,\,0.6]$ (Uniform distribution) 
                 \end{itemize}
@@
 
-Metric results for crossing scenario:
+    All results for each metric for the crossing scenario are presented on table \ref{table:metric-crossing}:
 
+    \begin{table}[H]
+        \begin{centering}
             \begin{tabular}{|c|c|c|}
@@
                 \hline 
-    $1$  & {\scriptsize{$1.800\pm20.748$}} & {\scriptsize{$5.333\pm2.625$}}\tabularnewline
+                $1$  & {\scriptsize{$15.0\pm4.3$}} & {\scriptsize{$23.2\pm6.4$}}\tabularnewline
                 \hline 
-    $2$  & {\scriptsize{$34.600\pm8.333$}} & {\scriptsize{$12.333\pm8.340$}}\tabularnewline
+                $2$  & {\scriptsize{$158.2\pm60.6$}} & {\scriptsize{$57.2\pm18.8$}}\tabularnewline
                 \hline 
-    $3$  & {\scriptsize{$1.024\pm0.016$ $[m/s]$}} & {\scriptsize{$1.052\pm0.003$ $[m/s]$}}\tabularnewline
+                $3$  & {\scriptsize{$1.26\pm0.02$ $[m/s]$}} & {\scriptsize{$1.28\pm0.01$ $[m/s]$}}\tabularnewline
                 \hline 
-    $4$  & {\scriptsize{$1.910\pm0.022$ $[s]$}} & {\scriptsize{$1.876\pm0.003$ $[s]$}}\tabularnewline
+                $4$  & {\scriptsize{$17.61\pm0.27$ $[s]$}} & {\scriptsize{$17.33\pm0.06$ $[s]$}}\tabularnewline
                 \hline 
-    $5$  & {\scriptsize{$2.392\pm0.005$ $[m]$}} & {\scriptsize{$2.391\pm0.002$ $[m]$}}\tabularnewline
+                $5$  & {\scriptsize{$22.61\pm0.07$ $[m]$}} & {\scriptsize{$22.52\pm0.07$ $[m]$}}\tabularnewline
                 \hline 
-    $6$  & {\scriptsize{$91.062\pm12.122$ $[rad]$}} & {\scriptsize{$106.185\pm13.778$ $[rad]$}}\tabularnewline
+                $6$  & {\scriptsize{$103.35\pm32.81$ $[rad]$}} & {\scriptsize{$193.06\pm20.44$ $[rad]$}}\tabularnewline
                 \hline 
             \end{tabular}
+        \par\end{centering}
+        \caption{Results for crossing scenario \label{table:metric-crossing}}
+    \end{table}
 
-\vspace{1cm}
+    Metrics for the crossing scenario don't present noticeable improvements over the SFM.
+    The one improvement is the average turn angle, which can be recognized by looking
+    and comparing the two models. The SFM presents a much more unnatural navigation than
+    the FVPM.
 
-\begin{figure}[h]
+    \begin{figure}[H]
         \begin{centering}
             \includegraphics[width=6cm]{pics/program/crossing-no-future} 
-    \par\end{centering}
+            \par
+        \end{centering}
         \caption{\label{fig:crossing-no-future}Crossing visualization}
@@
 
-\begin{figure}[h]
+    \begin{figure}[H]
         \centering{} \includegraphics[width=6cm]{pics/program/crossing-future}
@@
 
-Metric results for hallway scenario:
-
+    \vspace{1cm}
+    All results for each metric for the hallway scenario are presented on table \ref{table:metric-hallway}:
+    \begin{table}[H]
+        \begin{centering}
 			\begin{tabular}{|c|c|c|}
@@
 				\hline 
-    $1$  & {\scriptsize{$24.400\pm2.653$}} & {\scriptsize{$52.400\pm4.543$}}\tabularnewline
+				$1$  & {\scriptsize{$7.8\pm5.3$}} & {\scriptsize{$20.8\pm8.5$}}\tabularnewline
 				\hline 
-    $2$  & {\scriptsize{$190.800\pm28.701$}} & {\scriptsize{$252.800\pm28.764$}}\tabularnewline
+				$2$  & {\scriptsize{$53.8\pm29.5$}} & {\scriptsize{$85.2\pm32.3$}}\tabularnewline
 				\hline 
-    $3$  & {\scriptsize{$1.237\pm0.014$ $[m/s]$}} & {\scriptsize{$1.235\pm0.002$ $[m/s]$}}\tabularnewline
+				$3$  & {\scriptsize{$1.27\pm0.01$ $[m/s]$}} & {\scriptsize{$1.04\pm0.08$ $[m/s]$}}\tabularnewline
 				\hline 
-    $4$  & {\scriptsize{$0.919\pm0.009$ $[s]$}} & {\scriptsize{$0.920\pm0.003$ $[s]$}}\tabularnewline
+				$4$  & {\scriptsize{$13.15\pm0.06$ $[s]$}} & {\scriptsize{$18.17\pm2.12$ $[s]$}}\tabularnewline
 				\hline 
-    $5$  & {\scriptsize{$20.922\pm0.132$ $[m]$}} & {\scriptsize{$22.823\pm0.077$ $[m]$}}\tabularnewline
+				$5$  & {\scriptsize{$17.13\pm0.05$ $[m]$}} & {\scriptsize{$19.16\pm0.83$ $[m]$}}\tabularnewline
 				\hline 
-    $6$  & {\scriptsize{$142.495\pm11.511$ $[rad]$}} & {\scriptsize{$160.950\pm7.749$ $[rad]$}}\tabularnewline
+				$6$  & {\scriptsize{$109.88\pm6.22$ $[rad]$}} & {\scriptsize{$1431.94\pm436.44$ $[rad]$}}\tabularnewline
 				\hline 
 			\end{tabular}
+        \par\end{centering}
+        \caption{Results for hallway scenario \label{table:metric-hallway}}
+    \end{table}
 
-\vspace{1cm}
+    In the hallway scenario, great improvements in behaviour and metrics were achieved.
+    Every metric was beaten by the new model with considerable changes. The FVPM
+    removes the bouncing of pedestrians which is typical of the SFM in this
+    scenario and gives way to the forming of natural pathways for pedestrians.
 
-\begin{figure}[h]
+    \begin{figure}[H]
         \begin{centering}
@@
 
-\begin{figure}[h]
+    \begin{figure}[H]
         \begin{centering}
@@
 
-The number of collisions is decresead compared to the SFM. The fact
+    The number of collisions is decreased compared to the SFM. The fact
     that the time of collision (metric \#2) is bigger than in the SFM,
@@
     scenario but much smaller in the hallway, this shows the problem of
-SFM in high simmetry scenarios (inverse velocities). \\
+    SFM in high symmetry scenarios (inverse velocities). \\
      Each pedestrian turns (in average) $10\%$ less with the FVPM than
@@
 
-\begin{figure}[h]
+    For the escape room scenario, all 9 combinations for the number of pedestrians in [$100$, $150$, $200$] 
+    and the door sizes in [$1.2$, $1.5$, $1.8$] where run.
+    Before presenting the results, two definitions need to be defined:
+    \begin{itemize}
+        \item Pedestrian flow: This is the amount of pedestrians that left the room
+        per unit of time. It is defined as: 
+        \[
+            Q=\frac{\triangle N}{\triangle T}\,\,[Pedestrian/s]
+        \]
+
+        \item Pedestrian specific flow: This is the amount of pedestrians that left
+        the room per unit of time per unit of distance. It is defined as:
+        \[
+            Q_{s}=\frac{\triangle N}{\triangle T*door\_width}\,\,[Pedestrian/s/m]
+        \]
+    \end{itemize}
+
+    The average pedestrian flow ($Q_avg$) was taken by averaging the results of $5$ simulations for each configuration.\\
+    The results are shown on fig. \ref{fig:room-flow-100}, fig. \ref{fig:room-flow-150} and fig. 
+    \ref{fig:room-flow-200}.
+
+    \begin{figure}[H]
         \begin{centering}
-    \includegraphics[width=8.5cm]{pics/steps/room} 
+        \includegraphics[scale=0.2]{pics/flow/12door} 
         \par\end{centering}
-
-    \caption{\label{fig:room-flow}Pedestrian exit flow in room scenario}
+        \caption{\label{fig:room-flow-100}Room evacuation with $1.2$ $[m]$ door}
     \end{figure}
 
-In the case of the escape room, figure \ref{fig:room-flow} shows
-that the first pedestrian leaves the room at the $5$ seconds mark,
-while the last one does it at the $90$ seconds mark, so the flow
-is: 
-\[
-    flow=\frac{100}{1.2*(90-5)}=\frac{100}{102}=0.98\,\,[ped/sec]
-\]
+    \begin{figure}[H]
+        \begin{centering}
+        \includegraphics[scale=0.2]{pics/flow/15door} 
+        \par\end{centering}
+        \caption{\label{fig:room-flow-150}Room evacuation with $1.5$ $[m]$ door}
+    \end{figure}
 
-\begin{figure}[h]
+    \begin{figure}[H]
+        \begin{centering}
+        \includegraphics[scale=0.2]{pics/flow/18door} 
+        \par\end{centering}
+        \caption{\label{fig:room-flow-200}Room evacuation with $1.8$ $[m]$ door}
+    \end{figure}
+
+    The escape flow for each configuration was calculated using octave's $polyfit$ using a 
+    grade $1$ polygon and the slopes for each door size are as follows:
+
+    \begin{table}[H]
+        \begin{centering}
+        \begin{tabular}{|c|c|c|c|}
+        \hline 
+        N \textbackslash{} Door size & $1.2$ & $1.5$ & $1.8$\tabularnewline
+        \hline 
+        \hline 
+        $100$ & $1.02$ & $1.05$ & $1.05$\tabularnewline
+        \hline 
+        $150$ & $1.17$ & $1.18$ & $1.18$\tabularnewline
+        \hline 
+        $200$ & $1.20$ & $1.22$ & $1.23$\tabularnewline
+        \hline 
+        \end{tabular}
+        \caption{Escape room configurations \label{tbl:room-runs}}
+        \end{centering}
+    \end{table}
+
+    \begin{figure}[H]
         \begin{centering}
@@
 
-\begin{figure}[h]
+    \begin{figure}[H]
         \centering{} \includegraphics[width=6.5cm]{pics/program/room-future}
@@
     \end{figure}
+
+    The escape flow of pedestrians does not change drastically depending on the
+    number of pedestrians, unlike the SFM. This happens because of the removal
+    of the social force, which increased as pedestrians increased.
 
@@
     true, we still need further analysis of this scenario to adjust our
-model for both cases. In future work, the paths our virtual pedestrians
-make need to be compared and validated with real-life pedestrians
+    model for both cases. \\
+    In future work, the paths our virtual pedestrians
+    may need to be compared and validated with real-life pedestrians
     paths to complement the use of metrics for the mean of pedestrians.
-Parameters should be revalidated with more metrics and analyzed in
-more detail.
+    Parameters should be re validated with more metrics and analyzed in
+    even more detail. \\
+    % It is important to notice that we have successfully removed the 
+    % (undesired) social force from the original model and replacing it  
+    % with the proposed changes, we were able reproduce real life results.
+\newpage{}
 
-\newpage{}
 \begin{thebibliography}{10}
 
-\bibitem{key-hoog2004} Hoogonen and Bovy (2004).
+\bibitem{key-hoog2004} Hoogendoorn, Serge P., and Piet HL Bovy.
+"Pedestrian route-choice and activity scheduling theory and models." Transportation Research Part B: Methodological 38.2 (2004): 169-190.
 
-\bibitem{key-scha2009} A. Schadschneider (2009). \textquotedbl{}Evacuation
-Dynamics: Empirical Results, Modeling and Applications\textquotedbl{}.
+\bibitem{key-scha2009} Schadschneider, Andreas, et al.
+"Evacuation dynamics: Empirical results, modeling and applications." Encyclopedia of complexity and systems science.
+Springer New York, 2009.
+3142-3176.
 
-\bibitem{key-scha2002} A. Schadschneider (2009). \textquotedbl{}Traffic
-flow: A statistical physics point of view\textquotedbl{}.
+\bibitem{key-scha2002} Schadschneider, Andreas. "Traffic flow: a statistical physics point of view." Physica A: Statistical Mechanics and its Applications 313.1 (2002): 153-187.
 
-\bibitem{key-helb1995} Helbing, Dirk; Molnr, Pter (1995). ``Social
-force model for pedestrian dynamics``.
+\bibitem{key-helb1995} Helbing, Dirk, and Peter Molnar. "Social force model for pedestrian dynamics." Physical review E 51.5 (1995): 4282.
 
-\bibitem{key-helb2000} Helbing, Dirk; Farkas, Ills; Vicsek, Tams
-(2000). ``Simulating dynamical features of escape panic``.
+\bibitem{key-helb2000} Helbing, Dirk, Illés Farkas, and Tamas Vicsek. "Simulating dynamical features of escape panic." Nature 407.6803 (2000): 487-490.
 
-\bibitem{key-tara2005} Taras I. Lakoba (2005). \textquotedbl{}Modifications
-of the Helbing-Molnar-Farkas-Vicsek Social Force Model for Pedestrian
-Evolution\textquotedbl{}.
+\bibitem{key-tara2005} Lakoba, Taras I., David J.
+Kaup, and Neal M.
+Finkelstein.
+"Modifications of the Helbing-Molnar-Farkas-Vicsek social force model for pedestrian evolution." Simulation 81.5 (2005): 339-352.
 
-\bibitem{key-pari2009} Parisi (2009). \textquotedbl{}A modification
-of the Social Force Model can reproduce experimental data of pedestrian
-flows in normal conditions\textquotedbl{}.
+\bibitem{key-pari2009} Parisi, Daniel R., Marcelo Gilman, and Herman Moldovan.
+"A modification of the social force model can reproduce experimental data of pedestrian flows in normal conditions." Physica A: Statistical Mechanics and its Applications 388.17 (2009): 3600-3608.
 
-\bibitem{key-kirc2002} Kirchner and Schadschneider (2002). \textquotedbl{}Simulation
-ofevacuation processes using a bionics-inspired cellular automaton
-model for pedestrian dynamics\textquotedbl{}.
+\bibitem{key-kirc2002} Kirchner, Ansgar, and Andreas Schadschneider.
+"Simulation of evacuation processes using a bionics-inspired cellular automaton model for pedestrian dynamics." Physica A: Statistical Mechanics and its Applications 312.1 (2002): 260-276.
 
-\bibitem{key-pari2011} Baglietto and Parisi, (2011). \textquotedbl{}Continuous-space
-automaton model for pedestrian dynamics\textquotedbl{}.
+\bibitem{key-pari2011} Baglietto, Gabriel, and Daniel R. Parisi. "Continuous-space automaton model for pedestrian dynamics." Physical Review E 83.5 (2011): 056117.
 
-\bibitem{key-kara2009} I. Karamouzas (2009). \textquotedbl{}A Predictive
-Collision Avoidance Model for Pedestrian Simulation\textquotedbl{}.
+\bibitem{key-kara2009} Karamouzas, Ioannis, et al. "A predictive collision avoidance model for pedestrian simulation." Motion in Games. Springer Berlin Heidelberg, 2009. 41-52.
 
-\bibitem{key-kret2001} Kretz (2011). \textquotedbl{}Quickest Paths
-in Simulations of Pedestrians\textquotedbl{}.
+\bibitem{key-kret2001} Kretz, Tobias, et al. "Quickest paths in simulations of pedestrians." Advances in Complex Systems 14.05 (2011): 733-759.
 
-\bibitem{key-mous2009} Moussad M, Helbing D, Garnier S, Johansson
-A, Combe M and aulaz G (2009).
+\bibitem{key-mous2009} Moussaïd, Mehdi, et al.
+"Experimental study of the behavioural mechanisms underlying self-organization in human crowds." Proceedings of the Royal Society B: Biological Sciences (2009): rspb-2009.
 
-\bibitem{key-pedEvDyn2012} Ulrich Weidmann, Uwe Kirsch, Michael Schreckenberg
-(2012). Pedestrian and Evacuation Dynamics 2012.\end{thebibliography}
+\bibitem{key-pedEvDyn2012} Weidmann, Ulrich, Uwe Kirsch, and Michael Schreckenberg, eds. Pedestrian and Evacuation Dynamics 2012. Springer Science \& Business, 2014.
+
+\bibitem{key-qianLing2015} Qian-Ling, Wang, et al. "A new collision avoidance model for pedestrian dynamics." Chinese Physics B 24.3 (2015): 038901.
+
+\end{thebibliography}
 

### 2015-06-09 doc/informe/informe.tex
agrego grafico para room escape - SFM. renombro carpeta room_evacuation a flow (ya que asi se usa en el informe). Correcciones varias para el informe.

@@
 reduced number of collisions, increased average
-speed and reduced average deviation angle of navigating pedestrians.
+speed and reduced average deviation angle of navigating pedestrians. \\
 \textbf{keywords:} pedestrian, collision avoidance, future virtual
@@
     The average pedestrian flow ($Q_avg$) was taken by averaging the results of $5$ simulations for each configuration.\\
-    The results are shown on fig. \ref{fig:room-flow-100}, fig. \ref{fig:room-flow-150} and fig. 
-    \ref{fig:room-flow-200}.
+    The results for the scenario with a door size of $1.5$ $[m]$ are shown on fig. \ref{fig:room-flow-150}:
 
-    \begin{figure}[H]
-        \begin{centering}
-        \includegraphics[scale=0.2]{pics/flow/12door} 
-        \par\end{centering}
-        \caption{\label{fig:room-flow-100}Room evacuation with $1.2$ $[m]$ door}
-    \end{figure}
+    %\begin{figure}[H]
+    %    \begin{centering}
+    %    \includegraphics[scale=0.2]{pics/flow/12door} 
+    %    \par\end{centering}
+    %    \caption{\label{fig:room-flow-100}Room evacuation with $1.2$ $[m]$ door}
+    %\end{figure}
 
@@
         \par\end{centering}
-        \caption{\label{fig:room-flow-150}Room evacuation with $1.5$ $[m]$ door}
+        \caption{\label{fig:room-flow-150}FVPM - Room evacuation with $1.5$ $[m]$ door}
     \end{figure}
+
+    For the same scenario, the escape flow when using the SFM model is shown on fig. \ref{fig:sfm-room-flow-15}
 
@@
         \begin{centering}
-        \includegraphics[scale=0.2]{pics/flow/18door} 
+        \includegraphics[scale=0.2]{pics/flow/sfm/sfm15door} 
         \par\end{centering}
-        \caption{\label{fig:room-flow-200}Room evacuation with $1.8$ $[m]$ door}
+        \caption{\label{fig:sfm-room-flow-15}SFM - Room evacuation with $1.5$ $[m]$ door}
     \end{figure}
 
-    The escape flow for each configuration was calculated using octave's $polyfit$ using a 
-    grade $1$ polygon and the slopes for each door size are as follows:
+    %\begin{figure}[H]
+    %    \begin{centering}
+    %    \includegraphics[scale=0.2]{pics/flow/18door} 
+    %    \par\end{centering}
+    %    \caption{\label{fig:room-flow-200}Room evacuation with $1.8$ $[m]$ door}
+    %\end{figure}
+
+    The escape flow for each door configuration for the FVPM was calculated using octave's 
+    $polyfit$ using a grade $1$ polygon and the slopes for each door size are as follows:
 
@@
         \hline 
-        N \textbackslash{} Door size & $1.2$ & $1.5$ & $1.8$\tabularnewline
+        Door size \textbackslash{} N & $100$ & $1.5$ & $200$\tabularnewline
         \hline 
         \hline 
-        $100$ & $1.02$ & $1.05$ & $1.05$\tabularnewline
+        $1.2$ & $1.02$ & $1.05$ & $1.05$\tabularnewline
         \hline 
-        $150$ & $1.17$ & $1.18$ & $1.18$\tabularnewline
+        $1.5$ & $1.17$ & $1.18$ & $1.18$\tabularnewline
         \hline 
-        $200$ & $1.20$ & $1.22$ & $1.23$\tabularnewline
+        $1.8$ & $1.20$ & $1.22$ & $1.23$\tabularnewline
         \hline 
@@
     % with the proposed changes, we were able reproduce real life results.
+    % The presented model was able to reproduce different number of pedestrians
+    % leaving a room with different door sizes and showing that the exit flow
+    % dos not depend on the number of pedestrians (in contrast to the SFM model)
 \newpage{}
